### 2016-11-23 Draft-1.tex
Changes from papeeria

%% It is just an empty TeX file.
%% Write your code here.
\documentclass {article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{bm}

\hypersetup{
	colorlinks=true,
	urlcolor=blue!70!black
}

\title{Bibliography}
\date{2016-11-07}
\author{Max Penrose}

\begin{document}
\pagenumbering{roman}

\section{Effective Computability}

In this first section I would like to describe the fundamental attributes a machine must have for it to be called a 'computer'. Prior to the war and the development of electronic computation, any human who performed a calculation would  frequently be called a 'computer'. However, this specific attribute of computation is difficult to define - to do so, I will be looking at the minimalist  $\lambda$-Calculus developed by Mathematician and Logician Alonzo Church, the famous concept of Universal Computation and  Computable Numbers developed by English Mathematician Alan Turing, and the work of [OTHERS]

\subsection{Church's $\lambda$-Calculus}

The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability, far from the very real and mechanical world of Turing. It deals with a set of objects - for our purposes denoted with alphanumeric characters - which define what school mathematics or common computer science would call 'functions'. These functions take as their arguments (other objects which the functions act upon) functions alone, and can also output only functions. Take, for example the function $f$:
\begin{equation*}
f = ab
\end{equation*}
This particular function $f$ applies the function $a$ to the function $b$. Note that while commonly we would use the syntax $\mathit{a(b)}$ to express the same thing, it greatly simplifies expression to use this format. Church defines these functions through the method of 'abstraction' - let us look at a different function:
\begin{equation*}
\lambda u.tu
\end{equation*}
This function takes one single argument, which it names the abstract name $u$. It then applies the function $t$ to $u$ and outputs the result. For example, if we were to apply this function to the function $a$:
\begin{equation*}
(\lambda u.tu) a = ta	
\end{equation*}
Functions can take multiple arguments through the use of nesting:
\begin{gather*}
\begin{aligned}
\lambda a.(\lambda b.ba) &=  \lambda ab.ba \\
([\lambda a.(\lambda b.ba)]u)v &= (\lambda b.bu)v \\ &= vu
\end{aligned}
\end{gather*}

Church applies this medium to a variety of concepts we are familiar with. His definitions of numbers are:
\begin{equation*}
\begin{aligned}
\bm{\mathrm{0}} &= \lambda sz.z,
  & % separation
\bm{\mathrm{1}} &= \lambda sz.sz,
  \\
\bm{\mathrm{2}} &= \lambda sz.s(sz),
  &
\bm{\mathrm{3}} &= \lambda sz.s(s(sz)),
  &
etc.
\end{aligned}
\end{equation*}
Here it can bee seen that for each number \textit{n} the argument $s$  is applied to the argument $z$ \textit{n} times.
From this, it is not difficult to define an operation that takes a number as input and increments it by 1 - such a function would take three arguments (the first being the number, and the second two being the arguments $s$ and $z$ for the number) and would apply the argument $s$ to the number:
\begin{equation*}
\bm{\mathrm{S}} = \lambda wyx.y(wyx)
\end{equation*}
Let us test our new successor function by applying it to \textbf{2}:
\begin{gather*}
\begin{aligned}
\bm{\mathrm{S2}} &= (\lambda wyx.y(wyx)) (\lambda sz.s(s(z)))\\
&= y([\lambda sz.(s(s(z)))]yx)\\
&=y[y(y(z))]\\
&=s(s(s(z)))\\
&=\bm{\mathrm{3}}
\end{aligned}
\end{gather*}

From this concept, we are not far from the nursery-school concept of addition. Remembering that each number applies the function $s$ to $z$ \textit{n} times, and that addition is simply incrementing \textit{a} \textit{b} times, addition is as simple as:
\begin{equation*}
a\bm{\mathrm{S}}b	
\end{equation*}
Let us test this by summing \textbf{2} and \textbf{3}:
\begin{gather*}
\begin{aligned}
\bm{\mathrm{2S3}} &= (\lambda sz.s(s(z))) (\lambda wyx.y(wyx)) (\lambda sz.s(s(s(z))))\\
&= (\lambda wyx.y(wyx)) [(\lambda wyx.y(wyx)) [\lambda sz.s(s(s(z)))]]\\
&= (\lambda wyx.y(wyx)) [\lambda sz.s(s(s(s(z))))]\\
&= \lambda sz.s(s(s(s(s(z)))))\\
&= \bm{\mathrm{5}} \qed
\end{aligned}
\end{gather*}

\end{document}

### 2016-11-23 Draft-1.tex
Changes from papeeria

@@
-%% It is just an empty TeX file.
-%% Write your code here.
 \documentclass {article}
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{bm}
@@
 In this first section I would like to describe the fundamental attributes a machine must have for it to be called a 'computer'.
-Prior to the war and the development of electronic computation, any human who performed a calculation would  frequently be called a 'computer'.
+Prior to the war and the development of electronic computation, any human who performed a calculatiation would  frequently be called a 'computer'.
 However, this specific attribute of computation is difficult to define - to do so, I will be looking at the minimalist  $\lambda$-Calculus developed by Mathematician and Logician Alonzo Church, the famous concept of Universal Computation and  Computable Numbers developed by English Mathematician Alan Turing, and the work of [OTHERS]
@@
 \bm{\mathrm{0}} &= \lambda sz.z,
-  & % separation
+  & % seperation
 \bm{\mathrm{1}} &= \lambda sz.sz,
@@
 &= \lambda sz.s(s(s(s(s(z)))))\\
-&= \bm{\mathrm{5}} \qed
+&= \bm{\mathrm{5}}
+\end{aligned}
+\end{gather*}
+Multiplication can also be calculated by defining the function \textbf{M}:
+\begin{equation*}
+\bm{\mathrm{M}} = \lambda wyx.w(yx)
+\end{equation*}
+\begin{gather*}
+\begin{aligned}
+\bm{\mathrm{M22}} &= (\lambda wyx.w(yx))(\lambda ab.a(a(b)))(\lambda sz.s(s(z)))\\
+&= \lambda x.(\lambda ab.a(a(b)))[(\lambda sz.s(s(z)))x]\\
+&= \lambda x.(\lambda ab.a(a(b)))[\lambda z.x(x(z))]\\
+&= \lambda x.(\lambda b.[\lambda z.x(x(z))]([\lambda z.x(x(z))]b))\\
+&= \lambda x.(\lambda b.[\lambda z.x(x(z))][x(x(b))])\\
+&= \lambda x.(\lambda b.x(x(x(x(b)))))\\
+&= \lambda xb.x(x(x(x(b))))\\
+&= \bm{\mathrm{4}}
 \end{aligned}
@@
 
+    Church also defines boolean logic and operations used for them:
+
+\begin{equation*}
+\begin{aligned}
+\bm{\mathrm{T}} &= \lambda ab.a,
+  & % seperation
+\bm{\mathrm{F}} &= \lambda ab.b
+\end{aligned}
+\end{equation*}
+Note that for these functions which each takes two arguments, \textbf{T} outputs the first while \textbf{F} outputs the second. 
 \end{document}

### 2016-11-23 Draft-1.tex
Changes from papeeria

@@
 
-    Church also defines boolean logic and operations used for them:
+    Church defines functions to operate boolean logic - firstly representing True and False:
 
@@
 \end{equation*}
-Note that for these functions which each takes two arguments, \textbf{T} outputs the first while \textbf{F} outputs the second. 
+These functions each take two arguments - the \textbf{T} function returns the first, while the \textbf{F} function returns the second. Functions representing boolean operations can also be defined:
+\begin{gather*}
+\begin{aligned}
+\vee &= \lambda xy.x\bm{\mathrm{T}}y\\
+\wedge &= \lambda xy.xy\bm{\mathrm{F}}\\
+\lnot &= \lambda x.x\bm{\mathrm{FT}}
+\end{aligned}
+\end{gather*}
+From these operations, the xor operation can be found
+\begin{gather*}
+\begin{aligned}
+\oplus = \lambda xy.\wedge (\vee xy)(\lnot (\wedge xy))
+\oplus = \lambda xy.x(\lnot y)y
+\end{aligned}
+\end{gather*}
 \end{document}

### 2016-11-23 Draft-1.tex
Changes from papeeria

@@
 \wedge &= \lambda xy.xy\bm{\mathrm{F}}\\
-\lnot &= \lambda x.x\bm{\mathrm{FT}}
+\lnot &= \lambda x.x\bm{\mathrm{FT}} \\
+\veebar &= \lambda xy.x(\lnot y)y
 \end{aligned}
 \end{gather*}
-From these operations, the xor operation can be found
+The derivation of such operations is not difficult to understand if one considers the truth tables for each operation, remembering that T selects the first and F selects the second argument.
+\newpage
+With the fundamental boolean system of our computational system in place, we must next construct conditionals. The first, and simplest, of these will check if a number is equal to zero:
+\begin{equation*}
+\bm{\mathrm{Z}} = \lambda x.x\bm{\mathrm{F\lnot F}}
+\end{equation*}
+To understand this somewhat less than trivial concept, remember that \textbf{F} applied to any single argument yields the identity function $\lambda x.x$, and that \textbf{0} applied to any two arguments yields only the second:
+\begin{equation*}
+\bm{0}ab = (\lambda sz.z)ab = b
+\end{equation*}
+From this, it easier to see how the function works. Firstly with \textbf{0}:
 \begin{gather*}
 \begin{aligned}
-\oplus = \lambda xy.\wedge (\vee xy)(\lnot (\wedge xy))
-\oplus = \lambda xy.x(\lnot y)y
+\bm{\mathrm{Z0}} &= (\lambda x.x\bm{\mathrm{f\lnot F}})\bm{0}\\
+&= \bm{\mathrm{0F\lnot F}}\\
+&= \bm{\mathrm{\lnot F}}\\
+&= \bm{\mathrm{T}}
+\end{aligned}
+\end{gather*}
+Secondly with \textbf{2}:
+\begin{gather*}
+\begin{aligned}
+\bm{\mathrm{Z2}} &= (\lambda x.x\bm{\mathrm{f\lnot F}})\bm{2}\\
+&= \bm{\mathrm{2F\lnot F}}\\
+&= (\bm{\mathrm{F}}(\bm{\mathrm{F}}\lnot)) \bm{\mathrm{F}}\\
+&= (\bm{\mathrm{F}}(\lambda x.x))\bm{\mathrm{F}}\\
+&= (\lambda x.x)\bm{\mathrm{F}}
+&= \bm{\mathrm{F}
 \end{aligned}

### 2016-11-23 Draft-1.tex
Subtraction function

@@
 
-Church applies this medium to a variety of concepts we are familiar with. His definitions of numbers are:
+\subsubsection{Arithmetical definitions}
+
+Church applies this medium to a variety of concepts we will already be familiar with - firstly, that of positive integers:
 \begin{equation*}
@@
 \end{gather*}
+We should rearrange our earlier addition method into an 'addition' function of the same format which takes two arguments:
+\begin{equation*}
+\bm{\mathrm{A}} = \lambda ab.aSb
+\end{equation*}
+A 'power' function to find $a^b$can also be defined, of astonishing simplicity:
+\begin{equation*}
+\bm{\mathrm{P}} = \lambda ba.ab
+\end{equation*}
+\begin{gather*}
+\begin{aligned}
+\bm{\mathrm{P23}} &= (\lambda ab.ab)(\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
+&= (\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
+&= (\lambda z.[\lambda ty.t(t(t(y)))]([\lambda ux.u(u(u(x)))]z))\\
+&= (\lambda z.[\lambda ty.t(t(t(y))][\lambda x.z(z(z(x)))])\\
+&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]y))])\\
+&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([\lambda x.z(z(z(x)))][z(z(z(y)))])])\\
+&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([z(z(z(z(z(z(y))))))])])\\
+&= (\lambda z.[\lambda y.[z(z(z(z(z(z(z(z(z(y)))))))))]])\\
+&= \lambda zy.z(z(z(z(z(z(z(z(z(y)))))))))\\
+&= \bm{\mathrm{9}} = \bm{\mathrm{3^2}}
+\end{aligned}
+\end{gather*}
+
+\subsubsection{Logic and Conditions}
 
@@
 \end{equation*}
-These functions each take two arguments - the \textbf{T} function returns the first, while the \textbf{F} function returns the second. Functions representing boolean operations can also be defined:
+These functions each take two arguments - the \textbf{T} function returns the first, while the \textbf{F} function returns the second.
+These concepts are the base of conditional logic in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
+For such operations, the concept of a 'pair' exists:
+\begin{equation*}
+\lambda x.xab
+\end{equation*}
+where $a$ and $b$ are functions. For a choice of an element from the pair, the argument of either \textbf{T} or \textbf{F} is provided:
+\begin{gather*}
+\begin{aligned}
+(\lambda x.xab)T &= a\\
+(\lambda x.xab)F &= b
+\end{aligned}
+\end{gather*}
+
+Functions representing boolean operations can also be defined:
 \begin{gather*}
@@
 The derivation of such operations is not difficult to understand if one considers the truth tables for each operation, remembering that T selects the first and F selects the second argument.
-\newpage
 With the fundamental boolean system of our computational system in place, we must next construct conditionals. The first, and simplest, of these will check if a number is equal to zero:
@@
 &= (\bm{\mathrm{F}}(\lambda x.x))\bm{\mathrm{F}}\\
-&= (\lambda x.x)\bm{\mathrm{F}}
-&= \bm{\mathrm{F}
+&= (\lambda x.x)\bm{\mathrm{F}}\\
+&= \bm{\mathrm{F}} 
 \end{aligned}
 \end{gather*}
+However, in order to develop other conditional tests we will need a 'predecessor' function - something frighteningly difficult under lambda calculus.
+\subsubsection{Subtraction}
+
+The elusive predecessor function was created by Stephen Kleene, a student of Church's, and was something of a landmark in the development of $\lambda$-calculus.
+Firstly, the function transforms the pair (n, n-1) (the argument $p$) into the pair (n+1, n) (the new pair's elements are an increment and a copy of the first value respectively):
+\begin{equation*}
+\bm{\psi} = \lambda pc.c(S(pT))(pT)
+\end{equation*}
+To find the predecessor to $n$ therefore, we apply this function $n$ times to the pair (0, 0) and the pair (n, n-1) is formed, after which the second element can easily be selected.
+\begin{equation*}
+\bm{\mathrm{P}} = \lambda n.n \bm{\psi} (\lambda x.00) F 
+\end{equation*}
+\begin{equation*}
+\begin{aligned}
+\bm{\mathrm{P3}} &= (\lambda n.n [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}] \bm{\mathrm{F}}) [\lambda sz.s(s(s(z)))]\\
+&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
+&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
+&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda x.\bm{\mathrm{00}}]))\bm{\mathrm{F}}\\
+&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c(\bm{\mathrm{S}}[\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})([\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})))\bm{\mathrm{F}}\\
+&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c\bm{\mathrm{10}}))\bm{\mathrm{F}}\\
+&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda c.c\bm{\mathrm{21}}]\bm{\mathrm{F}}\\
+&= [\lambda c.c\bm{\mathrm{32}} ])\bm{\mathrm{F}}\\
+&= \bm{\mathrm{2}}
+\end{aligned}
+\end{equation*}
 \end{document}

### 2016-11-24 Draft-1.tex
Subtraction Function 💯💯👌👌💪💪
Changes from papeeria

@@
 \end{equation*}
+Of course now the subtraction function can be found (using \textbf{D} for difference):
+\begin{equation*}
+\bm{\mathrm{D}} = \lambda ab.bPa
+\end{equation*}
+Bearing in mind the predecessor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b>a$.
+\subsubsection{Further Conditional Logic}
+With this useful quirk of the \textbf{D} function, we can produce comparative logical operators:
+\begin{gather*}
+\begin{aligned}
+\bm{\leq} = \lambda ab.\bm{\mathrm{Z}}(Dab)
+\end{aligned}
+\end{gather*}
 \end{document}

### 2016-11-24 Draft-1.tex
Conditional comparison, Recursor function

@@
 \subsubsection{Further Conditional Logic}
+
 With this useful quirk of the \textbf{D} function, we can produce comparative logical operators:
-\begin{gather*}
+\begin{equation*}
 \begin{aligned}
-\bm{\leq} = \lambda ab.\bm{\mathrm{Z}}(Dab)
+\bm{\leq} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}ab)
+  & % seperation
+\bm{\geq} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}ba)
+  \\
+\bm{<} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}a[Sb])
+  &
+\bm{>} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}[Sb]a)
 \end{aligned}
-\end{gather*}
+\end{equation*}
+And through combination of these, we can create the equivalence and inequivalence operators (using $\bm{\doteq}$ for clarity from $=$:
+\begin{equation*}
+\begin{aligned}
+\bm{\doteq} &= \lambda ab.\wedge(\bm{\leq}ab)(\bm{\geq}ab)\\
+\bm{\neq} &= \lambda ab.\vee(\bm{<}ab)(\bm{>}ab)
+\end{aligned}
+\end{equation*}
+\subsubsection{Recursion}
+
+So far, Church's $\lambda$-Calculus is very close to the operation of a modern computation language.
+It has representation for boolean values, for conditional statements, for positive integers (signed integers can be expressed as a pair of a positive integer and a boolean for sign) and arithmetic, as well as set operations for booleans and comparators for integers - In fact, we are very close to our definition of computability save one thing.
+Continuity and repetition is one of the most significant aspects of computers, the power of this being the ability to transform a finite configuration into a potentially infinite result.
+This is done through one of the most remarkable functions in $\lambda$-Calculus, the recursor function:
+
+\begin{equation*}
+\bm{\mathrm{R}} = \lambda y.(\lambda x.y(xx))(\lambda x.y(xx)
+\end{equation*}
+
+\begin{equation*}
+\begin{aligned}
+\bm{\mathrm{R}}a &= (\lambda x.a(xx))[\lambda x.a(xx)]\\
+&= a([\lambda x.a(xx)][\lambda x.a(xx)]\\
+&= a(\bm{\mathrm{R}}a)
+\end{aligned}
+\end{equation*}
 \end{document}

### 2016-11-24 Draft-1.tex
Outroduction and finished off recursion

@@
   \\
-\bm{<} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}a[Sb])
+\bm{<} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}a[\bm{\mathrm{S}}b])
   &
-\bm{>} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}[Sb]a)
+\bm{>} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}[\bm{\mathrm{S}}b]a)
 \end{aligned}
@@
 \end{equation*}
-
 \begin{equation*}
@@
 \end{equation*}
+Therefore, the \textbf{R} function applied to any function $a$ applies the function $a$ to the function \textbf{R} applied to $a$ - if substitution continues, an infinite series of nested $a$ functions is created; an infinite result is produced from a finite configuration.
+Of course we can create finites as well by halting the function - an example of this would be the factorial function, where \textbf{!}a = \textbf{M}a(\textbf{!}[\textbf{P}a]) and \textbf{!0} = \textbf{1}.
+Firstly, a recursive definition:
+\begin{equation*}
+\begin{aligned}
+\bm{\mathrm{\xi}} &= (\lambda fa.\bm{\mathrm{Z}}a\bm{\mathrm{1}}[\bm{\mathrm{M}}a(f[\bm{\mathrm{P}}a])])\\
+\bm{!} &= \bm{\xi}!
+\end{aligned}
+\end{equation*}
+i.e.
+the factorial function is the $\bm{\xi}$ function with itself as the argument $f$.
+Unfortunately such a definition is illegal under $\lambda$-Calculus as strictly no functions have names - this is where the function \textbf{R} comes into play.
+To find the factorial of \textbf{3}:
+\begin{equation*}
+\begin{aligned}
+\bm{\mathrm{R\xi 3}} &= \bm{\mathrm{\xi}}(\bm{\mathrm{R\xi}})\bm{\mathrm{3}}\\
+&= \bm{\mathrm{Z30}}[\bm{\mathrm{M3}}([\bm{\mathrm{R\xi}}][\bm{\mathrm{P3}}])\\
+&= \bm{\mathrm{M3}}(\bm{\mathrm{R\xi}}\bm{2})]\\
+&= \bm{\mathrm{M3}}(\bm{\mathrm{M2}}(\bm{\mathrm{M11}}))\\
+&= \bm{\mathrm{6}}
+\end{aligned}
+\end{equation*}
+The recursive identity \textbf{R} allows for \textbf{R}$\bm{\xi}$ to be applied as the first argument to the $\bm{\xi}$ function - as a result, the procedure is repeated for \textbf{2} and \textbf{1}, before stopping at \textbf{0}.
+To simplify, the factorial function:
+\begin{equation*}
+\bm{!} = \lambda x.\bm{\mathrm{R\xi}}x
+\end{equation*}
+
+Our brief stroll through the key aspects of $\lambda$-Calculus is complete.
+We have defined that every basic necessary concept in a common programming language can be defined through the use of two simple axioms - that of the concept of functions, and the operation of substitution.
+$\lambda$-Calculus was described by Church as an 'effectively calculable' system, in that it could perform any calculable calculation.
+In more popular terms, it is Turing-complete - we will look at what this is and why this is the case later on in the project.
+However, it is clear to see that the Calculus is able to simulate many aspects of the computer - data storage with pairs (pairs of pairs can be used for larger capacity), conditionals and booleans, integers and arithmetic and, finally, the ability to be continuous (circular) from a finite configuration.
+This is our first definition of a 'computer', and therefore any mechanical or axiomatic system which is able to simulate $\lambda$-calculus is also a 'computer', and shall also be called 'effectively calculable'.
 \end{document}

### 2016-11-24 Draft-1.tex
Formatting, Title, Contents

@@
 \usepackage[a4paper, total={6in, 8in}]{geometry}
-\usepackage{hyperref}
-\usepackage{xcolor}
 \usepackage{amsmath}
@@
 
-\hypersetup{
-	colorlinks=true,
-	urlcolor=blue!70!black
-}
-
-\title{Bibliography}
-\date{2016-11-07}
+\title{How Significant was WW2 in the Development of the Computer?}
+\date{November 24, 2016}
 \author{Max Penrose}
@@
 \pagenumbering{roman}
+\maketitle
+\tableofcontents
 
@@
 In this first section I would like to describe the fundamental attributes a machine must have for it to be called a 'computer'.
-Prior to the war and the development of electronic computation, any human who performed a calculatiation would  frequently be called a 'computer'.
-However, this specific attribute of computation is difficult to define - to do so, I will be looking at the minimalist  $\lambda$-Calculus developed by Mathematician and Logician Alonzo Church, the famous concept of Universal Computation and  Computable Numbers developed by English Mathematician Alan Turing, and the work of [OTHERS]
+Prior to the war and the development of electronic computation, any human who performed a calculation would  frequently be called a 'computer'.
+However, this specific attribute of computation is difficult to define - to do so, I will be looking at the minimalist  $\lambda$-Calculus developed by Mathematician and Logician Alonzo Church, the famous concept of the Universal Turing Machine created by English Mathematician Alan Turing, and the similarities and differences between these two definitions.
 
@@
 The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability, far from the very real and mechanical world of Turing.
-It deals with a set of objects - for our purposes denoted with alphanumeric characters - which define what school mathematics or common computer science would call 'functions'.
+It deals with a set of objects - for our purposes denoted with single symbolic characters - which define what school mathematics or common computer science would call 'functions'.
 These functions take as their arguments (other objects which the functions act upon) functions alone, and can also output only functions.
@@
 This particular function $f$ applies the function $a$ to the function $b$.
-Note that while commonly we would use the syntax $\mathit{a(b)}$ to express the same thing, it greatly simplifies expression to use this format.
-Church defines these functions through the method of 'abstraction' - let us look at a different function:
+Note that while commonly we would use the syntax $a(b)$ to express the same thing, it greatly simplifies expression to use this format.
+Church defines these functions through the method of 'abstraction' - let us look at a different function to illustrate:
 \begin{equation*}
@@
 \end{equation*}
+
 Functions can take multiple arguments through the use of nesting:
@@
 Here it can bee seen that for each number \textit{n} the argument $s$  is applied to the argument $z$ \textit{n} times.
+
 From this, it is not difficult to define an operation that takes a number as input and increments it by 1 - such a function would take three arguments (the first being the number, and the second two being the arguments $s$ and $z$ for the number) and would apply the argument $s$ to the number:
@@
 \end{gather*}
+
 Multiplication can also be calculated by defining the function \textbf{M}:
@@
 \end{equation*}
+
 A 'power' function to find $a^b$can also be defined, of astonishing simplicity:
@@
 These functions each take two arguments - the \textbf{T} function returns the first, while the \textbf{F} function returns the second.
+
 These concepts are the base of conditional logic in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
@@
 The derivation of such operations is not difficult to understand if one considers the truth tables for each operation, remembering that T selects the first and F selects the second argument.
+
 With the fundamental boolean system of our computational system in place, we must next construct conditionals. The first, and simplest, of these will check if a number is equal to zero:
@@
 \end{gather*}
-However, in order to develop other conditional tests we will need a 'predecessor' function - something frighteningly difficult under lambda calculus.
+
+However, in order to develop other conditional tests we will need a 'predecessor' function - something surprisingly difficult under lambda calculus.
 \subsubsection{Subtraction}
@@
 The elusive predecessor function was created by Stephen Kleene, a student of Church's, and was something of a landmark in the development of $\lambda$-calculus.
+
 Firstly, the function transforms the pair (n, n-1) (the argument $p$) into the pair (n+1, n) (the new pair's elements are an increment and a copy of the first value respectively):
@@
 \end{equation*}
+
 Of course now the subtraction function can be found (using \textbf{D} for difference):
@@
 
+\subsubsection{Conclusion}
 Our brief stroll through the key aspects of $\lambda$-Calculus is complete.

### 2016-12-04 Draft 2/Master.tex
Draft 2 - migrated to multidocument
Uses embedded documents with subfiles package

--- 2016-11-24 Draft-1.tex
@@
 \usepackage[a4paper, total={6in, 8in}]{geometry}
-\usepackage{hyperref}
-\usepackage{xcolor}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage{subfiles}
+\usepackage{blindtext}
 \usepackage{amsmath}
@@
 
-The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability, far from the very real and mechanical world of Turing.
-It deals with a set of objects - for our purposes denoted with alphanumeric characters - which define what school mathematics or common computer science would call 'functions'.
-These functions take as their arguments (other objects which the functions act upon) functions alone, and can also output only functions.
-Take, for example the function $f$:
-\begin{equation*}
-f = ab
-\end{equation*}
-This particular function $f$ applies the function $a$ to the function $b$.
-Note that while commonly we would use the syntax $\mathit{a(b)}$ to express the same thing, it greatly simplifies expression to use this format.
-Church defines these functions through the method of 'abstraction' - let us look at a different function:
-\begin{equation*}
-\lambda u.tu
-\end{equation*}
-This function takes one single argument, which it names the abstract name $u$.
-It then applies the function $t$ to $u$ and outputs the result.
-For example, if we were to apply this function to the function $a$:
-\begin{equation*}
-(\lambda u.tu) a = ta	
-\end{equation*}
-Functions can take multiple arguments through the use of nesting:
-\begin{gather*}
-\begin{aligned}
-\lambda a.(\lambda b.ba) &=  \lambda ab.ba \\
-([\lambda a.(\lambda b.ba)]u)v &= (\lambda b.bu)v \\ &= vu
-\end{aligned}
-\end{gather*}
+\subfile{"Section 1 - Lambda Calculus"}
 
-\subsubsection{Arithmetical definitions}
-
-Church applies this medium to a variety of concepts we will already be familiar with - firstly, that of positive integers:
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{0}} &= \lambda sz.z,
-  & % seperation
-\bm{\mathrm{1}} &= \lambda sz.sz,
-  \\
-\bm{\mathrm{2}} &= \lambda sz.s(sz),
-  &
-\bm{\mathrm{3}} &= \lambda sz.s(s(sz)),
-  &
-etc.
-\end{aligned}
-\end{equation*}
-Here it can bee seen that for each number \textit{n} the argument $s$  is applied to the argument $z$ \textit{n} times.
-From this, it is not difficult to define an operation that takes a number as input and increments it by 1 - such a function would take three arguments (the first being the number, and the second two being the arguments $s$ and $z$ for the number) and would apply the argument $s$ to the number:
-\begin{equation*}
-\bm{\mathrm{S}} = \lambda wyx.y(wyx)
-\end{equation*}
-Let us test our new successor function by applying it to \textbf{2}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{S2}} &= (\lambda wyx.y(wyx)) (\lambda sz.s(s(z)))\\
-&= y([\lambda sz.(s(s(z)))]yx)\\
-&=y[y(y(z))]\\
-&=s(s(s(z)))\\
-&=\bm{\mathrm{3}}
-\end{aligned}
-\end{gather*}
-
-From this concept, we are not far from the nursery-school concept of addition.
-Remembering that each number applies the function $s$ to $z$ \textit{n} times, and that addition is simply incrementing \textit{a} \textit{b} times, addition is as simple as:
-\begin{equation*}
-a\bm{\mathrm{S}}b	
-\end{equation*}
-Let us test this by summing \textbf{2} and \textbf{3}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{2S3}} &= (\lambda sz.s(s(z))) (\lambda wyx.y(wyx)) (\lambda sz.s(s(s(z))))\\
-&= (\lambda wyx.y(wyx)) [(\lambda wyx.y(wyx)) [\lambda sz.s(s(s(z)))]]\\
-&= (\lambda wyx.y(wyx)) [\lambda sz.s(s(s(s(z))))]\\
-&= \lambda sz.s(s(s(s(s(z)))))\\
-&= \bm{\mathrm{5}}
-\end{aligned}
-\end{gather*}
-Multiplication can also be calculated by defining the function \textbf{M}:
-\begin{equation*}
-\bm{\mathrm{M}} = \lambda wyx.w(yx)
-\end{equation*}
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{M22}} &= (\lambda wyx.w(yx))(\lambda ab.a(a(b)))(\lambda sz.s(s(z)))\\
-&= \lambda x.(\lambda ab.a(a(b)))[(\lambda sz.s(s(z)))x]\\
-&= \lambda x.(\lambda ab.a(a(b)))[\lambda z.x(x(z))]\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))]([\lambda z.x(x(z))]b))\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))][x(x(b))])\\
-&= \lambda x.(\lambda b.x(x(x(x(b)))))\\
-&= \lambda xb.x(x(x(x(b))))\\
-&= \bm{\mathrm{4}}
-\end{aligned}
-\end{gather*}
-We should rearrange our earlier addition method into an 'addition' function of the same format which takes two arguments:
-\begin{equation*}
-\bm{\mathrm{A}} = \lambda ab.aSb
-\end{equation*}
-A 'power' function to find $a^b$can also be defined, of astonishing simplicity:
-\begin{equation*}
-\bm{\mathrm{P}} = \lambda ba.ab
-\end{equation*}
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{P23}} &= (\lambda ab.ab)(\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda z.[\lambda ty.t(t(t(y)))]([\lambda ux.u(u(u(x)))]z))\\
-&= (\lambda z.[\lambda ty.t(t(t(y))][\lambda x.z(z(z(x)))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]y))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([\lambda x.z(z(z(x)))][z(z(z(y)))])])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([z(z(z(z(z(z(y))))))])])\\
-&= (\lambda z.[\lambda y.[z(z(z(z(z(z(z(z(z(y)))))))))]])\\
-&= \lambda zy.z(z(z(z(z(z(z(z(z(y)))))))))\\
-&= \bm{\mathrm{9}} = \bm{\mathrm{3^2}}
-\end{aligned}
-\end{gather*}
-
-\subsubsection{Logic and Conditions}
-
-    Church defines functions to operate boolean logic - firstly representing True and False:
-
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{T}} &= \lambda ab.a,
-  & % seperation
-\bm{\mathrm{F}} &= \lambda ab.b
-\end{aligned}
-\end{equation*}
-These functions each take two arguments - the \textbf{T} function returns the first, while the \textbf{F} function returns the second.
-These concepts are the base of conditional logic in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
-For such operations, the concept of a 'pair' exists:
-\begin{equation*}
-\lambda x.xab
-\end{equation*}
-where $a$ and $b$ are functions. For a choice of an element from the pair, the argument of either \textbf{T} or \textbf{F} is provided:
-\begin{gather*}
-\begin{aligned}
-(\lambda x.xab)T &= a\\
-(\lambda x.xab)F &= b
-\end{aligned}
-\end{gather*}
-
-Functions representing boolean operations can also be defined:
-\begin{gather*}
-\begin{aligned}
-\vee &= \lambda xy.x\bm{\mathrm{T}}y\\
-\wedge &= \lambda xy.xy\bm{\mathrm{F}}\\
-\lnot &= \lambda x.x\bm{\mathrm{FT}} \\
-\veebar &= \lambda xy.x(\lnot y)y
-\end{aligned}
-\end{gather*}
-The derivation of such operations is not difficult to understand if one considers the truth tables for each operation, remembering that T selects the first and F selects the second argument.
-With the fundamental boolean system of our computational system in place, we must next construct conditionals. The first, and simplest, of these will check if a number is equal to zero:
-\begin{equation*}
-\bm{\mathrm{Z}} = \lambda x.x\bm{\mathrm{F\lnot F}}
-\end{equation*}
-To understand this somewhat less than trivial concept, remember that \textbf{F} applied to any single argument yields the identity function $\lambda x.x$, and that \textbf{0} applied to any two arguments yields only the second:
-\begin{equation*}
-\bm{0}ab = (\lambda sz.z)ab = b
-\end{equation*}
-From this, it easier to see how the function works. Firstly with \textbf{0}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{Z0}} &= (\lambda x.x\bm{\mathrm{f\lnot F}})\bm{0}\\
-&= \bm{\mathrm{0F\lnot F}}\\
-&= \bm{\mathrm{\lnot F}}\\
-&= \bm{\mathrm{T}}
-\end{aligned}
-\end{gather*}
-Secondly with \textbf{2}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{Z2}} &= (\lambda x.x\bm{\mathrm{f\lnot F}})\bm{2}\\
-&= \bm{\mathrm{2F\lnot F}}\\
-&= (\bm{\mathrm{F}}(\bm{\mathrm{F}}\lnot)) \bm{\mathrm{F}}\\
-&= (\bm{\mathrm{F}}(\lambda x.x))\bm{\mathrm{F}}\\
-&= (\lambda x.x)\bm{\mathrm{F}}\\
-&= \bm{\mathrm{F}} 
-\end{aligned}
-\end{gather*}
-However, in order to develop other conditional tests we will need a 'predecessor' function - something frighteningly difficult under lambda calculus.
-\subsubsection{Subtraction}
-
-The elusive predecessor function was created by Stephen Kleene, a student of Church's, and was something of a landmark in the development of $\lambda$-calculus.
-Firstly, the function transforms the pair (n, n-1) (the argument $p$) into the pair (n+1, n) (the new pair's elements are an increment and a copy of the first value respectively):
-\begin{equation*}
-\bm{\psi} = \lambda pc.c(S(pT))(pT)
-\end{equation*}
-To find the predecessor to $n$ therefore, we apply this function $n$ times to the pair (0, 0) and the pair (n, n-1) is formed, after which the second element can easily be selected.
-\begin{equation*}
-\bm{\mathrm{P}} = \lambda n.n \bm{\psi} (\lambda x.00) F 
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{P3}} &= (\lambda n.n [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}] \bm{\mathrm{F}}) [\lambda sz.s(s(s(z)))]\\
-&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
-&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda x.\bm{\mathrm{00}}]))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c(\bm{\mathrm{S}}[\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})([\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c\bm{\mathrm{10}}))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda c.c\bm{\mathrm{21}}]\bm{\mathrm{F}}\\
-&= [\lambda c.c\bm{\mathrm{32}} ])\bm{\mathrm{F}}\\
-&= \bm{\mathrm{2}}
-\end{aligned}
-\end{equation*}
-Of course now the subtraction function can be found (using \textbf{D} for difference):
-\begin{equation*}
-\bm{\mathrm{D}} = \lambda ab.bPa
-\end{equation*}
-Bearing in mind the predecessor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b>a$.
-\subsubsection{Further Conditional Logic}
-
-With this useful quirk of the \textbf{D} function, we can produce comparative logical operators:
-\begin{equation*}
-\begin{aligned}
-\bm{\leq} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}ab)
-  & % seperation
-\bm{\geq} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}ba)
-  \\
-\bm{<} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}a[Sb])
-  &
-\bm{>} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}[Sb]a)
-\end{aligned}
-\end{equation*}
-And through combination of these, we can create the equivalence and inequivalence operators (using $\bm{\doteq}$ for clarity from $=$:
-\begin{equation*}
-\begin{aligned}
-\bm{\doteq} &= \lambda ab.\wedge(\bm{\leq}ab)(\bm{\geq}ab)\\
-\bm{\neq} &= \lambda ab.\vee(\bm{<}ab)(\bm{>}ab)
-\end{aligned}
-\end{equation*}
-\subsubsection{Recursion}
-
-So far, Church's $\lambda$-Calculus is very close to the operation of a modern computation language.
-It has representation for boolean values, for conditional statements, for positive integers (signed integers can be expressed as a pair of a positive integer and a boolean for sign) and arithmetic, as well as set operations for booleans and comparators for integers - In fact, we are very close to our definition of computability save one thing.
-Continuity and repetition is one of the most significant aspects of computers, the power of this being the ability to transform a finite configuration into a potentially infinite result.
-This is done through one of the most remarkable functions in $\lambda$-Calculus, the recursor function:
-
-\begin{equation*}
-\bm{\mathrm{R}} = \lambda y.(\lambda x.y(xx))(\lambda x.y(xx)
-\end{equation*}
-
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{R}}a &= (\lambda x.a(xx))[\lambda x.a(xx)]\\
-&= a([\lambda x.a(xx)][\lambda x.a(xx)]\\
-&= a(\bm{\mathrm{R}}a)
-\end{aligned}
-\end{equation*}
 \end{document}

### 2016-12-04 Draft 2/Section 1 - Lambda Calculus.tex
Draft 2 - migrated to multidocument
Uses embedded documents with subfiles package

--- 2016-11-24 Draft-1.tex
@@
-\documentclass {article}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{bm}
-
-\title{How Significant was WW2 in the Development of the Computer?}
-\date{November 24, 2016}
-\author{Max Penrose}
+\documentclass[Master.tex]{subfiles}
 
@@
 \pagenumbering{roman}
-\maketitle
-\tableofcontents
-
-\section{Effective Computability}
-
-In this first section I would like to describe the fundamental attributes a machine must have for it to be called a 'computer'.
-Prior to the war and the development of electronic computation, any human who performed a calculation would  frequently be called a 'computer'.
-However, this specific attribute of computation is difficult to define - to do so, I will be looking at the minimalist  $\lambda$-Calculus developed by Mathematician and Logician Alonzo Church, the famous concept of the Universal Turing Machine created by English Mathematician Alan Turing, and the similarities and differences between these two definitions.
-
-\subsection{Church's $\lambda$-Calculus}
 

### 2016-12-04 Draft 2/Section 2 - Turing Machines.tex
Added Turing Machines section
(empty); Fixed numbering

--- 2016-12-04 Draft 2/Section 1 - Lambda Calculus.tex
@@
 \begin{document}
-\pagenumbering{roman}
 
-The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability, far from the very real and mechanical world of Turing.
-It deals with a set of objects - for our purposes denoted with single symbolic characters - which define what school mathematics or common computer science would call 'functions'.
-These functions take as their arguments (other objects which the functions act upon) functions alone, and can also output only functions.
-Take, for example the function $f$:
-\begin{equation*}
-f = ab
-\end{equation*}
-This particular function $f$ applies the function $a$ to the function $b$.
-Note that while commonly we would use the syntax $a(b)$ to express the same thing, it greatly simplifies expression to use this format.
-Church defines these functions through the method of 'abstraction' - let us look at a different function to illustrate:
-\begin{equation*}
-\lambda u.tu
-\end{equation*}
-This function takes one single argument, which it names the abstract name $u$.
-It then applies the function $t$ to $u$ and outputs the result.
-For example, if we were to apply this function to the function $a$:
-\begin{equation*}
-(\lambda u.tu) a = ta	
-\end{equation*}
-
-Functions can take multiple arguments through the use of nesting:
-\begin{gather*}
-\begin{aligned}
-\lambda a.(\lambda b.ba) &=  \lambda ab.ba \\
-([\lambda a.(\lambda b.ba)]u)v &= (\lambda b.bu)v \\ &= vu
-\end{aligned}
-\end{gather*}
-
-\subsubsection{Arithmetical definitions}
-
-Church applies this medium to a variety of concepts we will already be familiar with - firstly, that of positive integers:
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{0}} &= \lambda sz.z,
-  & % seperation
-\bm{\mathrm{1}} &= \lambda sz.sz,
-  \\
-\bm{\mathrm{2}} &= \lambda sz.s(sz),
-  &
-\bm{\mathrm{3}} &= \lambda sz.s(s(sz)),
-  &
-etc.
-\end{aligned}
-\end{equation*}
-Here it can bee seen that for each number \textit{n} the argument $s$  is applied to the argument $z$ \textit{n} times.
-
-From this, it is not difficult to define an operation that takes a number as input and increments it by 1 - such a function would take three arguments (the first being the number, and the second two being the arguments $s$ and $z$ for the number) and would apply the argument $s$ to the number:
-\begin{equation*}
-\bm{\mathrm{S}} = \lambda wyx.y(wyx)
-\end{equation*}
-Let us test our new successor function by applying it to \textbf{2}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{S2}} &= (\lambda wyx.y(wyx)) (\lambda sz.s(s(z)))\\
-&= y([\lambda sz.(s(s(z)))]yx)\\
-&=y[y(y(z))]\\
-&=s(s(s(z)))\\
-&=\bm{\mathrm{3}}
-\end{aligned}
-\end{gather*}
-
-From this concept, we are not far from the nursery-school concept of addition.
-Remembering that each number applies the function $s$ to $z$ \textit{n} times, and that addition is simply incrementing \textit{a} \textit{b} times, addition is as simple as:
-\begin{equation*}
-a\bm{\mathrm{S}}b	
-\end{equation*}
-Let us test this by summing \textbf{2} and \textbf{3}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{2S3}} &= (\lambda sz.s(s(z))) (\lambda wyx.y(wyx)) (\lambda sz.s(s(s(z))))\\
-&= (\lambda wyx.y(wyx)) [(\lambda wyx.y(wyx)) [\lambda sz.s(s(s(z)))]]\\
-&= (\lambda wyx.y(wyx)) [\lambda sz.s(s(s(s(z))))]\\
-&= \lambda sz.s(s(s(s(s(z)))))\\
-&= \bm{\mathrm{5}}
-\end{aligned}
-\end{gather*}
-
-Multiplication can also be calculated by defining the function \textbf{M}:
-\begin{equation*}
-\bm{\mathrm{M}} = \lambda wyx.w(yx)
-\end{equation*}
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{M22}} &= (\lambda wyx.w(yx))(\lambda ab.a(a(b)))(\lambda sz.s(s(z)))\\
-&= \lambda x.(\lambda ab.a(a(b)))[(\lambda sz.s(s(z)))x]\\
-&= \lambda x.(\lambda ab.a(a(b)))[\lambda z.x(x(z))]\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))]([\lambda z.x(x(z))]b))\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))][x(x(b))])\\
-&= \lambda x.(\lambda b.x(x(x(x(b)))))\\
-&= \lambda xb.x(x(x(x(b))))\\
-&= \bm{\mathrm{4}}
-\end{aligned}
-\end{gather*}
-We should rearrange our earlier addition method into an 'addition' function of the same format which takes two arguments:
-\begin{equation*}
-\bm{\mathrm{A}} = \lambda ab.aSb
-\end{equation*}
-
-A 'power' function to find $a^b$can also be defined, of astonishing simplicity:
-\begin{equation*}
-\bm{\mathrm{P}} = \lambda ba.ab
-\end{equation*}
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{P23}} &= (\lambda ab.ab)(\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda z.[\lambda ty.t(t(t(y)))]([\lambda ux.u(u(u(x)))]z))\\
-&= (\lambda z.[\lambda ty.t(t(t(y))][\lambda x.z(z(z(x)))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]y))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([\lambda x.z(z(z(x)))][z(z(z(y)))])])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([z(z(z(z(z(z(y))))))])])\\
-&= (\lambda z.[\lambda y.[z(z(z(z(z(z(z(z(z(y)))))))))]])\\
-&= \lambda zy.z(z(z(z(z(z(z(z(z(y)))))))))\\
-&= \bm{\mathrm{9}} = \bm{\mathrm{3^2}}
-\end{aligned}
-\end{gather*}
-
-\subsubsection{Logic and Conditions}
-
-Church defines functions to operate boolean logic - firstly representing True and False:
-
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{T}} &= \lambda ab.a,
-  & % seperation
-\bm{\mathrm{F}} &= \lambda ab.b
-\end{aligned}
-\end{equation*}
-These functions each take two arguments - the \textbf{T} function returns the first, while the \textbf{F} function returns the second.
-
-These concepts are the base of conditional logic in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
-For such operations, the concept of a 'pair' exists:
-\begin{equation*}
-\lambda x.xab
-\end{equation*}
-where $a$ and $b$ are functions. For a choice of an element from the pair, the argument of either \textbf{T} or \textbf{F} is provided:
-\begin{gather*}
-\begin{aligned}
-(\lambda x.xab)T &= a\\
-(\lambda x.xab)F &= b
-\end{aligned}
-\end{gather*}
-
-Functions representing boolean operations can also be defined:
-\begin{gather*}
-\begin{aligned}
-\vee &= \lambda xy.x\bm{\mathrm{T}}y\\
-\wedge &= \lambda xy.xy\bm{\mathrm{F}}\\
-\lnot &= \lambda x.x\bm{\mathrm{FT}} \\
-\veebar &= \lambda xy.x(\lnot y)y
-\end{aligned}
-\end{gather*}
-The derivation of such operations is not difficult to understand if one considers the truth tables for each operation, remembering that T selects the first and F selects the second argument.
-
-With the fundamental boolean system of our computational system in place, we must next construct conditionals. The first, and simplest, of these will check if a number is equal to zero:
-\begin{equation*}
-\bm{\mathrm{Z}} = \lambda x.x\bm{\mathrm{F\lnot F}}
-\end{equation*}
-To understand this somewhat less than trivial concept, remember that \textbf{F} applied to any single argument yields the identity function $\lambda x.x$, and that \textbf{0} applied to any two arguments yields only the second:
-\begin{equation*}
-\bm{0}ab = (\lambda sz.z)ab = b
-\end{equation*}
-From this, it easier to see how the function works. Firstly with \textbf{0}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{Z0}} &= (\lambda x.x\bm{\mathrm{f\lnot F}})\bm{0}\\
-&= \bm{\mathrm{0F\lnot F}}\\
-&= \bm{\mathrm{\lnot F}}\\
-&= \bm{\mathrm{T}}
-\end{aligned}
-\end{gather*}
-Secondly with \textbf{2}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{Z2}} &= (\lambda x.x\bm{\mathrm{f\lnot F}})\bm{2}\\
-&= \bm{\mathrm{2F\lnot F}}\\
-&= (\bm{\mathrm{F}}(\bm{\mathrm{F}}\lnot)) \bm{\mathrm{F}}\\
-&= (\bm{\mathrm{F}}(\lambda x.x))\bm{\mathrm{F}}\\
-&= (\lambda x.x)\bm{\mathrm{F}}\\
-&= \bm{\mathrm{F}} 
-\end{aligned}
-\end{gather*}
-
-However, in order to develop other conditional tests we will need a 'predecessor' function - something surprisingly difficult under lambda calculus.
-\subsubsection{Subtraction}
-
-The elusive predecessor function was created by Stephen Kleene, a student of Church's, and was something of a landmark in the development of $\lambda$-calculus.
-
-Firstly, the function transforms the pair (n, n-1) (the argument $p$) into the pair (n+1, n) (the new pair's elements are an increment and a copy of the first value respectively):
-\begin{equation*}
-\bm{\psi} = \lambda pc.c(S(pT))(pT)
-\end{equation*}
-To find the predecessor to $n$ therefore, we apply this function $n$ times to the pair (0, 0) and the pair (n, n-1) is formed, after which the second element can easily be selected.
-\begin{equation*}
-\bm{\mathrm{P}} = \lambda n.n \bm{\psi} (\lambda x.00) F 
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{P3}} &= (\lambda n.n [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}] \bm{\mathrm{F}}) [\lambda sz.s(s(s(z)))]\\
-&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
-&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda x.\bm{\mathrm{00}}]))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c(\bm{\mathrm{S}}[\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})([\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c\bm{\mathrm{10}}))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda c.c\bm{\mathrm{21}}]\bm{\mathrm{F}}\\
-&= [\lambda c.c\bm{\mathrm{32}} ])\bm{\mathrm{F}}\\
-&= \bm{\mathrm{2}}
-\end{aligned}
-\end{equation*}
-
-Of course now the subtraction function can be found (using \textbf{D} for difference):
-\begin{equation*}
-\bm{\mathrm{D}} = \lambda ab.bPa
-\end{equation*}
-Bearing in mind the predecessor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b>a$.
-\subsubsection{Further Conditional Logic}
-
-With this useful quirk of the \textbf{D} function, we can produce comparative logical operators:
-\begin{equation*}
-\begin{aligned}
-\bm{\leq} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}ab)
-  & % seperation
-\bm{\geq} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}ba)
-  \\
-\bm{<} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}a[\bm{\mathrm{S}}b])
-  &
-\bm{>} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}[\bm{\mathrm{S}}b]a)
-\end{aligned}
-\end{equation*}
-And through combination of these, we can create the equivalence and inequivalence operators (using $\bm{\doteq}$ for clarity from $=$:
-\begin{equation*}
-\begin{aligned}
-\bm{\doteq} &= \lambda ab.\wedge(\bm{\leq}ab)(\bm{\geq}ab)\\
-\bm{\neq} &= \lambda ab.\vee(\bm{<}ab)(\bm{>}ab)
-\end{aligned}
-\end{equation*}
-\subsubsection{Recursion}
-
-So far, Church's $\lambda$-Calculus is very close to the operation of a modern computation language.
-It has representation for boolean values, for conditional statements, for positive integers (signed integers can be expressed as a pair of a positive integer and a boolean for sign) and arithmetic, as well as set operations for booleans and comparators for integers - In fact, we are very close to our definition of computability save one thing.
-Continuity and repetition is one of the most significant aspects of computers, the power of this being the ability to transform a finite configuration into a potentially infinite result.
-This is done through one of the most remarkable functions in $\lambda$-Calculus, the recursor function:
-
-\begin{equation*}
-\bm{\mathrm{R}} = \lambda y.(\lambda x.y(xx))(\lambda x.y(xx)
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{R}}a &= (\lambda x.a(xx))[\lambda x.a(xx)]\\
-&= a([\lambda x.a(xx)][\lambda x.a(xx)]\\
-&= a(\bm{\mathrm{R}}a)
-\end{aligned}
-\end{equation*}
-Therefore, the \textbf{R} function applied to any function $a$ applies the function $a$ to the function \textbf{R} applied to $a$ - if substitution continues, an infinite series of nested $a$ functions is created; an infinite result is produced from a finite configuration.
-Of course we can create finites as well by halting the function - an example of this would be the factorial function, where \textbf{!}a = \textbf{M}a(\textbf{!}[\textbf{P}a]) and \textbf{!0} = \textbf{1}.
-Firstly, a recursive definition:
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{\xi}} &= (\lambda fa.\bm{\mathrm{Z}}a\bm{\mathrm{1}}[\bm{\mathrm{M}}a(f[\bm{\mathrm{P}}a])])\\
-\bm{!} &= \bm{\xi}!
-\end{aligned}
-\end{equation*}
-i.e.
-the factorial function is the $\bm{\xi}$ function with itself as the argument $f$.
-Unfortunately such a definition is illegal under $\lambda$-Calculus as strictly no functions have names - this is where the function \textbf{R} comes into play.
-To find the factorial of \textbf{3}:
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{R\xi 3}} &= \bm{\mathrm{\xi}}(\bm{\mathrm{R\xi}})\bm{\mathrm{3}}\\
-&= \bm{\mathrm{Z30}}[\bm{\mathrm{M3}}([\bm{\mathrm{R\xi}}][\bm{\mathrm{P3}}])\\
-&= \bm{\mathrm{M3}}(\bm{\mathrm{R\xi}}\bm{2})]\\
-&= \bm{\mathrm{M3}}(\bm{\mathrm{M2}}(\bm{\mathrm{M11}}))\\
-&= \bm{\mathrm{6}}
-\end{aligned}
-\end{equation*}
-The recursive identity \textbf{R} allows for \textbf{R}$\bm{\xi}$ to be applied as the first argument to the $\bm{\xi}$ function - as a result, the procedure is repeated for \textbf{2} and \textbf{1}, before stopping at \textbf{0}.
-To simplify, the factorial function:
-\begin{equation*}
-\bm{!} = \lambda x.\bm{\mathrm{R\xi}}x
-\end{equation*}
-
-\subsubsection{Conclusion}
-Our brief stroll through the key aspects of $\lambda$-Calculus is complete.
-We have defined that every basic necessary concept in a common programming language can be defined through the use of two simple axioms - that of the concept of functions, and the operation of substitution.
-$\lambda$-Calculus was described by Church as an 'effectively calculable' system, in that it could perform any calculable calculation.
-In more popular terms, it is Turing-complete - we will look at what this is and why this is the case later on in the project.
-However, it is clear to see that the Calculus is able to simulate many aspects of the computer - data storage with pairs (pairs of pairs can be used for larger capacity), conditionals and booleans, integers and arithmetic and, finally, the ability to be continuous (circular) from a finite configuration.
-This is our first definition of a 'computer', and therefore any mechanical or axiomatic system which is able to simulate $\lambda$-calculus is also a 'computer', and shall also be called 'effectively calculable'.
+Turing woo
 \end{document}

### 2016-12-08 Draft 2/Section 2 - Turing Machines.tex
Basic Turing Machines
Intro to Turing, 101010 machine (both types), 1011011101 machine (no
explanation), .gitignore

@@
 \documentclass[Master.tex]{subfiles}
+
+\usepackage{multirow, bigdelim}
+\usepackage{hhline}
+\usepackage{tabu}	
+\usepackage[bb=boondox]{mathalfa}
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath}
+
+\renewcommand{\arraystretch}{1.5}
 
@@
 
-Turing woo
+At roughly the same time, the English Mathematician Alan Turing was constructing a method to achieve the same goal, but in an entirely different way.
+Rather than building an incredibly simple axiomatic system to illustrate Effective Computability, the concept used was far more practical, and far closer to the mechanical computers that implemented this idea.
+
+The Turing Machine, or Finite State Machine (FSM), is composed of two parts: firstly, an ordered set of \textit{squares} of infinite length known as \textit{tape}, with a cursor at a certain point on this list, in which \textit{symbols} can be written for future use or output (much like random access memory on a modern computer); secondly, a set of states known as \textit{m-configurations}, each of which contain operations to be performed on the tape, and the \textit{m-configuration} that the FSM moves to.
+An example description of such a set would be:
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behaviour}} \\
+    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \hhline{====}
+    \multirow{1}{*}{$\mathbb{A}$} & None & P0, R & $\mathbb{B}$ \\
+    \hhline{----}
+    \multirow{1}{*}{$\mathbb{B}$} & None & R        & $\mathbb{C}$ \\
+    \hhline{----}
+    \multirow{1}{*}{$\mathbb{C}$} & None & P1, R & $\mathbb{D}$ \\
+    \hhline{----}
+    \multirow{1}{*}{$\mathbb{D}$} & None & R        & $\mathbb{A}$ \\
+\end{tabu}
+
+\noindent $\Rightarrow \mathbb{A}$
+
+\medskip
+
+This table format shall be used to describe FSM configurations.
+Firstly, the final line describes the starting \textit{m-configuration}.
+When the machine begins an interation on any one of these \textit{m-configurations}, it first checks if the symbol aspect of the configuration is equal to the \textit{symbol} currently under the cursor on the tape.
+If this condition is met, the operations are carried out - P\textit{n} for any symbol \textit{n} prints the symbol \textit{n} on the tape under the cursor; E erases any symbol under the cursor; L moves the cursor to the left; R moves the cursor to the right.
+When these operations are completed, the \textit{m-configuration} is set to that described in the last column.
+The FSM then moves to the next iteration.
+
+In this case, it is not difficult to see that as the machine runs, it leaves a sequence of alternating 0s and 1s on every other square on the tape.
+However, with the use of the \textit{symbol} condition, this table can be simplified:
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behaviour}} \\
+    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \hhline{====}
+    \multirow{3}{*}{$\mathbb{A}$} & None & P0          & $\mathbb{A}$ \\
+                                    & 0       & R, R, P1 & $\mathbb{A}$ \\ 
+                                    & 1       & R, R, P0 & $\mathbb{A}$ \\ 
+\end{tabu}
+
+\noindent $\Rightarrow \mathbb{A}$
+
+\medskip
+
+It is again not difficult to see that this produces the same output as the previous machine, but this time using only one \textit{m-configuration}.
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behaviour}} \\
+    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \hhline{====}
+    \multirow{1}{*}{$\mathbb{Q}$} & Any & Pe, R Pe, R,  P0, R, R, P0, L, L   & $\mathbb{A}$ \\
+    \hhline{----}
+    \multirow{2}{*}{$\mathbb{A}$} & 1        & R, Px, L, L, L                                     & $\mathbb{A}$ \\
+                                                        & 0        &                                                           & $\mathbb{B}$ \\
+    \hhline{----}
+    \multirow{2}{*}{$\mathbb{B}$} & Any   & R, R                                                  & $\mathbb{B}$ \\
+                                                         & None & P1, L                                                 & $\mathbb{C}$ \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{C}$} & x        & E, R                                                  & $\mathbb{B}$ \\
+                                                         & e        & R                                                      & $\mathbb{D}$ \\
+                                                         & None & L, L                                                   & $\mathbb{C}$ \\
+    \hhline{----}
+    \multirow{2}{*}{$\mathbb{D}$} & Any    & R, R                                                  & $\mathbb{D}$ \\
+                                                          & None & P0, L, L                                            & $\mathbb{A}$ \\
+\end{tabu}
+
+\noindent $\Rightarrow \mathbb{Q}$
+
+\medskip
 \end{document}

### 2016-12-12 Draft 2/Section 2 - Turing Machines.tex
Misc changes
Ngl thats the best you're getting

@@
 \documentclass[Master.tex]{subfiles}
-
-\usepackage{multirow, bigdelim}
-\usepackage{hhline}
-\usepackage{tabu}	
-\usepackage[bb=boondox]{mathalfa}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
 
@@
 \medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behaviour}} \\
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
     \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
@@
 Firstly, the final line describes the starting \textit{m-configuration}.
-When the machine begins an interation on any one of these \textit{m-configurations}, it first checks if the symbol aspect of the configuration is equal to the \textit{symbol} currently under the cursor on the tape.
+When the machine begins an iteration on any one of these \textit{m-configurations}, it first checks if the symbol aspect of the configuration is equal to the \textit{symbol} currently under the cursor on the tape.
 If this condition is met, the operations are carried out - P\textit{n} for any symbol \textit{n} prints the symbol \textit{n} on the tape under the cursor; E erases any symbol under the cursor; L moves the cursor to the left; R moves the cursor to the right.
@@
 \medskip
+
+blah
+
+\begin{equation*}
+\begin{aligned}
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \underset{\uparrow}{\cdot}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ x\ 0} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{x}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+\end{aligned}
+\end{equation*}
+
+blah
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \hhline{====}
+    \multirow{2}{*}{$\mathbb{f}$(\textfrak{C},\textfrak{E},\textit{a})}   & e              & L & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+                                                                          & Not e          & L & $\mathbb{f}$(\textfrak{C},\textfrak{E},\textit{a})   \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a})} & \textit{a}     &   & \textfrak{C} \\
+                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+                                                                          & None           & R & $\mathbb{f}_2$(\textfrak{C},\textfrak{E},\textit{a}) \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{f}_2$(\textfrak{C},\textfrak{E},\textit{a})} & \textit{a}     &   & \textfrak{C} \\
+                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+                                                                          & None           & R & \textfrak{E} 
+\end{tabu}
+
+\medskip
+
+blah
 \end{document}

### 2017-01-12 Draft 2/Section 2 - Turing Machines.tex
Loooooads of nice nice changes
Cba to explain I havn't been commiting regularly

--- 2016-12-08 Draft 2/Section 2 - Turing Machines.tex
@@
 
-\usepackage{multirow, bigdelim}
-\usepackage{hhline}
-\usepackage{tabu}	
-\usepackage[bb=boondox]{mathalfa}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
+\crefname{section}{§}{§§}
+\Crefname{section}{§}{§§}
 
@@
 
-The Turing Machine, or Finite State Machine (FSM), is composed of two parts: firstly, an ordered set of \textit{squares} of infinite length known as \textit{tape}, with a cursor at a certain point on this list, in which \textit{symbols} can be written for future use or output (much like random access memory on a modern computer); secondly, a set of states known as \textit{m-configurations}, each of which contain operations to be performed on the tape, and the \textit{m-configuration} that the FSM moves to.
+\subsubsection{Examples of simple Finite State Machines}\label{sec:FSMintro}
+The Turing Machine, or Finite State Machine (FSM), is composed of two parts: firstly, an ordered set of \textit{squares} of infinite length known as \textit{tape}, with a cursor at a certain point on this list, in which \textit{symbols} can be written for future use or output (much like random access memory on a modern computer); secondly, a set of states known as \textit{m}-configurations, each of which contain operations to be performed on the tape, and the \textit{m-configuration} that the FSM moves to.
 An example description of such a set would be:
@@
 This table format shall be used to describe FSM configurations.
-Firstly, the final line describes the starting \textit{m-configuration}.
-When the machine begins an interation on any one of these \textit{m-configurations}, it first checks if the symbol aspect of the configuration is equal to the \textit{symbol} currently under the cursor on the tape.
+Firstly, the final line describes the starting \textit{m}-configuration.
+When the machine begins an iteration on any one of these \textit{m}-configurations, it first checks if the symbol aspect of the configuration is equal to the \textit{symbol} currently under the cursor on the tape.
 If this condition is met, the operations are carried out - P\textit{n} for any symbol \textit{n} prints the symbol \textit{n} on the tape under the cursor; E erases any symbol under the cursor; L moves the cursor to the left; R moves the cursor to the right.
-When these operations are completed, the \textit{m-configuration} is set to that described in the last column.
+When these operations are completed, the \textit{m}-configuration is set to that described in the last column.
 The FSM then moves to the next iteration.
@@
 
+An example of a more complex FSM is shown below, which generates the sequence \texttt{010110111011110111110...} again on alternate squares, beginning at the fifth square.
+
 \medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behaviour}} \\
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
     \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
@@
 \medskip
+
+The operation of such a machine is significantly more complex than the earlier one.
+Key to the operation of this machine is the fact that squares are paired into primary squares or \textit{p}-squares (odd-numbered squares) on which the symbols of the output sequence are printed.
+Only the symbols \texttt{0} and \texttt{1} will be printed on these squares, and printed symbols will never be erased.
+To the right of each \textit{p}-square is a secondary square, or \textit{s}-square (an even-numbered square).
+These squares will either be left empty or will contain a 'marker' symbol, which marks the symbol on the \textit{p}-square to the left.
+These symbols can be erased and overwritten, and are not part of the output sequence.
+Only one \textit{s}-square is needed to contain multiple markers, or more descriptive markers for a single \textit{p}-square, as this can be achieved with a sufficiently large array of marker symbols.
+
+This machine operates by first printing the symbols \texttt{e e 0} at the start of the tape, before printing the first \texttt{0} of the sequence on the fifth square, finishing on the third square and moving to state $\mathbb{A}$.
+(in future I shall represent this finishing state as $\rightarrow \mathbb{A}$).
+
+If $\mathbb{A}$ is triggered, every \texttt{1} consecutively to the left of the cursor inclusively will be marked with \texttt{x}, $\rightarrow \mathbb{B}$.
+
+If $\mathbb{B}$ is triggered, the symbol \texttt{1} is appended to the output sequence, $\rightarrow \mathbb{C}$.
+
+If $\mathbb{C}$ is triggered, the cursor moves leftwards through the markers: if an \texttt{x} is found it is erased and $\rightarrow \mathbb{B}$; if the cursor reaches the beginning (an \texttt{e} is found) $\rightarrow \mathbb{D}$.
+
+If $\mathbb{D}$ is triggered, the symbol \texttt{0} is appended to the output sequence, the cursor moves to the previous \textit{p}-square and $\rightarrow \mathbb{A}$.
+
+The workings of this algorithm are mostly in states $\mathbb{A}$ and $\mathbb{C}$: after the \texttt{0} is drawn $\mathbb{A}$ draws a number of \texttt{x} symbols equal to the previous number of \texttt{1} symbols drawn.
+$\mathbb{C}$ triggers $\mathbb{B}$ a number of times equal to the number of found \texttt{x} symbols before drawing a \texttt{0} - as $\mathbb{B}$ has already been triggered once, a number of \texttt{1} symbols will be drawn which is one more than the previous number drawn.
+For clarity in the comprehension of this somewhat abstract algorithm, some of the early states have been listed on the next page.
+Empty squares are represented by dots ($\cdot$) and the tape states continue in columns.
+An ellipsis marks the omission of a set of states which are implied or trivial.
+
+\begin{equation*}
+\begin{aligned}
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{A}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 1\ x\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \underset{\uparrow}{\cdot}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 1\ x\ 0} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ x\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ x\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \underset{\uparrow}{x}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{A}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{A}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ x\ 0} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{x}\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{x}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{D}\\
+&...& &...&\\
+&\mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{D}\\
+\end{aligned}
+\end{equation*}
+
+\clearpage
+
+It is clear from this example that the operation of the FSM is very different from that of an ordinary computer.
+However, the core components are still mostly present - conditionals in the form of the symbol tests in the second column, variables in the form of markers, and continuity and looping when a state triggers itself - a form of recursion.
+The end result is the same - a solution is produced in the form of the computable sequence written on the \textit{p}-squares, and the machine can continue this sequence without halting indefinitely.
+Unfortunately, the operation of this machine is somewhat complex and involved.
+To simplify the usage of the FSM, we will introduce a type of function for the FSM.
+
+\subsubsection{\textit{M}-functions}\label{sec:mfunctions}
+
+\textit{M}-functions are effectively an extension of \textit{m}-configurations.
+They are described by a lowercase letter and a set of arguments contained in brackets - arguments in gothic script refer to \textit{m}-configurations (or other \textit{m}-functions), and arguments in italics refer to symbols.
+When an \textit{m}-function is triggered, the italic and gothic symbols in the description are substituted by the supplied arguments (much like in $\lambda$-calculus).
+An example of an \textit{m}-function would be the function $\mathbb{f}$ below:
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \hhline{====}
+    \multirow{2}{*}{$\mathbb{f}$(\textfrak{C},\textfrak{E},\textit{a})}   & e              & L & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+                                                                          & Not e          & L & $\mathbb{f}$(\textfrak{C},\textfrak{E},\textit{a})   \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a})} & \textit{a}     &   & \textfrak{C} \\
+                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+                                                                          & None           & R & $\mathbb{f}_2$(\textfrak{C},\textfrak{E},\textit{a}) \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{f}_2$(\textfrak{C},\textfrak{E},\textit{a})} & \textit{a}     &   & \textfrak{C} \\
+                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+                                                                          & None           & R & \textfrak{E} 
+\end{tabu}
+
+\medskip
+
+The function $\mathbb{f}$ takes three arguments - the \textit{m}-configurations \textfrak{C} and \textfrak{E} and the symbol \textit{a}.
+It is not difficult to see that if $\rightarrow \mathbb{f}$($\mathbb{A}$,$\mathbb{B}$,x) the cursor would trigger $\mathbb{A}$ at the leftmost occurrence of \texttt{x}.
+If no symbols \texttt{x} were found, \textfrak{E} would be triggered on the marker of the first empty \textit{p}-square.
+
+The use of \textit{m}-functions greatly simplifies the table descriptions, as certain operations are common to many machines.
+Of course, any table description that includes or refers to \textit{m}-functions can be written as an ordinary table as described in \cref{sec:FSMintro}.
+This is possible because of the finite nature of both symbols and \textit{m}-configurations; simply by listing in separate rows under the same \textit{m}-configuration every permutation of symbols and \textit{m}-configurations that the function could possibly take substituted in.
+
+\subsubsection{Common Operations}
+
+In this section I will define a set of common \textit{m}-functions that will be used regularly in future.
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \hhline{====}
+    $\mathbb{e}$(\textfrak{C},\textfrak{E},\textit{a}) & - & - & $\mathbb{f}$($\mathbb{e}_1$(\textfrak{C}),\textfrak{E},\textit{a}) & \multirow{2}{80pt}{Erases first occurrence of symbol \textit{a}} \\
+    \hhline{----}
+    $\mathbb{e}_1$(\textfrak{C}) & - & E & \textfrak{C}\\
+    \hhline{====}
+    $\mathbb{l}$(\textfrak{C}) & - & L & \textfrak{C} \\
+    \hhline{----}
+    $\mathbb{r}$(\textfrak{C}) & - & R & \textfrak{C} \\
+    \hhline{====}
+    $\mathbb{fl}$(\textfrak{C}, \textfrak{e}, \textit{a}) & - & - & $\mathbb{f}$($\mathbb{l}$(\textfrak{C}),\textfrak{E},\textit{a}) \\
+    \hhline{----}
+    $\mathbb{fr}$(\textfrak{C}, \textfrak{e}, \textit{a}) & - & - & $\mathbb{f}$($\mathbb{r}$(\textfrak{C}),\textfrak{E},\textit{a}) \\
+    \hhline{====}
+    $\mathbb{p0}$(\textfrak{C}) & - & P0 & \textfrak{C} \\
+    \hhline{----}
+    $\mathbb{p1}$(\textfrak{C}) & - & P1 & \textfrak{C} \\
+    \hhline{====}
+    $\mathbb{n}$(\textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$($\mathbb{n}_1$(\textfrak{C}),\textfrak{E},e) \\
+    \hhline{----}
+    \multirow{2}{*}{$\mathbb{n}_1$(\textfrak{C})} & Any  & RR & $\mathbb{n}_1$(\textfrak{C}) \\
+                                                  & None & - & \textfrak{C} \\
+    \hhline{====}
+\end{tabu}
+
+\medskip
+
+\subsubsection{Data Structures and Pointers}
+
+At this point, the similarity between Turing machines and modern computers becomes very clear.
+The machine is able to store more complex information, from integers to strings of characters to images, as binary sequences of \textit{p}-square \texttt{0}s and \texttt{1}s - these shall be stored on the tape as memory.
+The first data structure we shall define is the simple boolean - only 1 bit (1 \textit{p}-square) long.
+In order to identify these sequences on the tape as booleans, we shall mark the first character of the boolean with an identifier (we shall call these pointers) unique to that boolean variable - for example the symbol \texttt{\textbf{B}myvar} (bear in mind this is one symbol, not six) would mark a boolean named \textit{myvar}.
+Let us define an \textit{m}-function to deal with assignments for the boolean type:
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \hhline{====}
+    $\mathbb{\mathbf{b}copy}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E}),\textfrak{E},\textit{r}) \\
+    \hhline{----}
+    \multirow{2}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
+                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
+\end{tabu}
+
+\medskip
+
 \end{document}

### 2017-01-12 Draft 2/Section 2 - Turing Machines.tex
I have no idea what this is

--- 2016-12-08 Draft 2/Section 2 - Turing Machines.tex
@@
  \documentclass[Master.tex]{subfiles}
-
-\usepackage{multirow, bigdelim}
-\usepackage{hhline}
-\usepackage{tabu}	
-\usepackage[bb=boondox]{mathalfa}
-\usepackage[utf8]{inputenc}
-\usepackage{amsmath}
 
@@
 \medskip
+
+blah
+
+\begin{equation*}
+\begin{aligned}
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \underset{\uparrow}{\cdot}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ x\ 0} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{x}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \underset{\uparrow}{\cdot}\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \underset{\uparrow}{\cdot}\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \underset{\uparrow}{\cdot}\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{D}\\
+\end{aligned}
+\end{equation*}
+
+blah
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \hhline{====}
+    \multirow{2}{*}{$\mathbb{f}$(\textfrak{C},\textfrak{E},\textit{a})}   & e              & L & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+                                                                          & Not e          & L & $\mathbb{f}$(\textfrak{C},\textfrak{E},\textit{a})   \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a})} & \textit{a}     &   & \textfrak{C} \\
+                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+                                                                          & None           & R & $\mathbb{f}_2$(\textfrak{C},\textfrak{E},\textit{a}) \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{f}_2$(\textfrak{C},\textfrak{E},\textit{a})} & \textit{a}     &   & \textfrak{C} \\
+                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+                                                                          & None           & R & \textfrak{E} 
+\end{tabu}
+
+\medskip
+
+blah
 \end{document}

### 2017-01-26 Draft 2/Section 2 - Turing Machines.tex
Changes from papeeria

--- 2017-01-12 Draft 2/Section 2 - Turing Machines.tex
@@
     \hhline{====}
-    $\mathbb{l}$(\textfrak{C}) & - & L & \textfrak{C} \\
+    $\mathbb{l}$(\textfrak{C}) & - & L & \textfrak{C} & Moves cursor left\\
     \hhline{----}
-    $\mathbb{r}$(\textfrak{C}) & - & R & \textfrak{C} \\
+    $\mathbb{r}$(\textfrak{C}) & - & R & \textfrak{C} & Moves cursor right\\
     \hhline{====}
-    $\mathbb{fl}$(\textfrak{C}, \textfrak{e}, \textit{a}) & - & - & $\mathbb{f}$($\mathbb{l}$(\textfrak{C}),\textfrak{E},\textit{a}) \\
+    $\mathbb{fl}$(\textfrak{C}, \textfrak{e}, \textit{a}) & - & - & $\mathbb{f}$($\mathbb{l}$(\textfrak{C}),\textfrak{E},\textit{a}) & Moves to left of \textit{a} \\
     \hhline{----}
-    $\mathbb{fr}$(\textfrak{C}, \textfrak{e}, \textit{a}) & - & - & $\mathbb{f}$($\mathbb{r}$(\textfrak{C}),\textfrak{E},\textit{a}) \\
+    $\mathbb{fr}$(\textfrak{C}, \textfrak{e}, \textit{a}) & - & - & $\mathbb{f}$($\mathbb{r}$(\textfrak{C}),\textfrak{E},\textit{a}) & Moves to right of \textit{a} \\
     \hhline{====}
-    $\mathbb{p0}$(\textfrak{C}) & - & P0 & \textfrak{C} \\
+    $\mathbb{p0}$(\textfrak{C}) & - & P0 & \textfrak{C} & Prints \texttt{0} \\
     \hhline{----}
-    $\mathbb{p1}$(\textfrak{C}) & - & P1 & \textfrak{C} \\
+    $\mathbb{p1}$(\textfrak{C}) & - & P1 & \textfrak{C} & Prints \texttt{0} \\
     \hhline{====}
-    $\mathbb{n}$(\textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$($\mathbb{n}_1$(\textfrak{C}),\textfrak{E},e) \\
+    $\mathbb{n}$(\textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$($\mathbb{n}_1$(\textfrak{C}),\textfrak{E},e) & \multirow{3}{80pt}{Moves to first empty (final) \textit{p}-square} \\
     \hhline{----}
-    \multirow{2}{*}{$\mathbb{n}_1$(\textfrak{C})} & Any  & RR & $\mathbb{n}_1$(\textfrak{C}) \\
+    \multirow{2}{*}{$\mathbb{n}_1$(\textfrak{C})} & Any  & R, R & $\mathbb{n}_1$(\textfrak{C}) \\
                                                   & None & - & \textfrak{C} \\
@@
 In order to identify these sequences on the tape as booleans, we shall mark the first character of the boolean with an identifier (we shall call these pointers) unique to that boolean variable - for example the symbol \texttt{\textbf{B}myvar} (bear in mind this is one symbol, not six) would mark a boolean named \textit{myvar}.
-Let us define an \textit{m}-function to deal with assignments for the boolean type:
+Let us define some \textit{m}-functions to define and assign values to variables of the boolean type:
 
@@
     \hhline{====}
+    $\mathbb{\mathbf{b}def}$(\textit{p},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{n}$($\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C}),\textfrak{E}) \\
+    $\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C})   & - & P0, R, P\textit{p}, L & \textfrak{C} \\
+    \hhline{====}
     $\mathbb{\mathbf{b}copy}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E}),\textfrak{E},\textit{r}) \\
     \hhline{----}
-    \multirow{2}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
+    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
                                                                                        & 1 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
+                                                                                       & other, none & - & \textfrak{E} \\
 \end{tabu}
@@
 
+The first takes one pointer \textit{p}, finds the first free bit (\textit{p}-square) on the tape, writes the dummy value of \texttt{0} to it and marks it with \textit{p}.
+This method of assumption - appending
+
 \end{document}

### 2017-01-26 Draft 2/Section 2 - Turing Machines.tex
Boolean not, description of bolean copy

@@
 The first takes one pointer \textit{p}, finds the first free bit (\textit{p}-square) on the tape, writes the dummy value of \texttt{0} to it and marks it with \textit{p}.
-This method of assumption - appending
+This method of appendng makes the assumption that no \textit{p}-squares are left empty across the used tape - in order to preserve this, we shall only append to \textit{p}-squares directly at the end of the used tape, and we shall never erase \textit{p}-squares.
+The second very simply finds the bit at pointer \textit{r}, and branches to write either \texttt{0} or \texttt{1} at the bit at the pointer \textit{w}
+
+Next, similar to as we did in $\lambda$-calculus, we shall define boolean operations.
+Every operation will take one or many pointers as arguments, and write the evaluated result to another given pointer.
+The simplest of these we can create is the negator:
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    $\mathbb{\mathbf{b}neg}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
+                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
+                                                                                       & other, none & - & \textfrak{E} \\
+\end{tabu}
+
+\medskip
+
+This is almost identical to the copying function, but inverting the written symbols.56
 

### 2017-01-29 Draft 2/Section 1 - Lambda Calculus.tex
Added Turing Machines section
(empty); Fixed numbering
Corrections on Sec1
Quick corrections to Factorial function

@@
 \begin{document}
-\pagenumbering{roman}
 
@@
 \begin{equation*}
-\bm{\mathrm{A}} = \lambda ab.aSb
+\bm{\mathrm{A}} = \lambda ab.a\bm{\mathrm{S}}b
 \end{equation*}
@@
 \begin{aligned}
-(\lambda x.xab)T &= a\\
-(\lambda x.xab)F &= b
+(\lambda x.xab)\bm{\mathrm{T}} &= a\\
+(\lambda x.xab)\bm{\mathrm{F}} &= b
 \end{aligned}
@@
 \begin{equation*}
-\bm{\psi} = \lambda pc.c(S(pT))(pT)
+\bm{\psi} = \lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})
 \end{equation*}
@@
 \begin{equation*}
-\bm{\mathrm{P}} = \lambda n.n \bm{\psi} (\lambda x.00) F 
+\bm{\mathrm{P}} = \lambda n.n \bm{\psi} (\lambda x.\bm{\mathrm{00}}) \bm{\mathrm{F}} 
 \end{equation*}
@@
 \begin{equation*}
-\bm{\mathrm{D}} = \lambda ab.bPa
+\bm{\mathrm{D}} = \lambda ab.b\bm{\mathrm{P}}a
 \end{equation*}
@@
 \begin{equation*}
-\bm{\mathrm{R}} = \lambda y.(\lambda x.y(xx))(\lambda x.y(xx)
+\bm{\mathrm{R}} = \lambda y.(\lambda x.y(xx))(\lambda x.y(xx))
 \end{equation*}
@@
 \bm{\mathrm{R}}a &= (\lambda x.a(xx))[\lambda x.a(xx)]\\
-&= a([\lambda x.a(xx)][\lambda x.a(xx)]\\
+&= a([\lambda x.a(xx)][\lambda x.a(xx)])\\
 &= a(\bm{\mathrm{R}}a)
@@
 \begin{aligned}
-\bm{\mathrm{\xi}} &= (\lambda fa.\bm{\mathrm{Z}}a\bm{\mathrm{1}}[\bm{\mathrm{M}}a(f[\bm{\mathrm{P}}a])])\\
+\bm{\mathrm{\xi}} &= \lambda fa.\bm{\mathrm{Z}}a\bm{\mathrm{1}}[\bm{\mathrm{M}}a(f[\bm{\mathrm{P}}a])]\\
 \bm{!} &= \bm{\xi}!
@@
 \bm{\mathrm{R\xi 3}} &= \bm{\mathrm{\xi}}(\bm{\mathrm{R\xi}})\bm{\mathrm{3}}\\
-&= \bm{\mathrm{Z30}}[\bm{\mathrm{M3}}([\bm{\mathrm{R\xi}}][\bm{\mathrm{P3}}])\\
-&= \bm{\mathrm{M3}}(\bm{\mathrm{R\xi}}\bm{2})]\\
+&= \bm{\mathrm{Z31}}[\bm{\mathrm{M3}}([\bm{\mathrm{R\xi}}][\bm{\mathrm{P3}}])]\\
+&= \bm{\mathrm{M3}}(\bm{\mathrm{R\xi}}\bm{2})\\
 &= \bm{\mathrm{M3}}(\bm{\mathrm{M2}}(\bm{\mathrm{M11}}))\\
@@
 \end{equation*}
-The recursive identity \textbf{R} allows for \textbf{R}$\bm{\xi}$ to be applied as the first argument to the $\bm{\xi}$ function - as a result, the procedure is repeated for \textbf{2} and \textbf{1}, before stopping at \textbf{0}.
+The recursive identity \textbf{R} allows for \textbf{R}$\bm{\xi}$ to be applied as the first argument to the $\bm{\xi}$ function - as a result, the procedure also processes \textbf{2} and \textbf{1}, before stopping at \textbf{0} (which produces simply \textbf{1}.
 To simplify, the factorial function:

### 2017-02-02 Draft 2/Section 2 - Turing Machines.tex
Added remaining boolean conditions, and conditional function

@@
                                                                                        & 1 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
-                                                                                       & other, none & - & \textfrak{E} \\
+                                                                                       & other & - & \textfrak{E} \\
 \end{tabu}
@@
 This method of appendng makes the assumption that no \textit{p}-squares are left empty across the used tape - in order to preserve this, we shall only append to \textit{p}-squares directly at the end of the used tape, and we shall never erase \textit{p}-squares.
-The second very simply finds the bit at pointer \textit{r}, and branches to write either \texttt{0} or \texttt{1} at the bit at the pointer \textit{w}
+The second very simply finds the bit at pointer \textit{r}, and branches to write either \texttt{0} or \texttt{1} at the bit at the pointer \textit{w}.
 
-Next, similar to as we did in $\lambda$-calculus, we shall define boolean operations.
+\subsubsection{Boolean Operations}
+
+As we did in $\lambda$-calculus, we shall define boolean operations.
 Every operation will take one or many pointers as arguments, and write the evaluated result to another given pointer.
@@
                                                                                        & 1 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
-                                                                                       & other, none & - & \textfrak{E} \\
+                                                                                       & other & - & \textfrak{E} \\
+\end{tabu}
+
+\medskip
+This is almost identical to the copying function, but inverting the written symbols. The definition of the remaining logical functions based on truth tables now becomes simple:
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    $\mathbb{\mathbf{b}and}$(\textit{a},\textit{b},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}and}_1$(\textit{b},\textit{w},\textfrak{C}),\textfrak{E}) \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b},\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
+                                                                                       & 1 & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
+                                                                                       & other & - & \textfrak{E} \\
+    \hhline{====}
+    $\mathbb{\mathbf{b}or}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}or}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{\mathbf{b}or}_1$(\textit{w},\textfrak{C},\textfrak{E})} 
+                                                                                       & 0 & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
+                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
+                                                                                       & other & - & \textfrak{E} \\
+    \hhline{====}
+    $\mathbb{\mathbf{b}xor}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}xor}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{\mathbf{b}xor}_1$(\textit{w},\textfrak{C},\textfrak{E})} 
+                                                                                       & 0 & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
+                                                                                       & 1 & - &  $\mathbb{\mathbf{b}not}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
+                                                                                       & other & - & \textfrak{E} \\
+\end{tabu}
+
+\medskip
+In each of these, the first argument \textit{a} is observed, and an action which either writes a \texttt{1} or \texttt{0}, or copies or negates from \textit{b} depending on the truth tables, in a very similar manner to $\lambda$-calculus.
+Gradually, the cryptic and simplified language of Finite State Machines is yielding results similar to that of a computer.
+
+\subsubsection{Simplified Configurations}
+
+As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions.
+We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, and $\mathbb{p1}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multirow{2}{*}{$\mathbb{if}$(\textit{c},\textfrak{I},\textfrak{O})} 
+                                                                                       & \textit{c} & - & \textfrak{I} \\
+                                                                                       & other & - & \textfrak{O} \\ 
+    \hhline{====}
+    $\mathbb{ifp}$(\textit{r},\textit{c},\textfrak{I},\textfrak{O}, \textfrak{E}) & - & - & $\mathbb{fl}$($\mathbb{if}$(\textit{c}, \textfrak{I}, \textfrak{O}), \textfrak{E}, \textit{r}) \\
 \end{tabu}
@@
 
-This is almost identical to the copying function, but inverting the written symbols.56
+Since we have now entirely defined the operation of the machine in terms of functions, we no longer have any need for tables.
 

### 2017-02-03 Draft 2/Section 2 - Turing Machines.tex
Tiny description
Added recursive syntax

@@
 Gradually, the cryptic and simplified language of Finite State Machines is yielding results similar to that of a computer.
-
-\subsubsection{Simplified Configurations}
-
 As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions.
@@
 
-Since we have now entirely defined the operation of the machine in terms of functions, we no longer have any need for tables.
+The function $\mathbb{if}$ takes a symbol argument, which is compared to the symbol under the cursor - if they are the same, the machine $\rightarrow \mathbb{I}$; if not the machine $\rightarrow \mathbb{O}$.
+Since we have now entirely defined the operation of the machine in terms of functions (as loops can be done with recursion), we no longer have any need for tables - in effect, we have built a purely functional programming language in terms of a simple finite state machine.
+Now, in order to define more \textit{m}-functions we no longer have to write a table:
 
+\begin{lstlisting}
+ifp(r,c,I,O,E) = fl(
+    if(c,
+        I,
+        O
+    ),
+    E,
+    r
+)
+\end{lstlisting}
+
+Admittedly not the cleanest syntax, but still a simple one.
 \end{document}

### 2017-02-09 Draft 2/Section 2 - Turing Machines.tex
Clarified earlier tables
Added consistency over \texttt{s} for all symbols, and moved all continuity and exception functions to last two arguments. Begun work on Scripting language.

@@
     \hhline{====}
-    \multirow{1}{*}{$\mathbb{A}$} & None & P0, R & $\mathbb{B}$ \\
+    \multirow{1}{*}{$\mathbb{A}$} & None & P\texttt{0}, R & $\mathbb{B}$ \\
     \hhline{----}
@@
     \hhline{----}
-    \multirow{1}{*}{$\mathbb{C}$} & None & P1, R & $\mathbb{D}$ \\
+    \multirow{1}{*}{$\mathbb{C}$} & None & P\texttt{1}, R & $\mathbb{D}$ \\
     \hhline{----}
@@
     \hhline{====}
-    \multirow{3}{*}{$\mathbb{A}$} & None & P0       & $\mathbb{A}$ \\
-                                  & 0    & R, R, P1 & $\mathbb{A}$ \\ 
-                                  & 1    & R, R, P0 & $\mathbb{A}$ \\ 
+    \multirow{3}{*}{$\mathbb{A}$} & None & P\texttt{0}       & $\mathbb{A}$ \\
+                                  & \texttt{0}    & R, R, P\texttt{1} & $\mathbb{A}$ \\ 
+                                  & \texttt{1}    & R, R, P\texttt{0} & $\mathbb{A}$ \\ 
 \end{tabu}
@@
     \hhline{====}
-    \multirow{1}{*}{$\mathbb{Q}$} & Any  & Pe, R Pe, R,  P0, R, R, P0, L, L & $\mathbb{A}$ \\
+    \multirow{1}{*}{$\mathbb{Q}$} & Any        & P\texttt{e}, R P\texttt{e}, R,  P\texttt{e}, R, R, P\texttt{0}, L, L & $\mathbb{A}$ \\
     \hhline{----}
-    \multirow{2}{*}{$\mathbb{A}$} & 1    & R, Px, L, L, L                   & $\mathbb{A}$ \\
-                                  & 0    &                                  & $\mathbb{B}$ \\
+    \multirow{2}{*}{$\mathbb{A}$} & \texttt{1} & R, P\texttt{x}, L, L, L                   & $\mathbb{A}$ \\
+                                  & \texttt{1} &                                  & $\mathbb{B}$ \\
     \hhline{----}
     \multirow{2}{*}{$\mathbb{B}$} & Any        & R, R                             & $\mathbb{B}$ \\
-                                  & None & P1, L                            & $\mathbb{C}$ \\
+                                  & None       & P\texttt{1}, L                            & $\mathbb{C}$ \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{C}$} & x    & E, R                             & $\mathbb{B}$ \\
-                                  & e    & R                                & $\mathbb{D}$ \\
+    \multirow{3}{*}{$\mathbb{C}$} & \texttt{x} & E, R                             & $\mathbb{B}$ \\
+                                  & \texttt{e} & R                                & $\mathbb{D}$ \\
                                   & None       & L, L                             & $\mathbb{C}$ \\
@@
     \multirow{2}{*}{$\mathbb{D}$} & Any        & R, R                             & $\mathbb{D}$ \\
-                                  & None & P0, L, L                         & $\mathbb{A}$ \\
+                                  & None       & P\texttt{0}, L, L                         & $\mathbb{A}$ \\
 \end{tabu}
@@
     \hhline{====}
-    \multirow{2}{*}{$\mathbb{f}$(\textfrak{C},\textfrak{E},\textit{a})}   & e              & L & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
-                                                                          & Not e          & L & $\mathbb{f}$(\textfrak{C},\textfrak{E},\textit{a})   \\
+    \multirow{2}{*}{$\mathbb{f}$(\textit{a}, \textfrak{C}, \textfrak{E})}   & \texttt{e}              & L & $\mathbb{f}_1$(\textit{a}, \textfrak{C}, \textfrak{E}) \\
+                                                                          & Not \texttt{e}          & L & $\mathbb{f}$(\textit{a}, \textfrak{C}, \textfrak{E})   \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a})} & \textit{a}     &   & \textfrak{C} \\
-                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
-                                                                          & None           & R & $\mathbb{f}_2$(\textfrak{C},\textfrak{E},\textit{a}) \\
+    \multirow{3}{*}{$\mathbb{f}_1$(\textit{a}, \textfrak{C}, \textfrak{E})} & \textit{a}     &   & \textfrak{C} \\
+                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textit{a}, \textfrak{C}, \textfrak{E}) \\
+                                                                          & None           & R & $\mathbb{f}_2$(\textit{a}, \textfrak{C}, \textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{f}_2$(\textfrak{C},\textfrak{E},\textit{a})} & \textit{a}     &   & \textfrak{C} \\
-                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textfrak{C},\textfrak{E},\textit{a}) \\
+    \multirow{3}{*}{$\mathbb{f}_2$(\textit{a}, \textfrak{C}, \textfrak{E})} & \textit{a}     &   & \textfrak{C} \\
+                                                                          & Not \textit{a} & R & $\mathbb{f}_1$(\textit{a}, \textfrak{C}, \textfrak{E}) \\
                                                                           & None           & R & \textfrak{E} 
@@
     \hhline{====}
-    $\mathbb{e}$(\textfrak{C},\textfrak{E},\textit{a}) & - & - & $\mathbb{f}$($\mathbb{e}_1$(\textfrak{C}),\textfrak{E},\textit{a}) & \multirow{2}{80pt}{Erases first occurrence of symbol \textit{a}} \\
+    $\mathbb{e}$(\textit{a}, \textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$(\textit{a}, $\mathbb{e}_1$(\textfrak{C}), \textfrak{E}) & \multirow{2}{80pt}{Erases first occurrence of symbol \textit{a}} \\
     \hhline{----}
@@
     \hhline{====}
-    $\mathbb{fl}$(\textfrak{C}, \textfrak{e}, \textit{a}) & - & - & $\mathbb{f}$($\mathbb{l}$(\textfrak{C}),\textfrak{E},\textit{a}) & Moves to left of \textit{a} \\
+    $\mathbb{fl}$(\textit{a}, \textfrak{C}, \textfrak{e}) & - & - & $\mathbb{f}$($\mathbb{l}$(\textit{a}, \textfrak{C}), \textfrak{E}) & Moves to left of \textit{a} \\
     \hhline{----}
-    $\mathbb{fr}$(\textfrak{C}, \textfrak{e}, \textit{a}) & - & - & $\mathbb{f}$($\mathbb{r}$(\textfrak{C}),\textfrak{E},\textit{a}) & Moves to right of \textit{a} \\
+    $\mathbb{fr}$(\textit{a}, \textfrak{C}, \textfrak{e}) & - & - & $\mathbb{f}$($\mathbb{r}$(\textit{a}, \textfrak{C}), \textfrak{E}) & Moves to right of \textit{a} \\
     \hhline{====}
-    $\mathbb{p0}$(\textfrak{C}) & - & P0 & \textfrak{C} & Prints \texttt{0} \\
+    $\mathbb{p0}$(\textfrak{C}) & - & P\texttt{0} & \textfrak{C} & Prints \texttt{0} \\
     \hhline{----}
-    $\mathbb{p1}$(\textfrak{C}) & - & P1 & \textfrak{C} & Prints \texttt{0} \\
+    $\mathbb{p1}$(\textfrak{C}) & - & P\texttt{1} & \textfrak{C} & Prints \texttt{0} \\
     \hhline{====}
-    $\mathbb{n}$(\textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$($\mathbb{n}_1$(\textfrak{C}),\textfrak{E},e) & \multirow{3}{80pt}{Moves to first empty (final) \textit{p}-square} \\
+    $\mathbb{n}$(\textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$($\mathbb{n}_1$(\texttt{e}, \textfrak{C}), \textfrak{E}) & \multirow{3}{80pt}{Moves to first empty (final) \textit{p}-square} \\
     \hhline{----}
@@
     $\mathbb{\mathbf{b}def}$(\textit{p},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{n}$($\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C}),\textfrak{E}) \\
-    $\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C})   & - & P0, R, P\textit{p}, L & \textfrak{C} \\
+    $\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C})   & - & P\texttt{0}, R, P\textit{p}, L & \textfrak{C} \\
     \hhline{====}
@@
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
-                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
+    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
                                                                                        & other & - & \textfrak{E} \\
@@
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
-                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
+    \multirow{3}{*}{$\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
                                                                                        & other & - & \textfrak{E} \\
@@
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b},\textit{w},\textfrak{C},\textfrak{E})} & 0 & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
-                                                                                       & 1 & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
+    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b},\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
                                                                                        & other & - & \textfrak{E} \\
@@
     \multirow{3}{*}{$\mathbb{\mathbf{b}or}_1$(\textit{w},\textfrak{C},\textfrak{E})} 
-                                                                                       & 0 & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
-                                                                                       & 1 & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
+                                                                                       & \texttt{0} & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
                                                                                        & other & - & \textfrak{E} \\
@@
     \multirow{3}{*}{$\mathbb{\mathbf{b}xor}_1$(\textit{w},\textfrak{C},\textfrak{E})} 
-                                                                                       & 0 & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
-                                                                                       & 1 & - &  $\mathbb{\mathbf{b}not}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
+                                                                                       & \texttt{0} & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
+                                                                                       & \texttt{1} & - &  $\mathbb{\mathbf{b}not}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
                                                                                        & other & - & \textfrak{E} \\
@@
 The function $\mathbb{if}$ takes a symbol argument, which is compared to the symbol under the cursor - if they are the same, the machine $\rightarrow \mathbb{I}$; if not the machine $\rightarrow \mathbb{O}$.
-Since we have now entirely defined the operation of the machine in terms of functions (as loops can be done with recursion), we no longer have any need for tables - in effect, we have built a purely functional programming language in terms of a simple finite state machine.
-Now, in order to define more \textit{m}-functions we no longer have to write a table:
+Since we have now entirely defined the operation of the machine in terms of functions (as loops can be done with recursion), we no longer have any need for the central two table columns.
+In continuing to define functions, we could simply choose to omit these columns, or even omit the table altogether and use a more common notation - in this case, for a definition of the if function but based on pointers:
 
@@
 \end{lstlisting}
-
-Admittedly not the cleanest syntax, but still a simple one.
+While this syntax is more concise, it is still somewhat obfuscated. Therefore, we will use our function method to define what is effectively a programming language.
 \end{document}

### 2017-02-09 Draft 2/Section 2 - Turing Machines.tex
Added more consistency (still more to go)
Real general

@@
     \hhline{----}
-    $\mathbb{e}_1$(\textfrak{C}) & - & E & \textfrak{C}\\
+    $\mathbb{e}_1$(\textfrak{C}, \textfrak{E}) & - & E & \textfrak{C}\\
     \hhline{====}
-    $\mathbb{l}$(\textfrak{C}) & - & L & \textfrak{C} & Moves cursor left\\
+    $\mathbb{l}$(\textfrak{C}, \textfrak{E}) & - & L & \textfrak{C} & Moves cursor left\\
     \hhline{----}
-    $\mathbb{r}$(\textfrak{C}) & - & R & \textfrak{C} & Moves cursor right\\
+    $\mathbb{r}$(\textfrak{C}, \textfrak{E}) & - & R & \textfrak{C} & Moves cursor right\\
     \hhline{====}
-    $\mathbb{fl}$(\textit{a}, \textfrak{C}, \textfrak{e}) & - & - & $\mathbb{f}$($\mathbb{l}$(\textit{a}, \textfrak{C}), \textfrak{E}) & Moves to left of \textit{a} \\
+    $\mathbb{fl}$(\textit{a}, \textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$(\textit{a}, $\mathbb{l}$(\textfrak{C}), \textfrak{E}) & Moves to left of \textit{a} \\
     \hhline{----}
-    $\mathbb{fr}$(\textit{a}, \textfrak{C}, \textfrak{e}) & - & - & $\mathbb{f}$($\mathbb{r}$(\textit{a}, \textfrak{C}), \textfrak{E}) & Moves to right of \textit{a} \\
+    $\mathbb{fr}$(\textit{a}, \textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$(\textit{a}, $\mathbb{r}$(\textfrak{C}), \textfrak{E}) & Moves to right of \textit{a} \\
     \hhline{====}
-    $\mathbb{p0}$(\textfrak{C}) & - & P\texttt{0} & \textfrak{C} & Prints \texttt{0} \\
+    $\mathbb{p0}$(\textfrak{C}, \textfrak{E}) & - & P\texttt{0} & \textfrak{C} & Prints \texttt{0} \\
     \hhline{----}
-    $\mathbb{p1}$(\textfrak{C}) & - & P\texttt{1} & \textfrak{C} & Prints \texttt{0} \\
+    $\mathbb{p1}$(\textfrak{C}, \textfrak{E}) & - & P\texttt{1} & \textfrak{C} & Prints \texttt{0} \\
+    \hhline{----}
+    $\mathbb{ps}$(\textit{s},\textfrak{C}, \textfrak{E}) & - & P\textit{s} & \textfrak{C} & Prints \texttt{0} \\
     \hhline{====}
-    $\mathbb{n}$(\textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$($\mathbb{n}_1$(\texttt{e}, \textfrak{C}), \textfrak{E}) & \multirow{3}{80pt}{Moves to first empty (final) \textit{p}-square} \\
+    $\mathbb{n}$(\textfrak{C}, \textfrak{E}) & - & - & $\mathbb{f}$(\texttt{e}, $\mathbb{n}_1$(\textfrak{C}), \textfrak{E}) & \multirow{3}{80pt}{Moves to first empty (final) \textit{p}-square} \\
     \hhline{----}
@@
     \hhline{====}
-    $\mathbb{\mathbf{b}def}$(\textit{p},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{n}$($\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C}),\textfrak{E}) \\
-    $\mathbb{\mathbf{b}def}_1$(\textit{p},\textfrak{C})   & - & P\texttt{0}, R, P\textit{p}, L & \textfrak{C} \\
+    $\mathbb{\mathbf{b}def}$(\textit{p}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{n}$($\mathbb{\mathbf{b}def}_1$(\textit{p}, \textfrak{C}), \textfrak{E}) \\
+    $\mathbb{\mathbf{b}def}_1$(\textit{p}, \textfrak{C})   & - & P\texttt{0}, R, P\textit{p}, L & \textfrak{C} \\
     \hhline{====}
-    $\mathbb{\mathbf{b}copy}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E}),\textfrak{E},\textit{r}) \\
+    $\mathbb{\mathbf{b}copy}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}copy}_1$(\textit{w}, \textfrak{C}, \textfrak{E}), \textfrak{E}, \textit{r}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
-                                                                                       & other & - & \textfrak{E} \\
+    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}), \textfrak{E}, \textit{w}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}), \textfrak{E}, \textit{w}) \\ 
+                                                                                       & Other & - & \textfrak{E} \\
 \end{tabu}
@@
 \medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    $\mathbb{\mathbf{b}neg}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
+    $\mathbb{\mathbf{b}neg}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
-                                                                                       & other & - & \textfrak{E} \\
+    \multirow{3}{*}{$\mathbb{\mathbf{b}neg}_1$(\textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}, \textfrak{E}), \textfrak{E}, \textit{w}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}, \textfrak{E}), \textfrak{E}, \textit{w}) \\ 
+                                                                                       & Other & - & \textfrak{E} \\
 \end{tabu}
@@
 \medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    $\mathbb{\mathbf{b}and}$(\textit{a},\textit{b},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}and}_1$(\textit{b},\textit{w},\textfrak{C}),\textfrak{E}) \\
+    $\mathbb{\mathbf{b}and}$(\textit{a}, \textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}and}_1$(\textit{b}, \textit{w}, \textfrak{C}), \textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b},\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}),\textfrak{E},\textit{w}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
-                                                                                       & other & - & \textfrak{E} \\
+    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}), \textfrak{E}, \textit{w}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{\mathbf{b}copy}$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}) \\ 
+                                                                                       & Other & - & \textfrak{E} \\
     \hhline{====}
-    $\mathbb{\mathbf{b}or}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}or}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
+    $\mathbb{\mathbf{b}or}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}or}_1$(\textit{w}, \textfrak{C}), \textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}or}_1$(\textit{w},\textfrak{C},\textfrak{E})} 
-                                                                                       & \texttt{0} & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}),\textfrak{E},\textit{w}) \\ 
-                                                                                       & other & - & \textfrak{E} \\
+    \multirow{3}{*}{$\mathbb{\mathbf{b}or}_1$(\textit{w}, \textfrak{C}, \textfrak{E})} 
+                                                                                       & \texttt{0} & - & $\mathbb{\mathbf{b}copy}$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}), \textfrak{E}, \textit{w}) \\ 
+                                                                                       & Other & - & \textfrak{E} \\
     \hhline{====}
-    $\mathbb{\mathbf{b}xor}$(\textit{r},\textit{w},\textfrak{C},\textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}xor}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
+    $\mathbb{\mathbf{b}xor}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}xor}_1$(\textit{w}, \textfrak{C}), \textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}xor}_1$(\textit{w},\textfrak{C},\textfrak{E})} 
-                                                                                       & \texttt{0} & - & $\mathbb{\mathbf{b}copy}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\
-                                                                                       & \texttt{1} & - &  $\mathbb{\mathbf{b}not}$(\textit{b},\textit{w},\textfrak{C},\textfrak{E}) \\ 
-                                                                                       & other & - & \textfrak{E} \\
+    \multirow{3}{*}{$\mathbb{\mathbf{b}xor}_1$(\textit{w}, \textfrak{C}, \textfrak{E})} 
+                                                                                       & \texttt{0} & - & $\mathbb{\mathbf{b}copy}$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}) \\
+                                                                                       & \texttt{1} & - &  $\mathbb{\mathbf{b}not}$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}) \\ 
+                                                                                       & Other & - & \textfrak{E} \\
 \end{tabu}
@@
 Gradually, the cryptic and simplified language of Finite State Machines is yielding results similar to that of a computer.
+
+\subsubsection{Scripted Configurations}
 As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions.
@@
 \medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    \multirow{2}{*}{$\mathbb{if}$(\textit{c},\textfrak{I},\textfrak{O})} 
+    \multirow{2}{*}{$\mathbb{if}$(\textit{c}, \textfrak{I}, \textfrak{O})} 
                                                                                        & \textit{c} & - & \textfrak{I} \\
-                                                                                       & other & - & \textfrak{O} \\ 
+                                                                                       & Other & - & \textfrak{O} \\ 
     \hhline{====}
-    $\mathbb{ifp}$(\textit{r},\textit{c},\textfrak{I},\textfrak{O}, \textfrak{E}) & - & - & $\mathbb{fl}$($\mathbb{if}$(\textit{c}, \textfrak{I}, \textfrak{O}), \textfrak{E}, \textit{r}) \\
+    $\mathbb{ifp}$(\textit{r}, \textit{c}, \textfrak{I}, \textfrak{O}, \textfrak{E}) & - & - & $\mathbb{fl}$($\mathbb{if}$(\textit{c}, \textfrak{I}, \textfrak{O}), \textfrak{E}, \textit{r}) \\
 \end{tabu}
@@
 
-The function $\mathbb{if}$ takes a symbol argument, which is compared to the symbol under the cursor - if they are the same, the machine $\rightarrow \mathbb{I}$; if not the machine $\rightarrow \mathbb{O}$.
-Since we have now entirely defined the operation of the machine in terms of functions (as loops can be done with recursion), we no longer have any need for the central two table columns.
-In continuing to define functions, we could simply choose to omit these columns, or even omit the table altogether and use a more common notation - in this case, for a definition of the if function but based on pointers:
+The function $\mathbb{if}$ takes a symbol argument, which is compared to the symbol under the cursor - if they are the same, the machine $\rightarrow$ \textfrak{O}; if not the machine $\rightarrow$ \textfrak{O}.
+Since we have now entirely defined the operation of the machine in terms of \textit{m}-functions, we no longer have any need for the central two table columns.
+In continuing to define \textit{m}-functions, we could simply choose to omit these columns, or even omit the table altogether and use a more common notation - in this case, for a definition of the if function but based on pointers:
 
 \begin{lstlisting}
-ifp(r,c,I,O,E) = fl(
-    if(c,
-        I,
-        O
-    ),
-    E,
-    r
+ifp(r, c, I, O, E) = fl(r,
+    if(c, I, O), E
 )
 \end{lstlisting}
-While this syntax is more concise, it is still somewhat obfuscated. Therefore, we will use our function method to define what is effectively a programming language.
+
+While this syntax is more concise, it is still somewhat obfuscated.
+Therefore, we will use our function method to define what is effectively a list of commands for the machine which will be executed in order.
+The main difference in this system is that, as the \textfrak{C} argument is always the function that must be run when that function is completed (except in the case of the conditional function), on interpretation of the language the entire operation of the machine after that point must be passed as the \textfrak{C} argument to that
+
 \end{document}

### 2017-02-20 Draft 2/Section 2 - Turing Machines.tex
Major changes to sec2, added sec3
Appendages & corrections & clarifications for sec2, first few subsections
of sec3

@@
 
-\renewcommand{\arraystretch}{1.5}
+\renewcommand{\arraystretch}{1.5}p
 
+\lstdefinelanguage{Turlang}
+{
+  morekeywords={
+    function,
+    bool,
+    int,
+    and,
+    or,
+    not,
+    xor
+  },
+  sensitive=true, % keywords are not case-sensitive
+  morecomment=[l]{//}, % l is for line comment
+  morecomment=[s]{/*}{*/}, % s is for start and end delimiter
+  morestring=[b]" % defines that strings are enclosed in double quotes
+}
+\lstset{language=Turlang}
 \begin{document}
@@
 
-\subsubsection{Examples of simple Finite State Machines}\label{sec:FSMintro}
-The Turing Machine, or Finite State Machine (FSM), is composed of two parts: firstly, an ordered set of \textit{squares} of infinite length known as \textit{tape}, with a cursor at a certain point on this list, in which \textit{symbols} can be written for future use or output (much like random access memory on a modern computer); secondly, a set of states known as \textit{m}-configurations, each of which contain operations to be performed on the tape, and the \textit{m-configuration} that the FSM moves to.
+\subsection{Examples of simple Finite State Machines}\label{sec:FSMintro}
+The Turing Machine, or Finite State Machine (FSM), is composed of two parts: firstly, an ordered set of \textit{squares} of infinite length known as \textit{tape}, with a cursor at a certain point on this list, in which \textit{symbols} can be written for future use or output; secondly, a set of states known as \textit{m}-configurations, each of which contain operations to be performed on the tape, and the \textit{m}-configuration that the FSM moves to.
 An example description of such a set would be:
@@
     \hhline{====}
-    \multirow{1}{*}{$\mathbb{Q}$} & Any        & P\texttt{e}, R P\texttt{e}, R,  P\texttt{e}, R, R, P\texttt{0}, L, L & $\mathbb{A}$ \\
+    \multirow{1}{*}{$\mathbb{Q}$} & Any        & P\texttt{e}, R P\texttt{e}, R,  P\texttt{0}, R, R, P\texttt{0}, L, L & $\mathbb{A}$ \\
     \hhline{----}
-    \multirow{2}{*}{$\mathbb{A}$} & \texttt{1} & R, P\texttt{x}, L, L, L                   & $\mathbb{A}$ \\
+    \multirow{2}{*}{$\mathbb{A}$} & \texttt{0} & R, P\texttt{x}, L, L, L                   & $\mathbb{A}$ \\
                                   & \texttt{1} &                                  & $\mathbb{B}$ \\
@@
 
-\subsubsection{\textit{M}-functions}\label{sec:mfunctions}
+\subsection{\textit{M}-functions}\label{sec:mfunctions}
 
@@
 
-\subsubsection{Data Structures and Pointers}
+\subsection{Data Structures and Pointers}
 
@@
 
-\subsubsection{Scripted Configurations}
+\subsection{Scripted Configurations}
 As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions.
@@
                                                                                        & Other & - & \textfrak{O} \\
-    \hhline{====}
-    $\mathbb{ifp}$(\textit{r}, \textit{c}, \textfrak{I}, \textfrak{O}, \textfrak{E}) & - & - & $\mathbb{fl}$($\mathbb{if}$(\textit{c}, \textfrak{I}, \textfrak{O}), \textfrak{E}, \textit{r}) \\
 \end{tabu}
@@
 \end{lstlisting}
-
 While this syntax is more concise, it is still somewhat obfuscated.
 Therefore, we will use our function method to define what is effectively a list of commands for the machine which will be executed in order.
-The main difference in this system is that, as the \textfrak{C} argument is always the function that must be run when that function is completed (except in the case of the conditional function), on interpretation of the language the entire operation of the machine after that point must be passed as the \textfrak{C} argument to that
+The main difference in this system is that, as the \textfrak{C} argument is always the function that must be run when that function is completed (except in the case of the conditional function), on interpretation of the language the entire operation of the machine after that point must be passed as the \textfrak{C} argument to that function in order for the functions to be called sequentially.
+The following function main() defines variables \textit{var1} and \textit{var2}, and sets \textit{var2} to be not \textit{var1}, or \texttt{1}.
+
+\begin{lstlisting}
+function main() {
+	bdef(var1)
+	bdef(var2)
+	bneg(var1, var2)
+}
+\end{lstlisting}
+For clarity, I have ignored error handling (i.e. omitted the E argument). This is equivalent to:
+
+\begin{lstlisting}
+
+main(C, E) = bdef(var1,
+    bdef(var2,
+        bneg(var1, var2, C, E), E
+    ), E
+)
+
+\end{lstlisting}
+With arguments for continuity and simple error correction. This, in turn, can be simplified into a table.
+
+Furthermore, we can simplify certain functions to have their own specific syntax. In the case of definitions, "\lstinline{bdef(var)}" shall be abbreviated to "\lstinline{bool var}";
 

### 2017-02-20 Draft 2/Section 3 - Universality.tex
Major changes to sec2, added sec3
Appendages & corrections & clarifications for sec2, first few subsections
of sec3

\documentclass[Master.tex]{subfiles}

\begin{document}

\subsection{Universality in the $\lambda$-calculus}

The machine will be described as a function of two parameters, which calculates a single step in the FSM's calculation. It will receive as its first parameter the current state of the tape, and as its second the current \textit{m}-configuration. As this function will be unique to the specific FSM that is being emulated, the entire behavior of the machine based on this configuration (i.e. the machine's table) shall be contained within this function. The function will then be applied to itself repeatedly to produce the output tape.

\subsubsection{Emulating the Tape}
In order to achieve this, we must define certain new objects in $\lambda$-calculus. First of all, ordered lists - these will be used to describe the current content of the tape. These are defined as a sequence of nodes, where each node is a pair with the first element as the content of the node and the second element is the next node in the sequence. The final node will have \textbf{0} as its second element to signify the end of the list (of course this only works if the list is not designed to contain any values of zero or true, as they will be indistinguishable from the end marker - I shall use \textbf{1} to represent $S_0$, \textbf{2} to represent $S_1$ and so on). For example, the list [a,b,c,d,e] would be represented as:
\begin{equation*}
\lambda l.la(\lambda m.mb(\lambda n.nc(\lambda o.od(\lambda p.pe\bm{\mathrm{F}}))))
\end{equation*}
In order to obtain the first element (head), the argument \textbf{T} would be applied to the list; to get the remaining elements (tail) the \textbf{F} argument would be applied. 
Furthermore, to prepend an element to the start of a list:
\begin{equation*}
\bm{\mathrm{:}} = \lambda xlf.f[x][l]
\end{equation*}
This takes an element to prepend $x$, and a list $l$, and constructs a new pair with the given element as the first element and the original list as the second.

The tape of the FSM extends infinitely in both directions either side of the cursor. We shall represent this as a pair of lists, $T_p$ as the list of all the predecessors to the cursor and $T_s$ as the list of all the successors to the cursor. The predecessors shall be listed in reverse order, such that the head of $T_p$ is the symbol directly to the left of the cursor. The head of $T_s$ is the symbol considered to be `under' the cursor, the next element is the symbol to the right of that, and so on. These tapes will begin as a single node, and as the machine requires further squares in either direction further nodes will be added.
\begin{equation*}
T_a = \lambda f.f T_p T_s
\end{equation*}

\subsubsection{Movement Operations}
To emulate cursor movement, we will create transformation functions for the tape. These functions will shift the tape by moving the head of $T_s$ to the head of $T_p$ or vice versa.

\begin{gather*}
\begin{aligned}
\bm{M}_L &= \lambda t_a f.f [(t_a\bm{\mathrm{T}})\bm{\mathrm{F}}] [\bm{\mathrm{:}}([t_a\bm{\mathrm{T}}]\bm{\mathrm{T}})(t_a\bm{\mathrm{F}})]\\
\bm{M}_R &= \lambda t_a f.f [\bm{\mathrm{:}}([t_a\bm{\mathrm{F}}]\bm{\mathrm{T}})(t_a\bm{\mathrm{T}})] [(t_a\bm{\mathrm{F}})\bm{\mathrm{F}}]\\
\bm{M}_S &= \lambda x.x\\
\end{aligned}
\end{gather*}
The $\bm{M}_L$ function produces a new tape pair, after taking the original tape pair as parameter $t_a$. The first element of this new pair is simply the tail of $T_p$ ($T_p$ being found at $T_a\bm{\mathrm{T}})$. The second element is the head of $T_p$ prepended to the entirety of $T_s$ (found at $T_a\bm{\mathrm{T}})$. $\bm{M}_R$ will do the effective opposite, prepending the head of $T_s$ to $T_p$ and producing the tail of $T_s$. $\bm{M}_S$ Will keep the tape in its current state.

\subsubsection{Infinite-Length Tape}

Unfortunately, the tape which we are currently dealing with is unlike that of a Turing machine, due to the fact that it is of finite length - we cannot write a single list in $\lambda$-calculus which expresses the entire tape. As such, when the machine moves left or right onto the \textbf{0} tail signifying the end of the list, we will replace it with a node, containing the blank square symbol $S_0$, represented by a \textbf{1}. To do this, we will have another transformation function which will check if either tail element of the tape pair is \textbf{0}, and if so, will replace it with $\lambda g.g[\bm{\textbf{1}}][\bm{\mathrm{0}}]$:
\begin{equation*}
\bm{C} = \lambda t_ag.g[\bm{\mathrm{Z}}(t_a\bm{\mathrm{T}}\bm{\mathrm{F}})(\lambda g.g[\bm{\textbf{1}}][\bm{\mathrm{0}}])(t_a\bm{\mathrm{T}}\bm{\mathrm{F}})][\bm{\mathrm{Z}}(t_a\bm{\mathrm{F}}\bm{\mathrm{F}})(\lambda g.g[\bm{\textbf{1}}][\bm{\mathrm{0}}])(t_a\bm{\mathrm{F}}\bm{\mathrm{F}})]
\end{equation*}
TODO: check that Z($\lambda x.xab$) -> F for all a,b

This transformation will be applied after every tape movement operation.

\subsubsection{Writing to the Tape}
\end{document}

### 2017-02-20 Draft 2/Section 1 - Lambda Calculus.tex
Insignificant tiny changes which I can't place
sec1: renamed R function to Y combinator

@@
 
-\subsubsection{Arithmetical definitions}
+\subsection{Arithmetical definitions}
 
@@
 
-\subsubsection{Logic and Conditions}
+\subsection{Boolean Logic}
 
@@
 
-With the fundamental boolean system of our computational system in place, we must next construct conditionals. The first, and simplest, of these will check if a number is equal to zero:
+\subsection{Basic Comparison operators}
+
+With the fundamental boolean system of our computational system in place, we must next construct comparison operators. The first, and simplest, of these will check if a number is equal to zero:
 \begin{equation*}
@@
 However, in order to develop other conditional tests we will need a 'predecessor' function - something surprisingly difficult under lambda calculus.
-\subsubsection{Subtraction}
+\subsection{Subtraction}
 
@@
 Bearing in mind the predecessor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b>a$.
-\subsubsection{Further Conditional Logic}
+\subsection{Further Conditional Logic}
 
@@
 \end{equation*}
-\subsubsection{Recursion}
+\subsection{Recursion}
 
@@
 Continuity and repetition is one of the most significant aspects of computers, the power of this being the ability to transform a finite configuration into a potentially infinite result.
-This is done through one of the most remarkable functions in $\lambda$-Calculus, the recursor function:
+This is done through one of the most remarkable functions in $\lambda$-Calculus, the \textbf{Y} combinator:
 
 \begin{equation*}
-\bm{\mathrm{R}} = \lambda y.(\lambda x.y(xx))(\lambda x.y(xx))
+\bm{\mathrm{Y}} = \lambda y.(\lambda x.y(xx))(\lambda x.y(xx))
 \end{equation*}
@@
 \begin{aligned}
-\bm{\mathrm{R}}a &= (\lambda x.a(xx))[\lambda x.a(xx)]\\
+\bm{\mathrm{Y}}a &= (\lambda x.a(xx))[\lambda x.a(xx)]\\
 &= a([\lambda x.a(xx)][\lambda x.a(xx)])\\
-&= a(\bm{\mathrm{R}}a)
+&= a(\bm{\mathrm{Y}}a)
 \end{aligned}
 \end{equation*}
-Therefore, the \textbf{R} function applied to any function $a$ applies the function $a$ to the function \textbf{R} applied to $a$ - if substitution continues, an infinite series of nested $a$ functions is created; an infinite result is produced from a finite configuration.
+Therefore, the \textbf{Y} function applied to any function $a$ applies the function $a$ to the function \textbf{Y} applied to $a$ - if substitution continues, an infinite series of nested $a$ functions is created; an infinite result is produced from a finite configuration.
 Of course we can create finites as well by halting the function - an example of this would be the factorial function, where \textbf{!}a = \textbf{M}a(\textbf{!}[\textbf{P}a]) and \textbf{!0} = \textbf{1}.
@@
 the factorial function is the $\bm{\xi}$ function with itself as the argument $f$.
-Unfortunately such a definition is illegal under $\lambda$-Calculus as strictly no functions have names - this is where the function \textbf{R} comes into play.
+Unfortunately such a definition is illegal under $\lambda$-Calculus as strictly no functions have names - this is where the \textbf{Y} combinator comes into play.
 To find the factorial of \textbf{3}:
@@
 \begin{aligned}
-\bm{\mathrm{R\xi 3}} &= \bm{\mathrm{\xi}}(\bm{\mathrm{R\xi}})\bm{\mathrm{3}}\\
-&= \bm{\mathrm{Z31}}[\bm{\mathrm{M3}}([\bm{\mathrm{R\xi}}][\bm{\mathrm{P3}}])]\\
-&= \bm{\mathrm{M3}}(\bm{\mathrm{R\xi}}\bm{2})\\
+\bm{\mathrm{Y\xi 3}} &= \bm{\mathrm{\xi}}(\bm{\mathrm{Y\xi}})\bm{\mathrm{3}}\\
+&= \bm{\mathrm{Z31}}[\bm{\mathrm{M3}}([\bm{\mathrm{Y\xi}}][\bm{\mathrm{P3}}])]\\
+&= \bm{\mathrm{M3}}(\bm{\mathrm{Y\xi}}\bm{2})\\
 &= \bm{\mathrm{M3}}(\bm{\mathrm{M2}}(\bm{\mathrm{M11}}))\\
@@
 \end{equation*}
-The recursive identity \textbf{R} allows for \textbf{R}$\bm{\xi}$ to be applied as the first argument to the $\bm{\xi}$ function - as a result, the procedure also processes \textbf{2} and \textbf{1}, before stopping at \textbf{0} (which produces simply \textbf{1}.
+The \textbf{Y} combinator allows for \textbf{Y}$\bm{\xi}$ to be applied as the first argument to the $\bm{\xi}$ function - as a result, the procedure also processes \textbf{2} and \textbf{1}, before stopping at \textbf{0} (which produces simply \textbf{1}.
 To simplify, the factorial function:
 \begin{equation*}
-\bm{!} = \lambda x.\bm{\mathrm{R\xi}}x
+\bm{!} = \lambda x.\bm{\mathrm{Y\xi}}x
 \end{equation*}

### 2017-02-21 Draft 2/Section 3 - Universality.tex
Fixed list end collection

@@
 These are defined as a sequence of nodes, where each node is a pair with the first element as the content of the node and the second element is the next node in the sequence.
-The final node will have \textbf{0} as its second element to signify the end of the list (of course this only works if the list is not designed to contain any values of zero or true, as they will be indistinguishable from the end marker - I shall use \textbf{1} to represent $S_0$, \textbf{2} to represent $S_1$ and so on).
+The final node will have \textbf{0} as its first element to signify the end of the list - the second element will never be referred to; as such \textbf{0} will be used as a placeholder (of course this only works if the list is not designed to contain any values of zero or true, as they will be indistinguishable from the end marker - I shall use \textbf{1} to represent $S_0$, \textbf{2} to represent $S_1$ and so on).
 For example, the list [a,b,c,d,e] would be represented as:
@@
 Unfortunately, the tape which we are currently dealing with is unlike that of a Turing machine, due to the fact that it is of finite length - we cannot write a single list in $\lambda$-calculus which expresses the entire tape.
-As such, when the machine moves left or right onto the \textbf{0} tail signifying the end of the list, we will replace it with a node, containing the blank square symbol $S_0$, represented by a \textbf{1}.
-To do this, we will have another transformation function which will check if either tail element of the tape pair is \textbf{0}, and if so, will replace it with $\lambda g.g[\bm{\textbf{1}}][\bm{\mathrm{0}}]$:
-\begin{equation*}
-\bm{C} = \lambda t_ag.g[\bm{\mathrm{Z}}(t_a\bm{\mathrm{T}}\bm{\mathrm{F}})(\lambda g.g[\bm{\textbf{1}}][\bm{\mathrm{0}}])(t_a\bm{\mathrm{T}}\bm{\mathrm{F}})][\bm{\mathrm{Z}}(t_a\bm{\mathrm{F}}\bm{\mathrm{F}})(\lambda g.g[\bm{\textbf{1}}][\bm{\mathrm{0}}])(t_a\bm{\mathrm{F}}\bm{\mathrm{F}})]
-\end{equation*}
-TODO: check that Z($\lambda x.xab$) -> F for all a,b
+As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, we will replace it with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as he tail.
+To do this, we will have another transformation function which will check if either head element of the tape pair is \textbf{0}, and if so, will replace it with an empty square node $\bm{\epsilon}$ - otherwise it will simply be replacced with the original head:
 
+\begin{gather*}
+\begin{aligned}
+\bm{\epsilon} &= \lambda g.g[\bm{\textbf{1}}][\lambda d.d\bm{\mathrm{0}}\bm{\mathrm{0}}] \\
+\bm{C} &= \lambda t_a g.g[\bm{\mathrm{Z}}(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})(\bm{\epsilon})(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})][\bm{\mathrm{Z}}(t_a\bm{\mathrm{F}}\bm{\mathrm{T}})(\bm{\epsilon})(t_a\bm{\mathrm{F}}\bm{\mathrm{T}})]
+\end{aligned}
+\end{gather*}
 This transformation will be applied after every tape movement operation.
 
-\subsubsection{Writing to the Tape}
+\subsubsection{Printing to the Tape}
+
+The transformation that writes a given real number to the square beneath the cursor is not particularly complex - it simply replaces the current head of $T_s$ with a successor.
+
+\begin{equation*}
+\bm{W} = \lambda a t_a p.p[t_a\bm{\mathrm{T}}][\lambda d.d(a)(t_a\bm{\mathrm{FF}})]
+\end{equation*}
+
+\subsubsection{storing & accessing \textit{m}-configurations}
+\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}
+
 \end{document}

### 2017-02-21 Draft 2/Section 3 - Universality.tex
I honestly don't know what I've changed but here's a commit becuase y not

@@
 
-\subsubsection{storing & accessing \textit{m}-configurations}
-\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}
+\subsubsection{Storing \& Accessing \textit{m}-configurations}
+%\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}
+Once again, in order to store the information and operations associated with each \textit{m}-configuration, we shall use another list.
+The first element of the list shall represent $q_0$, the second $q_1$ and so on.
+Each element of the list will be a pair: firstly, the symbol which should be checked for, as a real number; secondly, the transformation that should be performed on the tape.
+This transformation will be of the form $(\bm{C})(\{\bm{M}_L/\bm{M}_R/\bm{M}_S\})(\bm{W}a)$, which applies first a write transformation first, before a movement transformation and the tape length correction transformation.
 

### 2017-02-22 Draft 2/Section 3 - Universality.tex
I am literally so tired I have no idea what I changed
Started work on the config getter function and pasted a useless table

@@
 \begin{equation*}
-\lambda l.la(\lambda m.mb(\lambda n.nc(\lambda o.od(\lambda p.pe\bm{\mathrm{F}}))))
+\lambda l.la(\lambda m.mb(\lambda n.nc(\lambda o.od(\lambda p.pe(\lambda z.z\bm{\mathrm{00}})))))
 \end{equation*}
@@
 As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, we will replace it with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as he tail.
-To do this, we will have another transformation function which will check if either head element of the tape pair is \textbf{0}, and if so, will replace it with an empty square node $\bm{\epsilon}$ - otherwise it will simply be replacced with the original head:
+To do this, we will have another transformation function which will check if either head element of the tape pair is \textbf{0}, and if so, will replace it with an empty square node $\bm{\epsilon}$ - otherwise it will simply be replaced with the original head:
 
@@
 The first element of the list shall represent $q_0$, the second $q_1$ and so on.
-Each element of the list will be a pair: firstly, the symbol which should be checked for, as a real number; secondly, the transformation that should be performed on the tape.
-This transformation will be of the form $(\bm{C})(\{\bm{M}_L/\bm{M}_R/\bm{M}_S\})(\bm{W}a)$, which applies first a write transformation first, before a movement transformation and the tape length correction transformation.
+Each element of the list will be a list in itself.
+Each element of this list shall refer to the symbol aspect of the configuration.
+Each element of the list is a pair: the first element being the symbol to be found (a real number), the second being the actions to be performed under this configuration.
+
+The action itself will be yet another pair.
+The first element is the transformation that should be performed on the tape - this transformation will be of the form $(\bm{C})(\{\bm{M}_L/\bm{M}_R/\bm{M}_S\})(\bm{W}a)$, which applies first a write transformation before a movement transformation and the tape length correction transformation.
+The second element is a function which, when given the description of the machine, finds the given \textit{m}-configuration.
+We shall note these m-configuration references as shown, with the example of the reference to $q_3$:
+\begin{equation*}
+\bm{Q}_3 = \lambda l.l\bm{\textbf{FFFT}}
+\end{equation*}
+This gets the fourth head of the given list, which refers to $q_3$.
+
+As an example, here is the description for the first machine described, which generates the sequence \texttt{01010101...} (for clarity, this version does not leave \textit{s}-squares blank).
+For reference, here is the enumerated table:
+%\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+%    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+%    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+%    \hhline{====}
+%    $q_0$ & $S_0$ & PS_1       & $\mathbb{A}$ \\
+%    $q_0$ & $S_1$ & PS_2 & $\mathbb{A}$ \\ 
+%    $q_0$ & \texttt{1}    & R, R, P\texttt{0} & $\mathbb{A}$ \\ 
+%\end{tabu}
+We shall represent this table as such:
+\begin{gather*}
+\begin{aligned}
+\bm{}
+\end{aligned}
+\end{gather*}
+{I cba to do this now}
+
+In order to find which action should be performed given a certain configuration, we shall use the following function which produces a pair of a list transformation and an \textit{m}-config reference from a current \textit{m}-config, the current symbol, and the description function.
+
+\begin{gather*}
+\begin{aligned}
+\bm{I} = \lambda qsc.(qc)(RECURSIVE FUNCTION TO GET SYMBOL)
+\end{aligned}
+\end{gather*}
 

### 2017-02-22 Draft 2/Section 1 - Lambda Calculus.tex
Finished state transformation function

@@
 \end{equation*}
-And through combination of these, we can create the equivalence and inequivalence operators (using $\bm{\doteq}$ for clarity from $=$:
+And through combination of these, we can create the equivalence and inequivalence operators (using $\bm{\doteq}$ for clarity from $=$):
 \begin{equation*}

### 2017-02-22 Draft 2/Section 3 - Universality.tex
Finished state transformation function

@@
 Each element of this list shall refer to the symbol aspect of the configuration.
-Each element of the list is a pair: the first element being the symbol to be found (a real number), the second being the actions to be performed under this configuration.
+These elements are pairs: the first element being the symbol to be found (a real number), the second being the action to be performed under this configuration.
 
 The action itself will be yet another pair.
-The first element is the transformation that should be performed on the tape - this transformation will be of the form $(\bm{C})(\{\bm{M}_L/\bm{M}_R/\bm{M}_S\})(\bm{W}a)$, which applies first a write transformation before a movement transformation and the tape length correction transformation.
+The first element is the transformation that should be performed on the tape - this transformation will be of the form $(\bm{C})(\bm{M}_{L/R/S})(\bm{W}a)$, which applies first a write transformation before a movement transformation and the tape length correction transformation.
 The second element is a function which, when given the description of the machine, finds the given \textit{m}-configuration.
@@
 
-As an example, here is the description for the first machine described, which generates the sequence \texttt{01010101...} (for clarity, this version does not leave \textit{s}-squares blank).
+%As an example, here is the description for the first machine described, which generates the sequence \texttt{01010101...} (for simplicity, this version does not leave \textit{s}-squares blank).
 For reference, here is the enumerated table:
@@
 %\end{tabu}
-We shall represent this table as such:
-\begin{gather*}
-\begin{aligned}
-\bm{}
-\end{aligned}
-\end{gather*}
-{I cba to do this now}
+%We shall represent this table as such:
+%\begin{gather*}
+%\begin{aligned}
+%\bm{d}
+%\end{aligned}
+%\end{gather*}
+
+%[I cba to do this now]
 
 In order to find which action should be performed given a certain configuration, we shall use the following function which produces a pair of a list transformation and an \textit{m}-config reference from a current \textit{m}-config, the current symbol, and the description function.
+As part of this function, the recursive function $\bm{\rho}$ must be used in conjunction with the \textbf{Y} combinator, which returns the action aspect of the first pair under symbol $s$ in list $l$ (the $r$ argument is the argument which would represent the function as a whole, and is recursively called by the \textbf{Y} combinator)
 
@@
 \begin{aligned}
-\bm{I} = \lambda qsc.(qc)(RECURSIVE FUNCTION TO GET SYMBOL)
+\bm{\rho} &= \lambda rls.(\bm{\doteq}(l\bm{\mathrm{TT}})s)(l\bm{\mathrm{TF}})(r(l\bm{\mathrm{F}})s)\\
+\bm{I} &= \lambda qsd.\bm{\mathrm{Y}\rho}(qd)s
+\end{aligned}
+\end{gather*}
+
+\subsubsection{Universal Machine State Change Operation}
+
+Finally, we can involve all of these functions to create a single operation which transforms a given machine configuration (\textit{m}-config, $T_p$ \& $T_s$, and the description table) into the machine configuration for the next state.
+This configuration shall be represented as a pair, the first element being a pair of the \textit{m}-config reference and the tape, and the second element as the description table.
+The $\bm{\nu}$ function gets the action function from the given machine configuration.
+
+\begin{gather*}
+\begin{aligned}
+\bm{\nu} &= \lambda c.\bm{I}(c\bm{\mathrm{TT}})([c\bm{\mathrm{TF}}]\bm{\mathrm{FT}})(c\bm{\mathrm{F}})\\
+\bm{U} &= \lambda cf.f[\lambda g.g[(\bm{\nu}c)\bm{\mathrm{F}}][((\bm{\nu}c)\bm{\mathrm{T}})(c\bm{\mathrm{TF}})]]c
 \end{aligned}

### 2017-02-23 Draft 2/Section 3 - Universality.tex
finished universality

@@
 
+\renewcommand{\arraystretch}{1.5}p
+So far, we have explored how our two methods of computation can perform many common operations, including data manipulation \& storage, on top of looping and conditional branching.
+Unfortunatley, it is too vague to simply define a 'comuputer' as a system which can perform a somewhat arbitrary set of operations - we must refine this to a simple set of functions.
+The easiest way of doing this is by assuming that a certain system can perform every operation a computer can perform.
+For this purpose, we will choose Turing machines, for purposes that will become clear later.
+Now, in order to prove that any system is a 'computer', we must simply prove that it can perform any operation a Turing machine can perform - in essence, it must be able to fully emulate the operation of a Turing FSM.
+
+ This essentially means that a machine, given a specific Turing machine starting configuration, should be able to produce every consecutive following state (i.e.
+it takes an FSM description table as input, and generates an infinite sequence of following tape \& \textit{m}-configuration states).
+Any machine that can do this shall be called a \textit{Universal Machine}.
+
+\subsection{Standard Turing Description Form}
+
+First, we must define what we actually mean by a description table - we shall do this by describing a standard form for these tables.
+Looking at the first table described, we can see that any sequence described in the operations section of the table follows a similar format: E; [E, R]; [E, L]; P\textit{a}; [ P\textit{a}, R]; [ P\textit{a}, L] or no entry at all.
+A more complex set of operations such as those found in later tables can always be put into one of these forms through the addition of intermediary \textit{m}-configurations which are called in sequence.
+
+Next, let us rename the \textit{m}-configurations as $q_0$, $q_1$, $q_2$, $...$, $q_n$ for clarity (the initial \textit{m}-configuration shall always be called $q_0$, the second $q_1$ and so on).
+Furthermore, the symbols shall be renamed $S_0$, $S_1$, $S_2$, $...$, $S_n$ - in this case, $S_0$ will represent the blank square, $S_1$ will represent \texttt{0} and $S_2$ will represent \texttt{1}.
+The movement transformations L and R will be renamed $M_L$, $M_R$, and the operation to keep the tape stationary is simply $M_S$.
+Our tables are now of form:
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \hhline{====}
+    $q_i$ & $S_i$ & P$S_k$, $M_{L/R/S}$ & $q_m$ \\
+    \hhline{----}
+\end{tabu}
+
+\medskip
+
+Lines such as
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    $q_i$ & $S_i$ & E, $M_{L/R/S}$ & $q_m$ \\
+\end{tabu}
+\medskip
+are to be written as
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    $q_i$ & $S_i$ & P$S_0$, $M_{L/R/S}$ & $q_m$ \\
+\end{tabu}
+\medskip
+and lines such as
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    $q_i$ & $S_i$ & $M_{L/R/S}$ & $q_m$ \\
+\end{tabu}
+\medskip
+are to be written as
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    $q_i$ & $S_i$ & P$S_i$, $M_{L/R/S}$ & $q_m$ \\
+\end{tabu}
+\medskip
+in order for all lines to be written in the first format.
+As the number of symbols used for a machine is always finite as the number of states is finite, it is possible to enumerate under every single \textit{m}-configuration an action for every single symbol $S_i$ that the machine coud be reading.
+In this way, "All" and "Not \textit{a}" will be portrayed in this format as the enumerated behaviours for every relevant symbol.
+This idea also allows the last simplification shown in the table above to work.
+
+This expanded and generalised configuration is much more helpful to us, as while any Turing machine configuration (including using \textit{m}-functions) can be written in this format, it is very concise and regular.
+This allows it to be given as input to our universal machines.
+
 \subsection{Universality in the $\lambda$-calculus}
-
-The machine will be described as a function of two parameters, which calculates a single step in the FSM's calculation.
-It will receive as its first parameter the current state of the tape, and as its second the current \textit{m}-configuration.
+Firstly, we shall prove that $\lambda$-calculus is Turing complete by building a universal machine using only $\lambda$-functions.
+The core of the machine will be a function which calculates a single step in the FSM's calculation: It will receive as its parameters the current state of the tape and the current \textit{m}-configuration.
 As this function will be unique to the specific FSM that is being emulated, the entire behavior of the machine based on this configuration (i.e.
 the machine's table) shall be contained within this function.
-The function will then be applied to itself repeatedly to produce the output tape.
+The function will then be applied to itself repeatedly to produce the sequences of states.
 
@@
 
-Finally, we can involve all of these functions to create a single operation which transforms a given machine configuration (\textit{m}-config, $T_p$ \& $T_s$, and the description table) into the machine configuration for the next state.
+At last, we can involve all of these functions to create a single operation which transforms a given machine configuration (\textit{m}-config, $T_p$ \& $T_s$, and the description table) into the machine configuration for the next state.
 This configuration shall be represented as a pair, the first element being a pair of the \textit{m}-config reference and the tape, and the second element as the description table.
@@
 \bm{\nu} &= \lambda c.\bm{I}(c\bm{\mathrm{TT}})([c\bm{\mathrm{TF}}]\bm{\mathrm{FT}})(c\bm{\mathrm{F}})\\
-\bm{U} &= \lambda cf.f[\lambda g.g[(\bm{\nu}c)\bm{\mathrm{F}}][((\bm{\nu}c)\bm{\mathrm{T}})(c\bm{\mathrm{TF}})]]c
+\bm{X} &= \lambda cf.f[\lambda g.g[(\bm{\nu}c)\bm{\mathrm{F}}][((\bm{\nu}c)\bm{\mathrm{T}})(c\bm{\mathrm{TF}})]]c
+\end{aligned}
+\end{gather*}
+
+\subsubsection{Universal Machine State Generator}
+
+Finally, we shall define a recursive function which produces every consecutive state by running $\bm{X}$ on itself an infinite number of times.
+
+\begin{gather*}
+\begin{aligned}
+\bm{\omega} &= \lambda uc.u(\bm{X}c) \\
+\bm{U} &= \lambda c.\bm{\mathrm{Y}}\bm{\omega}c
 \end{aligned}

### 2017-02-23 Draft 2/Section 1 - Lambda Calculus.tex
Proof read sec1&2

--- 2017-02-20 Draft 2/Section 1 - Lambda Calculus.tex
@@
 
-Church applies this medium to a variety of concepts we will already be familiar with - firstly, that of positive integers:
+Church uses this medium to define a variety of concepts we are already familiar with - firstly, that of positive integers:
 \begin{equation*}
@@
 
-Church defines functions to operate boolean logic - firstly representing True and False:
+Church defines functions to operate boolean logic, most significantly defining True and False:
 
@@
 
-These concepts are the base of conditional logic in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
+These concepts are the base of conditional branching in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
 For such operations, the concept of a 'pair' exists:
@@
 
-With the fundamental boolean system of our computational system in place, we must next construct comparison operators. The first, and simplest, of these will check if a number is equal to zero:
+With the fundamental boolean system of our computational system in place, we will next construct comparison operators. The first and simplest of these will check if a number is equal to zero:
 \begin{equation*}
@@
 \end{equation*}
-To understand this somewhat less than trivial concept, remember that \textbf{F} applied to any single argument yields the identity function $\lambda x.x$, and that \textbf{0} applied to any two arguments yields only the second:
+To understand this somewhat less than trivial concept, note that \textbf{F} when given only a single argument yields the identity function $\lambda x.x$, and that \textbf{0} applied to any two arguments yields only the second:
 \begin{equation*}
@@
 
-However, in order to develop other conditional tests we will need a 'predecessor' function - something surprisingly difficult under lambda calculus.
+However, in order to develop other conditional tests we will need a 'predecessor' function - a more complex concept in $\lambda$-calculus
 \subsection{Subtraction}
@@
 
-Firstly, the function transforms the pair (n, n-1) (the argument $p$) into the pair (n+1, n) (the new pair's elements are an increment and a copy of the first value respectively):
+Firstly, the function $\bm{\psi}$ transforms the pair (n, n-1) (the argument $p$) into the pair (n+1, n) (the new pair's elements are an increment and a copy of the first value respectively):
 \begin{equation*}
@@
 \begin{equation*}
-\bm{\mathrm{P}} = \lambda n.n \bm{\psi} (\lambda x.\bm{\mathrm{00}}) \bm{\mathrm{F}} 
+\bm{\mathrm{P}} = \lambda n.[n \bm{\psi} (\lambda x.\bm{\mathrm{00}})] \bm{\mathrm{F}} 
 \end{equation*}
@@
 \end{equation*}
-Bearing in mind the predecessor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b>a$.
+Bearing in mind the predecessor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b\geq a$.
 \subsection{Further Conditional Logic}
@@
 \end{equation*}
-And through combination of these, we can create the equivalence and inequivalence operators (using $\bm{\doteq}$ for clarity from $=$:
+and through combination of these, we can create the equivalence and inequivalence operators (using $\bm{\doteq}$ for clarity from $=$):
 \begin{equation*}
@@
 
-So far, Church's $\lambda$-Calculus is very close to the operation of a modern computation language.
-It has representation for boolean values, for conditional statements, for positive integers (signed integers can be expressed as a pair of a positive integer and a boolean for sign) and arithmetic, as well as set operations for booleans and comparators for integers - In fact, we are very close to our definition of computability save one thing.
+So far, Church's $\lambda$-Calculus is very close to the operation of a modern programming language.
+It has representation for boolean values, for conditional statements, for positive integers (signed integers can be expressed as a pair of positive integers where the difference is the value to be represented) and arithmetic, as well as set operations for booleans and comparators for integers - In fact, we are very close to our definition of computability, save one thing.
 Continuity and repetition is one of the most significant aspects of computers, the power of this being the ability to transform a finite configuration into a potentially infinite result.
@@
 Our brief stroll through the key aspects of $\lambda$-Calculus is complete.
-We have defined that every basic necessary concept in a common programming language can be defined through the use of two simple axioms - that of the concept of functions, and the operation of substitution.
+We have shown that many basic necessary concepts in a common programming language can be defined through the use of two simple axioms - that of the concept of functions, and the operation of substitution.
 $\lambda$-Calculus was described by Church as an 'effectively calculable' system, in that it could perform any calculable calculation.
 In more popular terms, it is Turing-complete - we will look at what this is and why this is the case later on in the project.
-However, it is clear to see that the Calculus is able to simulate many aspects of the computer - data storage with pairs (pairs of pairs can be used for larger capacity), conditionals and booleans, integers and arithmetic and, finally, the ability to be continuous (circular) from a finite configuration.
-This is our first definition of a 'computer', and therefore any mechanical or axiomatic system which is able to simulate $\lambda$-calculus is also a 'computer', and shall also be called 'effectively calculable'.
+However, it is clear to see that the Calculus is able to simulate many functions of the computer - data storage with pairs (pairs of pairs can be used for storing more than two items of data as shown in \cref{sec:LambdaUnivTape}), conditionals and booleans, integers and arithmetic and, finally, the ability to be continuous (circular) from a finite configuration.
+$\lambda$-calculus is our first attempt to clarify the attributes of a computer, and does so both fundamentally and aesthetically.
 \end{document}

### 2017-02-23 Draft 2/Section 2 - Turing Machines.tex
Proof read sec1&2

@@
 \documentclass[Master.tex]{subfiles}
-
-\crefname{section}{§}{§§}
-\Crefname{section}{§}{§§}
-
-\renewcommand{\arraystretch}{1.5}p
 
@@
 \begin{document}
+\renewcommand{\arraystretch}{1.5}
 
-At roughly the same time, the English Mathematician Alan Turing was constructing a method to achieve the same goal, but in an entirely different way.
-Rather than building an incredibly simple axiomatic system to illustrate Effective Computability, the concept used was far more practical, and far closer to the mechanical computers that implemented this idea.
+At roughly the same time, the English mathematician Alan Turing was constructing a method to achieve the same goal, but in an entirely different way.
+Rather than building a simple and practical axiomatic system, the concept used was far more practical, and far closer to the mechanical computers that eventually implemented this idea.
 
@@
 This table format shall be used to describe FSM configurations.
-Firstly, the final line describes the starting \textit{m}-configuration.
+First of all, the last line describes the starting \textit{m}-configuration.
 When the machine begins an iteration on any one of these \textit{m}-configurations, it first checks if the symbol aspect of the configuration is equal to the \textit{symbol} currently under the cursor on the tape.
@@
 
-It is again not difficult to see that this produces the same output as the previous machine, but this time using only one \textit{m-configuration}.
+It is again not difficult to see that this produces the same output as the previous machine, but this time using only one \textit{m}-configuration.
 
@@
 The operation of such a machine is significantly more complex than the earlier one.
-Key to the operation of this machine is the fact that squares are paired into primary squares or \textit{p}-squares (odd-numbered squares) on which the symbols of the output sequence are printed.
-Only the symbols \texttt{0} and \texttt{1} will be printed on these squares, and printed symbols will never be erased.
+Key to the operation is the fact that squares are paired, firstly into primary squares or \textit{p}-squares (odd-numbered squares) on which the symbols of the output sequence are printed.
+Only the symbols \texttt{0} and \texttt{1} will ever be printed on these squares.
 To the right of each \textit{p}-square is a secondary square, or \textit{s}-square (an even-numbered square).
@@
 These symbols can be erased and overwritten, and are not part of the output sequence.
-Only one \textit{s}-square is needed to contain multiple markers, or more descriptive markers for a single \textit{p}-square, as this can be achieved with a sufficiently large array of marker symbols.
+Only one \textit{s}-square is needed to contain multiple markers, or more descriptive markers for a single \textit{p}-square, as this can be achieved with a sufficiently rich variety of marker symbols.
 
@@
 Unfortunately, the operation of this machine is somewhat complex and involved.
-To simplify the usage of the FSM, we will introduce a type of function for the FSM.
+To simplify this, we will introduce a type of function for the FSM.
 
@@
 
-In this section I will define a set of common \textit{m}-functions that will be used regularly in future.
+In this section a set of common and useful \textit{m}-functions are defined that will be used regularly in future.
 
@@
 Since we have now entirely defined the operation of the machine in terms of \textit{m}-functions, we no longer have any need for the central two table columns.
-In continuing to define \textit{m}-functions, we could simply choose to omit these columns, or even omit the table altogether and use a more common notation - in this case, for a definition of the if function but based on pointers:
+In continuing to define \textit{m}-functions, we could simply choose to omit these columns, or even omit the table altogether and use a clearer notation - in this case, for a definition of the if function but based on pointers:
 
@@
 \end{lstlisting}
-With arguments for continuity and simple error correction. This, in turn, can be simplified into a table.
+with arguments for continuity and simple error correction. This, in turn, can be simplified into a table.
 

### 2017-02-23 Draft 2/Master.tex
Added Turing Machines section
(empty); Fixed numbering
Misc changes
Ngl thats the best you're getting
Loooooads of nice nice changes
Cba to explain I havn't been commiting regularly
Added recursive syntax
Insignificant tiny changes which I can't place
sec1: renamed R function to Y combinator
Fixed list end collection
Proof read sec1&2
Lots of lovely changes

@@
 \usepackage{bm}
+\usepackage{multirow, bigdelim}
+\usepackage{hhline}
+\usepackage{tabu}	
+\usepackage[bb=boondox]{mathalfa}
+\usepackage{yfonts}
+\usepackage{cleveref}
+\usepackage{listings}
 
-\title{How Significant was WW2 in the Development of the Computer?}
-\date{November 24, 2016}
+\title{Did WW2 Produce an Equivalent to a Modern Computer?}
+\date{February 23, 2017}
 \author{Max Penrose}
@@
 \tableofcontents
+\clearpage
 
-\section{Effective Computability}
-
-In this first section I would like to describe the fundamental attributes a machine must have for it to be called a 'computer'.
-Prior to the war and the development of electronic computation, any human who performed a calculation would  frequently be called a 'computer'.
-However, this specific attribute of computation is difficult to define - to do so, I will be looking at the minimalist  $\lambda$-Calculus developed by Mathematician and Logician Alonzo Church, the famous concept of the Universal Turing Machine created by English Mathematician Alan Turing, and the similarities and differences between these two definitions.
-
-\subsection{Church's $\lambda$-Calculus}
+\section{Church's $\lambda$-Calculus}
 
@@
 
+\section{Turing Machines}
+
+\subfile{"Section 2 - Turing Machines"}
+
+\section{Universality}
+
+\subfile{"Section 3 - Universality"}
+
 \end{document}

### 2017-02-23 Draft 2/Section 3 - Universality.tex
Proof read sec1&2
Lots of lovely changes

@@
 
-\renewcommand{\arraystretch}{1.5}p
+\renewcommand{\arraystretch}{1.5}
 So far, we have explored how our two methods of computation can perform many common operations, including data manipulation \& storage, on top of looping and conditional branching.

### 2017-03-09 Draft 2/Section 1 - Lambda Calculus.tex
Lots of lovely changes
Corrections to sec1

@@
 \end{equation*}
-Here it can bee seen that for each number \textit{n} the argument $s$  is applied to the argument $z$ \textit{n} times.
+Here it can bee seen that for each number \textit{n} the argument $s$ is applied to the argument $z$ \textit{n} times - the $s$ functions representing \textit{n} successors to zero ($z$).
 
@@
 \bm{\mathrm{S2}} &= (\lambda wyx.y(wyx)) (\lambda sz.s(s(z)))\\
-&= y([\lambda sz.(s(s(z)))]yx)\\
-&=y[y(y(z))]\\
-&=s(s(s(z)))\\
-&=\bm{\mathrm{3}}
+&= \lambda yx.y([\lambda sz.(s(s(z)))]yx)\\
+&= \lambda yx.y(y(y(z)))\\
+&= \lambda sz.s(s(s(z)))\\
+&= \bm{\mathrm{3}}
 \end{aligned}
@@
 \begin{aligned}
-\bm{\mathrm{2S3}} &= (\lambda sz.s(s(z))) (\lambda wyx.y(wyx)) (\lambda sz.s(s(s(z))))\\
-&= (\lambda wyx.y(wyx)) [(\lambda wyx.y(wyx)) [\lambda sz.s(s(s(z)))]]\\
-&= (\lambda wyx.y(wyx)) [\lambda sz.s(s(s(s(z))))]\\
-&= \lambda sz.s(s(s(s(s(z)))))\\
+\bm{\mathrm{2S3}} &= (\lambda sz.s(s(z))) [\bm{\mathrm{S}}] [\bm{\textrm{3}}]\\
+&= \bm{\mathrm{S}} (\bm{\mathrm{S}} (\bm{\mathrm{3}}))\\
+&= \bm{\mathrm{S}} (\bm{\mathrm{4}})\\
 &= \bm{\mathrm{5}}
@@
 \begin{equation*}
-\bm{\mathrm{A}} = \lambda ab.a\bm{\mathrm{S}}b
+\bm{\mathrm{A}} = \lambda ab.b\bm{\mathrm{S}}a
 \end{equation*}
 
-A 'power' function to find $a^b$can also be defined, of astonishing simplicity:
+An 'exponent' function to find $a^b$can also be defined, of astonishing simplicity:
 \begin{equation*}
-\bm{\mathrm{P}} = \lambda ba.ab
+\bm{\mathrm{E}} = \lambda ba.ab
 \end{equation*}
@@
 \begin{aligned}
-\bm{\mathrm{P23}} &= (\lambda ab.ab)(\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
+\bm{\mathrm{E23}} &= (\lambda ab.ab)(\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
 &= (\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
@@
 \end{gather*}
-The derivation of such operations is not difficult to understand if one considers the truth tables for each operation, remembering that T selects the first and F selects the second argument.
+The derivation of such operations is not difficult to understand if one considers the truth tables for each operation, remembering that T selects the first and F selects the second argument - for example, looking at the OR function $\vee$:
+
+\begin{gather*}
+\begin{aligned}
+\vee \bm{\mathrm{TF}} &= \bm{\mathrm{T}}[\bm{\mathrm{T}}][\bm{\mathrm{F}}] \\
+&= \bm{\mathrm{T}} \\
+\vee \bm{\mathrm{FF}} &= \bm{\mathrm{F}}[\bm{\mathrm{T}}][\bm{\mathrm{F}}] \\
+&= \bm{\mathrm{F}} \\
+\vee \bm{\mathrm{FT}} &= \bm{\mathrm{F}}[\bm{\mathrm{T}}][\bm{\mathrm{T}}] \\
+&= \bm{\mathrm{T}} \\
+\end{aligned}
+\end{gather*}
+
+If the first argument is \textbf{T} the function will always return \textbf{T}, as it is the first argument.
+If the first argument is \textbf{F} on the other hand, the value of the second argument will be returned (the $\vee$ function is dependant on at least one argument being \textbf{T} - if this is not the first argument, the outcome is simply whether the second argument is \textbf{T} or not).
+The remaining functions work in a similar way.
 
@@
 \begin{aligned}
-\bm{\mathrm{Z0}} &= (\lambda x.x\bm{\mathrm{f\lnot F}})\bm{0}\\
+\bm{\mathrm{Z0}} &= (\lambda x.x\bm{\mathrm{F\lnot F}})\bm{0}\\
 &= \bm{\mathrm{0F\lnot F}}\\
@@
 \begin{aligned}
-\bm{\mathrm{Z2}} &= (\lambda x.x\bm{\mathrm{f\lnot F}})\bm{2}\\
+\bm{\mathrm{Z2}} &= (\lambda x.x\bm{\mathrm{F\lnot F}})\bm{2}\\
 &= \bm{\mathrm{2F\lnot F}}\\
@@
 \end{equation*}
+\subsubsection{Conclusion}
 
-\subsubsection{Conclusion}
 Our brief stroll through the key aspects of $\lambda$-Calculus is complete.

### 2017-03-14 Draft 2/Master.tex
Preparation for Luke Ong

@@
 
+\crefname{section}{§}{§§}
+\Crefname{section}{§}{§§}
+
 \begin{document}
@@
 \clearpage
+\textit{TODO: introduction - stating aim of checking whether computers produced during and after WW2 were 'computers'}
+
+In order to achieve this, I must first describe the fundamental attributes a machine must have for it to be called a 'computer'.
+Prior to the war and the development of electronic computation, any human who performed a calculation would  frequently be called a 'computer'.
+However, this specific attribute of computation is difficult to define - to do so, I will be looking at the minimalist  $\lambda$-Calculus developed by Mathematician and Logician Alonzo Church, the famous concept of the Universal Turing Machine created by English Mathematician Alan Turing, and the similarities and differences between these two definitions.
 

### 2017-03-14 Draft 2/Section 3 - Universality.tex
Preparation for Luke Ong

@@
 
-\subsubsection{Emulating the Tape}
+\subsubsection{Emulating the Tape}\label{sec:LambdaUnivTape}
 In order to achieve this, we must define certain new objects in $\lambda$-calculus.
@@
 
-Finally, we shall define a recursive function which produces every consecutive state by running $\bm{X}$ on itself an infinite number of times.
+Finally, we shall define a recursive function which produces every consecutive state by running $\bm{X}$ on itself repeatedly.
+When this is evaluated, each iteration of the machine shall be passed into the \textbf{Y} combinator, leading to each consecutive state being found during evaluation.
 

### 2017-04-19 Draft 2/Section 1 - Lambda Calculus.tex
Colossal changes to all sections
Added referencing, changed language of turing machines, more detailed
intros&concns

@@
 The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability, far from the very real and mechanical world of Turing.
-It deals with a set of objects - for our purposes denoted with single symbolic characters - which define what school mathematics or common computer science would call 'functions'.
+It deals with a set of objects - for our purposes denoted with singl  e symbolic characters - which define what school mathematics or common computer science would call `functions'.
 These functions take as their arguments (other objects which the functions act upon) functions alone, and can also output only functions.
@@
 Note that while commonly we would use the syntax $a(b)$ to express the same thing, it greatly simplifies expression to use this format.
-Church defines these functions through the method of 'abstraction' - let us look at a different function to illustrate:
+Church defines these functions through the method of `abstraction' - let us look at a different function to illustrate:
 \begin{equation*}
@@
 \lambda a.(\lambda b.ba) &=  \lambda ab.ba \\
-([\lambda a.(\lambda b.ba)]u)v &= (\lambda b.bu)v \\ &= vu
+[\lambda a.(\lambda b.ba)]uv &= (\lambda b.bu)v \\ &= vu
 \end{aligned}
@@
 
-Church uses this medium to define a variety of concepts we are already familiar with - firstly, that of positive integers:
+Church uses this medium to define a variety of concepts we are already familiar with - firstly, that of positive integers.
+\cite{church1941lambda}
 \begin{equation*}
@@
 \end{equation*}
-Here it can bee seen that for each number \textit{n} the argument $s$ is applied to the argument $z$ \textit{n} times - the $s$ functions representing \textit{n} successors to zero ($z$).
+Here it can be seen that for each number \textit{n} the argument $s$ is applied to the argument $z$ \textit{n} times - the $s$ functions representing \textit{n} successors to zero ($z$).
 
 From this, it is not difficult to define an operation that takes a number as input and increments it by 1 - such a function would take three arguments (the first being the number, and the second two being the arguments $s$ and $z$ for the number) and would apply the argument $s$ to the number:
+\cite{rojas2015lambdatutorial}
 \begin{equation*}
@@
 Remembering that each number applies the function $s$ to $z$ \textit{n} times, and that addition is simply incrementing \textit{a} \textit{b} times, addition is as simple as:
+\cite{rojas2015lambdatutorial}
 \begin{equation*}
@@
 \begin{aligned}
-\bm{\mathrm{2S3}} &= (\lambda sz.s(s(z))) [\bm{\mathrm{S}}] [\bm{\textrm{3}}]\\
+\bm{\mathrm{2S3}} &= (\lambda sz.s(s(z))) \bm{\mathrm{S}} \bm{\textrm{3}}\\
 &= \bm{\mathrm{S}} (\bm{\mathrm{S}} (\bm{\mathrm{3}}))\\
@@
 Multiplication can also be calculated by defining the function \textbf{M}:
+\cite{rojas2015lambdatutorial}
 \begin{equation*}
@@
 \end{gather*}
-We should rearrange our earlier addition method into an 'addition' function of the same format which takes two arguments:
+We should rearrange our earlier addition method into an `addition' function of the same format which takes two arguments:
 \begin{equation*}
@@
 
-An 'exponent' function to find $a^b$can also be defined, of astonishing simplicity:
+An `exponent' function to find $a^b$can also be defined, of astonishing simplicity:
+\cite{penrose1991emperor}
 \begin{equation*}
@@
 Church defines functions to operate boolean logic, most significantly defining True and False:
+\cite{rojas2015lambdatutorial}
 
@@
 These concepts are the base of conditional branching in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
-For such operations, the concept of a 'pair' exists:
+For such operations, the concept of a `pair' exists:
+\cite{church1941lambda}
 \begin{equation*}
@@
 Functions representing boolean operations can also be defined:
+\cite{rojas2015lambdatutorial}
 \begin{gather*}
@@
 
-With the fundamental boolean system of our computational system in place, we will next construct comparison operators. The first and simplest of these will check if a number is equal to zero:
+With the fundamental boolean system of our computational system in place, we will next construct comparison operators. The first and simplest of these will test if a number is equal to zero:
+\cite{rojas2015lambdatutorial}
 \begin{equation*}
@@
 To understand this somewhat less than trivial concept, note that \textbf{F} when given only a single argument yields the identity function $\lambda x.x$, and that \textbf{0} applied to any two arguments yields only the second:
+\cite{rojas2015lambdatutorial}
 \begin{equation*}
@@
 From this, it easier to see how the function works. Firstly with \textbf{0}:
+\cite{rojas2015lambdatutorial}
 \begin{gather*}
@@
 
-However, in order to develop other conditional tests we will need a 'predecessor' function - a more complex concept in $\lambda$-calculus
+However, in order to develop other conditional tests we will need a `predecessor' function - a more complex concept in $\lambda$-calculus.
 \subsection{Subtraction}
@@
 Firstly, the function $\bm{\psi}$ transforms the pair (n, n-1) (the argument $p$) into the pair (n+1, n) (the new pair's elements are an increment and a copy of the first value respectively):
+\cite{rojas2015lambdatutorial}
 \begin{equation*}
@@
 To find the predecessor to $n$ therefore, we apply this function $n$ times to the pair (0, 0) and the pair (n, n-1) is formed, after which the second element can easily be selected.
+\cite{rojas2015lambdatutorial}
 \begin{equation*}
@@
 \end{equation*}
-Bearing in mind the predecessor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b\geq a$.
+Bearing in mind the predeces sor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b\geq a$.
 \subsection{Further Conditional Logic}
@@
 This is done through one of the most remarkable functions in $\lambda$-Calculus, the \textbf{Y} combinator:
-
+\cite{rojas2015lambdatutorial}
 \begin{equation*}
@@
 \end{equation*}
-Therefore, the \textbf{Y} function applied to any function $a$ applies the function $a$ to the function \textbf{Y} applied to $a$ - if substitution continues, an infinite series of nested $a$ functions is created; an infinite result is produced from a finite configuration.
+This function is remarkable as it is a `fixpoint operator' - it is able to easily generate a `fixpoint' of any given function (a value $x$ is a fixpoint of the function $f$ if and only if $fx = x$) by applying the function as the first parameter of the \textbf{Y} combinator.
+
+Therefore, the \textbf{Y} combinator applied to any function $a$ applies the function $a$ to the function \textbf{Y} applied to $a$ - if substitution continues, an infinite series of nested $a$ functions is created; an infinite result is produced from a finite configuration.
 Of course we can create finites as well by halting the function - an example of this would be the factorial function, where \textbf{!}a = \textbf{M}a(\textbf{!}[\textbf{P}a]) and \textbf{!0} = \textbf{1}.
@@
 the factorial function is the $\bm{\xi}$ function with itself as the argument $f$.
-Unfortunately such a definition is illegal under $\lambda$-Calculus as strictly no functions have names - this is where the \textbf{Y} combinator comes into play.
+Unfortunately such a definition is illegal under $\lambda$-Calculus as all functions are strictly anonymous - this is where the \textbf{Y} combinator comes into play.
 To find the factorial of \textbf{3}:
@@
 \end{equation*}
-\subsubsection{Conclusion}
+\subsection{Conclusion}
 
@@
 We have shown that many basic necessary concepts in a common programming language can be defined through the use of two simple axioms - that of the concept of functions, and the operation of substitution.
-$\lambda$-Calculus was described by Church as an 'effectively calculable' system, in that it could perform any calculable calculation.
+$\lambda$-Calculus was described by Church as an `effectively calculable' system, in that it could perform any calculable calculation.
 In more popular terms, it is Turing-complete - we will look at what this is and why this is the case later on in the project.

### 2017-04-19 Draft 2/Section 2 - Turing Machines.tex
Lots of lovely changes
corrections and bibtex
Colossal changes to all sections
Added referencing, changed language of turing machines, more detailed
intros&concns

@@
 At roughly the same time, the English mathematician Alan Turing was constructing a method to achieve the same goal, but in an entirely different way.
-Rather than building a simple and practical axiomatic system, the concept used was far more practical, and far closer to the mechanical computers that eventually implemented this idea.
+Rather than building a basic and strongly theoretical system, the concept used was far more physical and far closer to the mechanical computers that eventually implemented this idea.
 
-\subsection{Examples of simple Finite State Machines}\label{sec:FSMintro}
-The Turing Machine, or Finite State Machine (FSM), is composed of two parts: firstly, an ordered set of \textit{squares} of infinite length known as \textit{tape}, with a cursor at a certain point on this list, in which \textit{symbols} can be written for future use or output; secondly, a set of states known as \textit{m}-configurations, each of which contain operations to be performed on the tape, and the \textit{m}-configuration that the FSM moves to.
-An example description of such a set would be:
+\subsection{Examples of simple Turing Machines}\label{sec:TMacIntro}
+The Turing Machine is composed of two parts.
+Firstly, an ordered set of \textit{cells} of infinite\footnote{Many definitions of Turing Machines have the tape extending infinitely in one direction only - in fact for full functionality a tape extending infinitely in both directions is unnecessary.} length known as \textit{tape}.
+On each of these cells one of a finite set of \textit{symbols} - either alphanumeric characters or the symbol which represents an empty cell.
+At a given point on this tape is a \textit{tape head} (or cursor) which is able to write symbols to the current cell.
+Secondly, a finite set of instructions known as \textit{states} contain finite-length sequences of operations known as the \textit{transition function} which the cursor enacts, and the states that the machine moves to after performing those operations.
+An example description of a set of states would be: \cite{turing1936computablenumbers}
 
@@
     \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
-    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+    \textit{state} & \textit{symbol} & \textit{transition function} & \textit{final state} \\
     \hhline{====}
@@
 
-This table format shall be used to describe FSM configurations.
-First of all, the last line describes the starting \textit{m}-configuration.
-When the machine begins an iteration on any one of these \textit{m}-configurations, it first checks if the symbol aspect of the configuration is equal to the \textit{symbol} currently under the cursor on the tape.
-If this condition is met, the operations are carried out - P\textit{n} for any symbol \textit{n} prints the symbol \textit{n} on the tape under the cursor; E erases any symbol under the cursor; L moves the cursor to the left; R moves the cursor to the right.
-When these operations are completed, the \textit{m}-configuration is set to that described in the last column.
-The FSM then moves to the next iteration.
+This table format shall be used to describe Turing Machine configurations.
+First of all, the last line describes the starting state ($\mathbb{A}$).
+When the machine begins an iteration on any one of these states, it first checks if the symbol aspect of the configuration is equal to the \textit{symbol} currently under the cursor on the tape.
+If this condition is met, the transition function is carried out - P\textit{n} for any symbol \textit{n} prints the symbol \textit{n} on the tape under the cursor; E erases any symbol under the cursor\footnote{More formally, prints the empty cell symbol}; L moves the cursor to the left; R moves the cursor to the right.
+When these operations are completed, the state is set to that described in the last column.
+The machine then moves to the next iteration.
 
-In this case, it is not difficult to see that as the machine runs, it leaves a sequence of alternating 0s and 1s on every other square on the tape.
-However, with the use of the \textit{symbol} condition, this table can be simplified:
+In this case, it is not difficult to see that as the machine runs, it leaves a sequence of alternating 0s and 1s on every other cell on the tape.
+With the use of the \textit{symbol} condition, this table can be simplified: \cite{turing1936computablenumbers}
 
@@
 
-It is again not difficult to see that this produces the same output as the previous machine, but this time using only one \textit{m}-configuration.
+It is again not difficult to see that this produces the same output as the previous machine, but this time using only one state.
 
-An example of a more complex FSM is shown below, which generates the sequence \texttt{010110111011110111110...} again on alternate squares, beginning at the fifth square.
+An example of a more complex Turing machine is shown below, which generates the sequence \texttt{010110111011110111110...} again on alternate cells, beginning at the fifth cell.
+\cite{turing1936computablenumbers}
 
@@
 The operation of such a machine is significantly more complex than the earlier one.
-Key to the operation is the fact that squares are paired, firstly into primary squares or \textit{p}-squares (odd-numbered squares) on which the symbols of the output sequence are printed.
-Only the symbols \texttt{0} and \texttt{1} will ever be printed on these squares.
-To the right of each \textit{p}-square is a secondary square, or \textit{s}-square (an even-numbered square).
-These squares will either be left empty or will contain a 'marker' symbol, which marks the symbol on the \textit{p}-square to the left.
+Key to the operation is the fact that cells are paired into value cells (odd-numbered cells) on which the symbols of the output sequence are printed.
+Only the symbols \texttt{0} and \texttt{1} will ever be printed on these cells.
+To the right of each value cell is a label cell (an even-numbered cell).
+These cells will either be left empty or will contain a 'marker' symbol, which labels the symbol on the value cell to the left.
 These symbols can be erased and overwritten, and are not part of the output sequence.
-Only one \textit{s}-square is needed to contain multiple markers, or more descriptive markers for a single \textit{p}-square, as this can be achieved with a sufficiently rich variety of marker symbols.
+Only one label cell is needed to contain multiple markers, or more descriptive markers for a single value cell, as this can be achieved with a sufficiently rich variety of marker symbols.
+This method is frequently used by Alan Turing in \cite{turing1936computablenumbers}.
 
-This machine operates by first printing the symbols \texttt{e e 0} at the start of the tape, before printing the first \texttt{0} of the sequence on the fifth square, finishing on the third square and moving to state $\mathbb{A}$.
+This machine operates by first printing the symbols \texttt{e e 0} at the start of the tape, before printing the first \texttt{0} of the sequence on the fifth cell, finishing on the third cell and moving to state $\mathbb{A}$.
 (in future I shall represent this finishing state as $\rightarrow \mathbb{A}$).
@@
 
-If $\mathbb{C}$ is triggered, the cursor moves leftwards through the markers: if an \texttt{x} is found it is erased and $\rightarrow \mathbb{B}$; if the cursor reaches the beginning (an \texttt{e} is found) $\rightarrow \mathbb{D}$.
+If $\mathbb{C}$ is triggered, the cursor moves leftwards through the labels: if an \texttt{x} is found it is erased and $\rightarrow \mathbb{B}$; if the cursor reaches the beginning (an \texttt{e} is found) $\rightarrow \mathbb{D}$.
 
-If $\mathbb{D}$ is triggered, the symbol \texttt{0} is appended to the output sequence, the cursor moves to the previous \textit{p}-square and $\rightarrow \mathbb{A}$.
+If $\mathbb{D}$ is triggered, the symbol \texttt{0} is appended to the output sequence, the cursor moves to the previous value cell and $\rightarrow \mathbb{A}$.
 
@@
 
-It is clear from this example that the operation of the FSM is very different from that of an ordinary computer.
-However, the core components are still mostly present - conditionals in the form of the symbol tests in the second column, variables in the form of markers, and continuity and looping when a state triggers itself - a form of recursion.
-The end result is the same - a solution is produced in the form of the computable sequence written on the \textit{p}-squares, and the machine can continue this sequence without halting indefinitely.
+It is clear from this example that the operation of the Turing Machine is very different from that of an ordinary computer.
+However, the core components are still mostly present - conditionals in the form of the symbol tests in the second column, variables in the form of labels, and continuity and looping when a state triggers itself - a form of recursion.
+The end result is the same - a solution is produced in the form of the computable sequence written on the value squares, and the machine can continue this sequence without halting indefinitely.
 Unfortunately, the operation of this machine is somewhat complex and involved.
-To simplify this, we will introduce a type of function for the FSM.
+To simplify this, we will introduce a type of function for the Turing machine.
 
@@
 
-\textit{M}-functions are effectively an extension of \textit{m}-configurations.
-They are described by a lowercase letter and a set of arguments contained in brackets - arguments in gothic script refer to \textit{m}-configurations (or other \textit{m}-functions), and arguments in italics refer to symbols.
-When an \textit{m}-function is triggered, the italic and gothic symbols in the description are substituted by the supplied arguments (much like in $\lambda$-calculus).
+\textit{M}-functions are effectively an extension of states described by Turing in \cite{turing1936computablenumbers}.
+They are denoted by a lowercase letter and a set of arguments contained in brackets - arguments in gothic script refer to states (or other \textit{m}-functions), and arguments in italics refer to symbols.
+When an \textit{m}-function is triggered, the italic and gothic symbols in the description are substituted by the supplied arguments (similar to application in $\lambda$-calculus).
 An example of an \textit{m}-function would be the function $\mathbb{f}$ below:
@@
 
-The function $\mathbb{f}$ takes three arguments - the \textit{m}-configurations \textfrak{C} and \textfrak{E} and the symbol \textit{a}.
+The function $\mathbb{f}$ takes three arguments - the states \textfrak{C} and \textfrak{E} and the symbol \textit{a}.
 It is not difficult to see that if $\rightarrow \mathbb{f}$($\mathbb{A}$,$\mathbb{B}$,x) the cursor would trigger $\mathbb{A}$ at the leftmost occurrence of \texttt{x}.
-If no symbols \texttt{x} were found, \textfrak{E} would be triggered on the marker of the first empty \textit{p}-square.
+If no symbols \texttt{x} were found, \textfrak{E} would be triggered on the marker of the first empty value square.
 
 The use of \textit{m}-functions greatly simplifies the table descriptions, as certain operations are common to many machines.
-Of course, any table description that includes or refers to \textit{m}-functions can be written as an ordinary table as described in \cref{sec:FSMintro}.
-This is possible because of the finite nature of both symbols and \textit{m}-configurations; simply by listing in separate rows under the same \textit{m}-configuration every permutation of symbols and \textit{m}-configurations that the function could possibly take substituted in.
+Of course, any table description that includes or refers to \textit{m}-functions can be written as an ordinary table as described in \cref{sec:TMacIntro}.
+This is possible because of the finite nature of both states and symbols; simply by listing in separate rows under the same state every permutation of the finite symbols and states that the function could possibly take substituted in.
 
@@
     \hhline{----}
-    $\mathbb{p1}$(\textfrak{C}, \textfrak{E}) & - & P\texttt{1} & \textfrak{C} & Prints \texttt{0} \\
+    $\mathbb{p1}$(\textfrak{C}, \textfrak{E}) & - & P\texttt{1} & \textfrak{C} & Prints \texttt{1} \\
     \hhline{----}
-    $\mathbb{ps}$(\textit{s},\textfrak{C}, \textfrak{E}) & - & P\textit{s} & \textfrak{C} & Prints \texttt{0} \\
+    $\mathbb{ps}$(\textit{s},\textfrak{C}, \textfrak{E}) & - & P\textit{s} & \textfrak{C} & Prints \textit{s} \\
     \hhline{====}
@@
 At this point, the similarity between Turing machines and modern computers becomes very clear.
-The machine is able to store more complex information, from integers to strings of characters to images, as binary sequences of \textit{p}-square \texttt{0}s and \texttt{1}s - these shall be stored on the tape as memory.
-The first data structure we shall define is the simple boolean - only 1 bit (1 \textit{p}-square) long.
-In order to identify these sequences on the tape as booleans, we shall mark the first character of the boolean with an identifier (we shall call these pointers) unique to that boolean variable - for example the symbol \texttt{\textbf{B}myvar} (bear in mind this is one symbol, not six) would mark a boolean named \textit{myvar}.
+The machine is able to store more complex information, from integers to strings of characters to images, as binary sequences of value square \texttt{0}s and \texttt{1}s - these shall be stored on the tape as memory.
+The first data structure we shall define is the simple boolean - only 1 bit (1 value square) long.
+In order to identify these sequences on the tape as booleans, we shall label the first character of the boolean with an identifier (we shall call these pointers) unique to that boolean variable - for example the symbol \texttt{\textbf{B}myvar} (bear in mind this is one symbol, not six) would mark a boolean named \textit{myvar}.
 Let us define some \textit{m}-functions to define and assign values to variables of the boolean type:
@@
     \hhline{====}
-    $\mathbb{\mathbf{b}copy}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}copy}_1$(\textit{w}, \textfrak{C}, \textfrak{E}), \textfrak{E}, \textit{r}) \\
+    $\mathbb{\mathbf{b}copy}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$(\textit{r}, $\mathbb{\mathbf{b}copy}_1$(\textit{w}, \textfrak{C}, \textfrak{E}), \textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}), \textfrak{E}, \textit{w}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}), \textfrak{E}, \textit{w}) \\ 
+    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p0}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p1}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\ 
                                                                                        & Other & - & \textfrak{E} \\
@@
 
-The first takes one pointer \textit{p}, finds the first free bit (\textit{p}-square) on the tape, writes the dummy value of \texttt{0} to it and marks it with \textit{p}.
-This method of appendng makes the assumption that no \textit{p}-squares are left empty across the used tape - in order to preserve this, we shall only append to \textit{p}-squares directly at the end of the used tape, and we shall never erase \textit{p}-squares.
+The first takes one pointer \textit{p}, finds the first free bit (value square) on the tape, writes the dummy value of \texttt{0} to it and marks it with \textit{p}.
+This method of appending makes the assumption that no value squares are left empty across the used tape - in order to preserve this, we shall only append to value squares directly at the end of the used tape, and we shall never erase (only overwrite fully) value squares.
 The second very simply finds the bit at pointer \textit{r}, and branches to write either \texttt{0} or \texttt{1} at the bit at the pointer \textit{w}.
@@
 \medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    $\mathbb{\mathbf{b}neg}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}neg}_1$(\textit{w},\textfrak{C}),\textfrak{E}) \\
+    $\mathbb{\mathbf{b}not}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$(\textit{r}, $\mathbb{\mathbf{b}not}_1$(\textit{w}, \textfrak{C}, \textfrak{E}), \textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}neg}_1$(\textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}, \textfrak{E}), \textfrak{E}, \textit{w}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}, \textfrak{E}), \textfrak{E}, \textit{w}) \\ 
+    \multirow{3}{*}{$\mathbb{\mathbf{b}not}_1$(\textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p1}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p0}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\ 
                                                                                        & Other & - & \textfrak{E} \\
@@
 \medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    $\mathbb{\mathbf{b}and}$(\textit{a}, \textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}and}_1$(\textit{b}, \textit{w}, \textfrak{C}), \textfrak{E}) \\
+    $\mathbb{\mathbf{b}and}$(\textit{a}, \textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$(\textit{a}, $\mathbb{\mathbf{b}and}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}), \textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$($\mathbb{p0}$(\textfrak{C}), \textfrak{E}, \textit{w}) \\
+    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p0}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\
                                                                                        & \texttt{1} & - & $\mathbb{\mathbf{b}copy}$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}) \\ 
@@
     \hhline{====}
-    $\mathbb{\mathbf{b}or}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}or}_1$(\textit{w}, \textfrak{C}), \textfrak{E}) \\
+    $\mathbb{\mathbf{b}or}$(\textit{a}, \textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$(\textit{a}, $\mathbb{\mathbf{b}or}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}), \textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}or}_1$(\textit{w}, \textfrak{C}, \textfrak{E})} 
+    \multirow{3}{*}{$\mathbb{\mathbf{b}or}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})} 
                                                                                        & \texttt{0} & - & $\mathbb{\mathbf{b}copy}$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{fl}$($\mathbb{p1}$(\textfrak{C}), \textfrak{E}, \textit{w}) \\ 
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p1}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\ 
                                                                                        & Other & - & \textfrak{E} \\
     \hhline{====}
-    $\mathbb{\mathbf{b}xor}$(\textit{r}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$($\mathbb{\mathbf{b}xor}_1$(\textit{w}, \textfrak{C}), \textfrak{E}) \\
+    $\mathbb{\mathbf{b}xor}$(\textit{a}, \textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})   & - & - & $\mathbb{fl}$(\textit{a}, $\mathbb{\mathbf{b}xor}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}), \textfrak{E}) \\
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}xor}_1$(\textit{w}, \textfrak{C}, \textfrak{E})} 
+    \multirow{3}{*}{$\mathbb{\mathbf{b}xor}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})} 
                                                                                        & \texttt{0} & - & $\mathbb{\mathbf{b}copy}$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}) \\
@@
 In each of these, the first argument \textit{a} is observed, and an action which either writes a \texttt{1} or \texttt{0}, or copies or negates from \textit{b} depending on the truth tables, in a very similar manner to $\lambda$-calculus.
-Gradually, the cryptic and simplified language of Finite State Machines is yielding results similar to that of a computer.
+Gradually, the cryptic and simplified language of Turing machines is yielding results similar to that of a computer.
 
 \subsection{Scripted Configurations}
-As we have moved into more and more complex FSM functions, it can be noted that the middle two columns of the FSM are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions.
+As we have moved into more and more complex Turing machine functions, it can be noted that the middle two columns of the description are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions.
 We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, and $\mathbb{p1}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.
@@
 Therefore, we will use our function method to define what is effectively a list of commands for the machine which will be executed in order.
-The main difference in this system is that, as the \textfrak{C} argument is always the function that must be run when that function is completed (except in the case of the conditional function), on interpretation of the language the entire operation of the machine after that point must be passed as the \textfrak{C} argument to that function in order for the functions to be called sequentially.
-The following function main() defines variables \textit{var1} and \textit{var2}, and sets \textit{var2} to be not \textit{var1}, or \texttt{1}.
+The main difference in this system is that, as the \textfrak{C} argument is always the function that must be run when that function is completed (except in the case of the conditional function), on interpretation of the language the entire operation of the machine after that point must be passed as the \textfrak{C} argument to that function in order for the functions to be called sequentially\footnote{For clarity, I have ignored error handling (i.e.
+omitted the E argument).}.
+The following function main() defines variables \textit{var1} and \textit{var2}, and sets \textit{var2} to be \textit{var1} negated, or \texttt{1}.
 
@@
 \end{lstlisting}
-For clarity, I have ignored error handling (i.e. omitted the E argument). This is equivalent to:
+This is equivalent to:
 
@@
 \end{lstlisting}
-with arguments for continuity and simple error correction. This, in turn, can be simplified into a table.
+with arguments for continuity and simple error correction. This, in turn, can be simplified into a description table.
 
-Furthermore, we can simplify certain functions to have their own specific syntax. In the case of definitions, "\lstinline{bdef(var)}" shall be abbreviated to "\lstinline{bool var}";
+\subsection{Conclusion}
+
+Turing machines are truly remarkable entities.
+While $\lambda$-calculus was able to mimic the operation of a modern computer (behaving like a purely functional programming language such as Haskell), its beginnings were completely abstract - the mathematical operations of abstraction and application, while being probably more useful than Turing machines in yielding results, were unlike anything which could actually be created in the real world.
+However, Turing machines are completely grounded in physical reality, and it is totally conceivable how one could create such a machine - despite this, they are able to produce results very similar to that of an imperative programming language such as Java - data storage, typed and referenceable variables, and boolean logic, all performed as a sequence of commands.
+From these building blocks, integers and more complex concepts can be produced.
+This is the truly remarkable thing about Turing machines - they illustrate clearly how mechanisms can in fact solve computable problems.
+As such, it is most useful to define a computer as something which is able to behave like a Turing machine - in effect, a computer is distinguished by the fact that it can simulate a Turing machine.
+A machine with this ability shall be called 'Turing-complete'
 

### 2017-04-19 Draft 2/Section 3 - Universality.tex
Colossal changes to all sections
Added referencing, changed language of turing machines, more detailed
intros&concns

@@
 So far, we have explored how our two methods of computation can perform many common operations, including data manipulation \& storage, on top of looping and conditional branching.
-Unfortunatley, it is too vague to simply define a 'comuputer' as a system which can perform a somewhat arbitrary set of operations - we must refine this to a simple set of functions.
+Unfortunately, it is too vague to simply define a 'comuputer' as a system which can perform a somewhat arbitrary set of operations - we must refine this to a simple set of functions.
 The easiest way of doing this is by assuming that a certain system can perform every operation a computer can perform.
-For this purpose, we will choose Turing machines, for purposes that will become clear later.
-Now, in order to prove that any system is a 'computer', we must simply prove that it can perform any operation a Turing machine can perform - in essence, it must be able to fully emulate the operation of a Turing FSM.
+For this purpose, we have chosen Turing machines, due to the fact that they are easy to realise physically.
+Now, in order to prove that any system is a 'computer', we must simply prove that it can perform any operation a Turing machine can perform - in essence, it must be able to fully emulate the operation of a Turing machine.
 
  This essentially means that a machine, given a specific Turing machine starting configuration, should be able to produce every consecutive following state (i.e.
-it takes an FSM description table as input, and generates an infinite sequence of following tape \& \textit{m}-configuration states).
+it takes a machine's description table as input, and generates an infinite sequence of the following tape configurations \& the corresponding finishing state for that step).
 Any machine that can do this shall be called a \textit{Universal Machine}.
@@
 First, we must define what we actually mean by a description table - we shall do this by describing a standard form for these tables.
-Looking at the first table described, we can see that any sequence described in the operations section of the table follows a similar format: E; [E, R]; [E, L]; P\textit{a}; [ P\textit{a}, R]; [ P\textit{a}, L] or no entry at all.
-A more complex set of operations such as those found in later tables can always be put into one of these forms through the addition of intermediary \textit{m}-configurations which are called in sequence.
+Looking at the first table described, we can see that any transition function follows a similar format: E; [E, R]; [E, L]; P\textit{a}; [ P\textit{a}, R]; [ P\textit{a}, L] or no entry at all.
+More complex transition functions such as those found in later tables can always be put into one of these forms through the addition of intermediary states which are called in sequence.
 
-Next, let us rename the \textit{m}-configurations as $q_0$, $q_1$, $q_2$, $...$, $q_n$ for clarity (the initial \textit{m}-configuration shall always be called $q_0$, the second $q_1$ and so on).
+Next, let us rename the states as $q_0$, $q_1$, $q_2$, $...$, $q_n$ for clarity (the initial state shall always be called $q_0$, the second $q_1$ and so on).
 Furthermore, the symbols shall be renamed $S_0$, $S_1$, $S_2$, $...$, $S_n$ - in this case, $S_0$ will represent the blank square, $S_1$ will represent \texttt{0} and $S_2$ will represent \texttt{1}.
-The movement transformations L and R will be renamed $M_L$, $M_R$, and the operation to keep the tape stationary is simply $M_S$.
+The movement operations L and R will be renamed $M_L$, $M_R$, and the operation to keep the tape stationary is simply $M_S$.
 Our tables are now of form:
@@
 in order for all lines to be written in the first format.
-As the number of symbols used for a machine is always finite as the number of states is finite, it is possible to enumerate under every single \textit{m}-configuration an action for every single symbol $S_i$ that the machine coud be reading.
+As the number of symbols used for a machine is always finite, it is possible to enumerate under every single state an action for every single symbol $S_i$ that the machine could be reading.
 In this way, "All" and "Not \textit{a}" will be portrayed in this format as the enumerated behaviours for every relevant symbol.
@@
 Firstly, we shall prove that $\lambda$-calculus is Turing complete by building a universal machine using only $\lambda$-functions.
-The core of the machine will be a function which calculates a single step in the FSM's calculation: It will receive as its parameters the current state of the tape and the current \textit{m}-configuration.
-As this function will be unique to the specific FSM that is being emulated, the entire behavior of the machine based on this configuration (i.e.
+The core of the machine will be a function which calculates a single step in the Turing machine's calculation: It will receive as its parameters the current configuration of the tape and the current state.
+As this function will be unique to the specific machine that is being emulated, the entire behaviour of the machine based on this configuration (i.e.
 the machine's table) shall be contained within this function.
@@
 First of all, ordered lists - these will be used to describe the current content of the tape.
-These are defined as a sequence of nodes, where each node is a pair with the first element as the content of the node and the second element is the next node in the sequence.
+These are defined as a sequence of nodes, where each node is a pair with the first element as the content of the node and the second element is the next node in the sequence (as shown in \cite{tromp2007binary}).
 The final node will have \textbf{0} as its first element to signify the end of the list - the second element will never be referred to; as such \textbf{0} will be used as a placeholder (of course this only works if the list is not designed to contain any values of zero or true, as they will be indistinguishable from the end marker - I shall use \textbf{1} to represent $S_0$, \textbf{2} to represent $S_1$ and so on).
@@
 
-The tape of the FSM extends infinitely in both directions either side of the cursor.
-We shall represent this as a pair of lists, $T_p$ as the list of all the predecessors to the cursor and $T_s$ as the list of all the successors to the cursor.
+The tape of the machine extends infinitely in both directions either side of the cursor.
+We shall represent this as a pair of lists: $T_p$ as the list of all the predecessors to the cursor and $T_s$ as the list of all the successors to the cursor.
 The predecessors shall be listed in reverse order, such that the head of $T_p$ is the symbol directly to the left of the cursor.
@@
 \subsubsection{Movement Operations}
-To emulate cursor movement, we will create transformation functions for the tape. These functions will shift the tape by moving the head of $T_s$ to the head of $T_p$ or vice versa.
+To emulate cursor movement, we will create transformation functions for the tape. These operations will shift the tape by moving the head of $T_s$ to the head of $T_p$ or vice versa.
 
@@
 \bm{M}_R &= \lambda t_a f.f [\bm{\mathrm{:}}([t_a\bm{\mathrm{F}}]\bm{\mathrm{T}})(t_a\bm{\mathrm{T}})] [(t_a\bm{\mathrm{F}})\bm{\mathrm{F}}]\\
-\bm{M}_S &= \lambda x.x\\
+\bm{M}_S &= \lambda t_a.t_a\\
 \end{aligned}
@@
 Unfortunately, the tape which we are currently dealing with is unlike that of a Turing machine, due to the fact that it is of finite length - we cannot write a single list in $\lambda$-calculus which expresses the entire tape.
-As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, we will replace it with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as he tail.
+As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, we will replace it with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as the tail.
 To do this, we will have another transformation function which will check if either head element of the tape pair is \textbf{0}, and if so, will replace it with an empty square node $\bm{\epsilon}$ - otherwise it will simply be replaced with the original head:
@@
 \bm{\epsilon} &= \lambda g.g[\bm{\textbf{1}}][\lambda d.d\bm{\mathrm{0}}\bm{\mathrm{0}}] \\
-\bm{C} &= \lambda t_a g.g[\bm{\mathrm{Z}}(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})(\bm{\epsilon})(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})][\bm{\mathrm{Z}}(t_a\bm{\mathrm{F}}\bm{\mathrm{T}})(\bm{\epsilon})(t_a\bm{\mathrm{F}}\bm{\mathrm{T}})]
+\bm{C} &= \lambda t_a g.g[\bm{\mathrm{Z}}(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})(\bm{\epsilon})(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})][\bm{\mathrm{Z}}(t_a\bm{\mathrm{F}}\bm{\mathrm{T}})(\bm{\epsilon})(t_a\bm {\mathrm{F}}\bm{\mathrm{T}})]
 \end{aligned}
@@
 
-The transformation that writes a given real number to the square beneath the cursor is not particularly complex - it simply replaces the current head of $T_s$ with a successor.
+The operation function that writes a given symbol to the square beneath the cursor is not a particularly complex transformation - it simply replaces the current head of $T_s$ with the given numeral $a$.
 
 \begin{equation*}
-\bm{W} = \lambda a t_a p.p[t_a\bm{\mathrm{T}}][\lambda d.d(a)(t_a\bm{\mathrm{FF}})]
+\bm{W} = \lambda a t_a p.p[t_a\bm{\mathrm{T}}][\mathrm{\bm{:}} a (t_a \bm{\mathrm{FF}})]
 \end{equation*}
 
-\subsubsection{Storing \& Accessing \textit{m}-configurations}
+\subsubsection{Storing \& Accessing states}
 %\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}
-Once again, in order to store the information and operations associated with each \textit{m}-configuration, we shall use another list.
+Once again, in order to store the symbol, transition function and final state associated with each states, we shall use a list.
 The first element of the list shall represent $q_0$, the second $q_1$ and so on.
 Each element of the list will be a list in itself.
-Each element of this list shall refer to the symbol aspect of the configuration.
-These elements are pairs: the first element being the symbol to be found (a real number), the second being the action to be performed under this configuration.
+Each element of this nested list shall refer to a single line described by the symbol aspect of the configuration.
+These elements are pairs: the first element being the symbol to be found (a numeral), the second being the action to be performed under this configuration.
 
 The action itself will be yet another pair.
-The first element is the transformation that should be performed on the tape - this transformation will be of the form $(\bm{C})(\bm{M}_{L/R/S})(\bm{W}a)$, which applies first a write transformation before a movement transformation and the tape length correction transformation.
-The second element is a function which, when given the description of the machine, finds the given \textit{m}-configuration.
+The first element is the transition function that should be executed on the tape - this will be of the form $(\bm{C})(\bm{M}_{L/R/S})(\bm{W}a)$, which applies first a write operation before a movement operation and the tape length correction operation.
+The second element is a function which, when given the description of the machine, finds the given state.
 We shall note these m-configuration references as shown, with the example of the reference to $q_3$:
@@
 
-In order to find which action should be performed given a certain configuration, we shall use the following function which produces a pair of a list transformation and an \textit{m}-config reference from a current \textit{m}-config, the current symbol, and the description function.
+In order to find which action should be performed given a certain configuration, we shall use the following function which produces a pair of a list transition function and an state reference from a current state, the current symbol, and the description function.
 As part of this function, the recursive function $\bm{\rho}$ must be used in conjunction with the \textbf{Y} combinator, which returns the action aspect of the first pair under symbol $s$ in list $l$ (the $r$ argument is the argument which would represent the function as a whole, and is recursively called by the \textbf{Y} combinator)
@@
 
-At last, we can involve all of these functions to create a single operation which transforms a given machine configuration (\textit{m}-config, $T_p$ \& $T_s$, and the description table) into the machine configuration for the next state.
-This configuration shall be represented as a pair, the first element being a pair of the \textit{m}-config reference and the tape, and the second element as the description table.
+At last, we can involve all of these functions to create a single operation which transforms a given machine configuration (state, $T_p$ \& $T_s$, and the description table) into the machine configuration for the next state.
+This configuration shall be represented as a pair, the first element being a pair of the state reference and the tape, and the second element as the description table.
 The $\bm{\nu}$ function gets the action function from the given machine configuration.
@@
 
+\subsection{Conclusion}
+
+We have successfully shown here that $\lambda$-calculus is a Universal, Turing-complete language - it is able to perform every action that a Turing Machine can perform, and as such is at least as powerful as Turing's method of computation.
+Furthermore - and this the reader must take on faith, or rely on intuition - it is possible for a Turing machine to simulate $\lambda$-calculus; Turing machines are Effectively Calculable, and are at least as powerful as the $\lambda$-calculus.
+Therefore, these two methods of computation - one based in physical ideas, one based in conceptual ideas, are totally equivalent.
+Intuitively, it is clear that both use similar logical processes, similar to the workings of the logical aspect of human thought, and as such this result is unsurprising.
+However, what is truly remarkable is that what appears to be a Platonic reality of the concept of computability has been stumbled upon by two different methods designed independently of each other.
+This strengthens the idea of computability as defined this way, and gives us a very solid foundation from which to base our exploration of physical machines.
+
 \end{document}

### 2017-04-20 Draft 2/Master.tex
Included bibliography
Added remaining files, included in Master.pdf, commented out sections for
testing
Removed comments and updated lambda rojas reference
Colossal changes to all sections
Added referencing, changed language of turing machines, more detailed
intros&concns
Introduction
Moving from nothing to something

--- 2017-02-23 Draft 2/Master.tex
@@
 \usepackage{subfiles}
-\usepackage{blindtext}
 \usepackage{amsmath}
@@
 \usepackage{amsthm}
+\usepackage{blindtext}
 \usepackage{bm}
+\usepackage{cleveref}
+\usepackage{hhline}
+\usepackage{listings}
+\usepackage[bb=boondox]{mathalfa}
 \usepackage{multirow, bigdelim}
-\usepackage{hhline}
 \usepackage{tabu}
-\usepackage[bb=boondox]{mathalfa}
 \usepackage{yfonts}
-\usepackage{cleveref}
-\usepackage{listings}
 
@@
 \author{Max Penrose}
+
+\crefname{section}{§}{§§}
+\Crefname{section}{§}{§§}
 
@@
 \clearpage
+\textit{TODO: introduction - stating aim of checking whether computers produced during and after WW2 were 'computers'}
+
+Computation rules the modern world - from the internet to the rise of automated labour, today's humanity puts colossal value in the hands of computers, taking them for granted as the remarkable machines they are.
+However, the fundamental ideas of computation and calculation lying alongside the transistors and silicon at the heart of this revolution are no less remarkable in themselves, primarily down to their simplicity.
+Furthermore, it is difficult for any modern computer user to see how basic electronics can operate the tasks a computer can perform.
+Therefore, I feel the natural way to shed light on this question is to look at the earliest and simplest computers, what they could do and what was distinctive about them.
+
+The most significant problem in answering this question is the actual definition of `computer'.
+In the early 20th Century, prior to developments in this field, any human which evaluated statements through computation was known, logically, as a `computer'.
+As such, we must explore the qualities that an entity - human, machine or other - must have to be able to perform computation.
+
+\textit{(Leibniz's ideas of computation, all effectively computable statements could be expressed in terms of a simple language \& a method to evaluate these statements - highlighting ideas of solving problems)}
+
+Therefore, in order for a machine to be called a `computer', it must be able to evaluate any member of a set of computable functions.
+However, this is an abstract notion - to clarify it, we must define a simple language to define computable functions, and find a simple method to evaluate them.
+We shall explore the two most common methods - the abstract $\lambda$-calculus and the
 
@@
 \subfile{"Section 3 - Universality"}
-
+\bibliography{bibliography}
+\bibliographystyle{unsrt}
 \end{document}

### 2017-04-20 Draft 2/Section 3 - Universality.tex
Introduction
Moving from nothing to something

@@
 
-First, we must define what we actually mean by a description table - we shall do this by describing a standard form for these tables.
+First, we must define what we actually mean by a description table - we shall do this by describing a standard form for these tables, as shown by Turing in \cite{turing1936computablenumbers}.
 Looking at the first table described, we can see that any transition function follows a similar format: E; [E, R]; [E, L]; P\textit{a}; [ P\textit{a}, R]; [ P\textit{a}, L] or no entry at all.

### 2017-04-20 Draft 2/Master.tex
Finished off introduction

@@
 \clearpage
-\textit{TODO: introduction - stating aim of checking whether computers produced during and after WW2 were 'computers'}
 
+\section*{Introduction}
 Computation rules the modern world - from the internet to the rise of automated labour, today's humanity puts colossal value in the hands of computers, taking them for granted as the remarkable machines they are.
@@
 However, this is an abstract notion - to clarify it, we must define a simple language to define computable functions, and find a simple method to evaluate them.
-We shall explore the two most common methods - the abstract $\lambda$-calculus and the
+We shall explore the two most common methods, the $\lambda$-Calculus and the Turing Machine, and evaluate them in terms of their similarities and differences, before exploring how well this definition is fulfilled by early computers.
 

### 2017-04-20 Draft 2/Section 1 - Lambda Calculus.tex
Finished off introduction

@@
 The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability, far from the very real and mechanical world of Turing.
-It deals with a set of objects - for our purposes denoted with singl  e symbolic characters - which define what school mathematics or common computer science would call `functions'.
+It deals with a set of objects - for our purposes denoted with single symbolic characters - which define what school mathematics or common computer science would call `functions'.
 These functions take as their arguments (other objects which the functions act upon) functions alone, and can also output only functions.

### 2017-04-22 Draft 2/Appendices.tex
Moved some things to appendices

--- 2017-04-20 Draft 2/Section 1 - Lambda Calculus.tex
@@
 \begin{document}
-
-The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability, far from the very real and mechanical world of Turing.
-It deals with a set of objects - for our purposes denoted with single symbolic characters - which define what school mathematics or common computer science would call `functions'.
-These functions take as their arguments (other objects which the functions act upon) functions alone, and can also output only functions.
-Take, for example the function $f$:
-\begin{equation*}
-f = ab
-\end{equation*}
-This particular function $f$ applies the function $a$ to the function $b$.
-Note that while commonly we would use the syntax $a(b)$ to express the same thing, it greatly simplifies expression to use this format.
-Church defines these functions through the method of `abstraction' - let us look at a different function to illustrate:
-\begin{equation*}
-\lambda u.tu
-\end{equation*}
-This function takes one single argument, which it names the abstract name $u$.
-It then applies the function $t$ to $u$ and outputs the result.
-For example, if we were to apply this function to the function $a$:
-\begin{equation*}
-(\lambda u.tu) a = ta	
-\end{equation*}
-
-Functions can take multiple arguments through the use of nesting:
-\begin{gather*}
-\begin{aligned}
-\lambda a.(\lambda b.ba) &=  \lambda ab.ba \\
-[\lambda a.(\lambda b.ba)]uv &= (\lambda b.bu)v \\ &= vu
-\end{aligned}
-\end{gather*}
-
-\subsection{Arithmetical definitions}
-
-Church uses this medium to define a variety of concepts we are already familiar with - firstly, that of positive integers.
-\cite{church1941lambda}
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{0}} &= \lambda sz.z,
-  & % seperation
-\bm{\mathrm{1}} &= \lambda sz.sz,
-  \\
-\bm{\mathrm{2}} &= \lambda sz.s(sz),
-  &
-\bm{\mathrm{3}} &= \lambda sz.s(s(sz)),
-  &
-etc.
-\end{aligned}
-\end{equation*}
-Here it can be seen that for each number \textit{n} the argument $s$ is applied to the argument $z$ \textit{n} times - the $s$ functions representing \textit{n} successors to zero ($z$).
-
-From this, it is not difficult to define an operation that takes a number as input and increments it by 1 - such a function would take three arguments (the first being the number, and the second two being the arguments $s$ and $z$ for the number) and would apply the argument $s$ to the number:
-\cite{rojas2015lambdatutorial}
-\begin{equation*}
-\bm{\mathrm{S}} = \lambda wyx.y(wyx)
-\end{equation*}
-Let us test our new successor function by applying it to \textbf{2}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{S2}} &= (\lambda wyx.y(wyx)) (\lambda sz.s(s(z)))\\
-&= \lambda yx.y([\lambda sz.(s(s(z)))]yx)\\
-&= \lambda yx.y(y(y(z)))\\
-&= \lambda sz.s(s(s(z)))\\
-&= \bm{\mathrm{3}}
-\end{aligned}
-\end{gather*}
-
-From this concept, we are not far from the nursery-school concept of addition.
-Remembering that each number applies the function $s$ to $z$ \textit{n} times, and that addition is simply incrementing \textit{a} \textit{b} times, addition is as simple as:
-\cite{rojas2015lambdatutorial}
-\begin{equation*}
-a\bm{\mathrm{S}}b	
-\end{equation*}
-Let us test this by summing \textbf{2} and \textbf{3}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{2S3}} &= (\lambda sz.s(s(z))) \bm{\mathrm{S}} \bm{\textrm{3}}\\
-&= \bm{\mathrm{S}} (\bm{\mathrm{S}} (\bm{\mathrm{3}}))\\
-&= \bm{\mathrm{S}} (\bm{\mathrm{4}})\\
-&= \bm{\mathrm{5}}
-\end{aligned}
-\end{gather*}
-
+\appendix
+\appendixpage
+\section{Further Arithmetic in $\lambda$-Calculus}
 Multiplication can also be calculated by defining the function \textbf{M}:
@@
 \end{gather*}
-
-\subsection{Boolean Logic}
-
-Church defines functions to operate boolean logic, most significantly defining True and False:
-\cite{rojas2015lambdatutorial}
-
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{T}} &= \lambda ab.a,
-  & % seperation
-\bm{\mathrm{F}} &= \lambda ab.b
-\end{aligned}
-\end{equation*}
-These functions each take two arguments - the \textbf{T} function returns the first, while the \textbf{F} function returns the second.
-
-These concepts are the base of conditional branching in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
-For such operations, the concept of a `pair' exists:
-\cite{church1941lambda}
-\begin{equation*}
-\lambda x.xab
-\end{equation*}
-where $a$ and $b$ are functions. For a choice of an element from the pair, the argument of either \textbf{T} or \textbf{F} is provided:
-\begin{gather*}
-\begin{aligned}
-(\lambda x.xab)\bm{\mathrm{T}} &= a\\
-(\lambda x.xab)\bm{\mathrm{F}} &= b
-\end{aligned}
-\end{gather*}
-
-Functions representing boolean operations can also be defined:
-\cite{rojas2015lambdatutorial}
-\begin{gather*}
-\begin{aligned}
-\vee &= \lambda xy.x\bm{\mathrm{T}}y\\
-\wedge &= \lambda xy.xy\bm{\mathrm{F}}\\
-\lnot &= \lambda x.x\bm{\mathrm{FT}} \\
-\veebar &= \lambda xy.x(\lnot y)y
-\end{aligned}
-\end{gather*}
-The derivation of such operations is not difficult to understand if one considers the truth tables for each operation, remembering that T selects the first and F selects the second argument - for example, looking at the OR function $\vee$:
-
-\begin{gather*}
-\begin{aligned}
-\vee \bm{\mathrm{TF}} &= \bm{\mathrm{T}}[\bm{\mathrm{T}}][\bm{\mathrm{F}}] \\
-&= \bm{\mathrm{T}} \\
-\vee \bm{\mathrm{FF}} &= \bm{\mathrm{F}}[\bm{\mathrm{T}}][\bm{\mathrm{F}}] \\
-&= \bm{\mathrm{F}} \\
-\vee \bm{\mathrm{FT}} &= \bm{\mathrm{F}}[\bm{\mathrm{T}}][\bm{\mathrm{T}}] \\
-&= \bm{\mathrm{T}} \\
-\end{aligned}
-\end{gather*}
-
-If the first argument is \textbf{T} the function will always return \textbf{T}, as it is the first argument.
-If the first argument is \textbf{F} on the other hand, the value of the second argument will be returned (the $\vee$ function is dependant on at least one argument being \textbf{T} - if this is not the first argument, the outcome is simply whether the second argument is \textbf{T} or not).
-The remaining functions work in a similar way.
-
-\subsection{Basic Comparison operators}
-
-With the fundamental boolean system of our computational system in place, we will next construct comparison operators. The first and simplest of these will test if a number is equal to zero:
-\cite{rojas2015lambdatutorial}
-\begin{equation*}
-\bm{\mathrm{Z}} = \lambda x.x\bm{\mathrm{F\lnot F}}
-\end{equation*}
-To understand this somewhat less than trivial concept, note that \textbf{F} when given only a single argument yields the identity function $\lambda x.x$, and that \textbf{0} applied to any two arguments yields only the second:
-\cite{rojas2015lambdatutorial}
-\begin{equation*}
-\bm{0}ab = (\lambda sz.z)ab = b
-\end{equation*}
-From this, it easier to see how the function works. Firstly with \textbf{0}:
-\cite{rojas2015lambdatutorial}
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{Z0}} &= (\lambda x.x\bm{\mathrm{F\lnot F}})\bm{0}\\
-&= \bm{\mathrm{0F\lnot F}}\\
-&= \bm{\mathrm{\lnot F}}\\
-&= \bm{\mathrm{T}}
-\end{aligned}
-\end{gather*}
-Secondly with \textbf{2}:
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{Z2}} &= (\lambda x.x\bm{\mathrm{F\lnot F}})\bm{2}\\
-&= \bm{\mathrm{2F\lnot F}}\\
-&= (\bm{\mathrm{F}}(\bm{\mathrm{F}}\lnot)) \bm{\mathrm{F}}\\
-&= (\bm{\mathrm{F}}(\lambda x.x))\bm{\mathrm{F}}\\
-&= (\lambda x.x)\bm{\mathrm{F}}\\
-&= \bm{\mathrm{F}} 
-\end{aligned}
-\end{gather*}
-
-However, in order to develop other conditional tests we will need a `predecessor' function - a more complex concept in $\lambda$-calculus.
-\subsection{Subtraction}
-
-The elusive predecessor function was created by Stephen Kleene, a student of Church's, and was something of a landmark in the development of $\lambda$-calculus.
-
-Firstly, the function $\bm{\psi}$ transforms the pair (n, n-1) (the argument $p$) into the pair (n+1, n) (the new pair's elements are an increment and a copy of the first value respectively):
-\cite{rojas2015lambdatutorial}
-\begin{equation*}
-\bm{\psi} = \lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})
-\end{equation*}
-To find the predecessor to $n$ therefore, we apply this function $n$ times to the pair (0, 0) and the pair (n, n-1) is formed, after which the second element can easily be selected.
-\cite{rojas2015lambdatutorial}
-\begin{equation*}
-\bm{\mathrm{P}} = \lambda n.[n \bm{\psi} (\lambda x.\bm{\mathrm{00}})] \bm{\mathrm{F}} 
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{P3}} &= (\lambda n.n [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}] \bm{\mathrm{F}}) [\lambda sz.s(s(s(z)))]\\
-&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
-&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda x.\bm{\mathrm{00}}]))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c(\bm{\mathrm{S}}[\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})([\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c\bm{\mathrm{10}}))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda c.c\bm{\mathrm{21}}]\bm{\mathrm{F}}\\
-&= [\lambda c.c\bm{\mathrm{32}} ])\bm{\mathrm{F}}\\
-&= \bm{\mathrm{2}}
-\end{aligned}
-\end{equation*}
-
-Of course now the subtraction function can be found (using \textbf{D} for difference):
-\begin{equation*}
-\bm{\mathrm{D}} = \lambda ab.b\bm{\mathrm{P}}a
-\end{equation*}
-Bearing in mind the predeces sor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b\geq a$.
-\subsection{Further Conditional Logic}
-
-With this useful quirk of the \textbf{D} function, we can produce comparative logical operators:
-\begin{equation*}
-\begin{aligned}
-\bm{\leq} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}ab)
-  & % seperation
-\bm{\geq} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}ba)
-  \\
-\bm{<} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}a[\bm{\mathrm{S}}b])
-  &
-\bm{>} &= \lambda ab.\bm{\mathrm{Z}}(\bm{\mathrm{D}}[\bm{\mathrm{S}}b]a)
-\end{aligned}
-\end{equation*}
-and through combination of these, we can create the equivalence and inequivalence operators (using $\bm{\doteq}$ for clarity from $=$):
-\begin{equation*}
-\begin{aligned}
-\bm{\doteq} &= \lambda ab.\wedge(\bm{\leq}ab)(\bm{\geq}ab)\\
-\bm{\neq} &= \lambda ab.\vee(\bm{<}ab)(\bm{>}ab)
-\end{aligned}
-\end{equation*}
-\subsection{Recursion}
-
-So far, Church's $\lambda$-Calculus is very close to the operation of a modern programming language.
-It has representation for boolean values, for conditional statements, for positive integers (signed integers can be expressed as a pair of positive integers where the difference is the value to be represented) and arithmetic, as well as set operations for booleans and comparators for integers - In fact, we are very close to our definition of computability, save one thing.
-Continuity and repetition is one of the most significant aspects of computers, the power of this being the ability to transform a finite configuration into a potentially infinite result.
-This is done through one of the most remarkable functions in $\lambda$-Calculus, the \textbf{Y} combinator:
-\cite{rojas2015lambdatutorial}
-\begin{equation*}
-\bm{\mathrm{Y}} = \lambda y.(\lambda x.y(xx))(\lambda x.y(xx))
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{Y}}a &= (\lambda x.a(xx))[\lambda x.a(xx)]\\
-&= a([\lambda x.a(xx)][\lambda x.a(xx)])\\
-&= a(\bm{\mathrm{Y}}a)
-\end{aligned}
-\end{equation*}
-This function is remarkable as it is a `fixpoint operator' - it is able to easily generate a `fixpoint' of any given function (a value $x$ is a fixpoint of the function $f$ if and only if $fx = x$) by applying the function as the first parameter of the \textbf{Y} combinator.
-
-Therefore, the \textbf{Y} combinator applied to any function $a$ applies the function $a$ to the function \textbf{Y} applied to $a$ - if substitution continues, an infinite series of nested $a$ functions is created; an infinite result is produced from a finite configuration.
-Of course we can create finites as well by halting the function - an example of this would be the factorial function, where \textbf{!}a = \textbf{M}a(\textbf{!}[\textbf{P}a]) and \textbf{!0} = \textbf{1}.
-Firstly, a recursive definition:
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{\xi}} &= \lambda fa.\bm{\mathrm{Z}}a\bm{\mathrm{1}}[\bm{\mathrm{M}}a(f[\bm{\mathrm{P}}a])]\\
-\bm{!} &= \bm{\xi}!
-\end{aligned}
-\end{equation*}
-i.e.
-the factorial function is the $\bm{\xi}$ function with itself as the argument $f$.
-Unfortunately such a definition is illegal under $\lambda$-Calculus as all functions are strictly anonymous - this is where the \textbf{Y} combinator comes into play.
-To find the factorial of \textbf{3}:
-\begin{equation*}
-\begin{aligned}
-\bm{\mathrm{Y\xi 3}} &= \bm{\mathrm{\xi}}(\bm{\mathrm{Y\xi}})\bm{\mathrm{3}}\\
-&= \bm{\mathrm{Z31}}[\bm{\mathrm{M3}}([\bm{\mathrm{Y\xi}}][\bm{\mathrm{P3}}])]\\
-&= \bm{\mathrm{M3}}(\bm{\mathrm{Y\xi}}\bm{2})\\
-&= \bm{\mathrm{M3}}(\bm{\mathrm{M2}}(\bm{\mathrm{M11}}))\\
-&= \bm{\mathrm{6}}
-\end{aligned}
-\end{equation*}
-The \textbf{Y} combinator allows for \textbf{Y}$\bm{\xi}$ to be applied as the first argument to the $\bm{\xi}$ function - as a result, the procedure also processes \textbf{2} and \textbf{1}, before stopping at \textbf{0} (which produces simply \textbf{1}.
-To simplify, the factorial function:
-\begin{equation*}
-\bm{!} = \lambda x.\bm{\mathrm{Y\xi}}x
-\end{equation*}
-\subsection{Conclusion}
-
-Our brief stroll through the key aspects of $\lambda$-Calculus is complete.
-We have shown that many basic necessary concepts in a common programming language can be defined through the use of two simple axioms - that of the concept of functions, and the operation of substitution.
-$\lambda$-Calculus was described by Church as an `effectively calculable' system, in that it could perform any calculable calculation.
-In more popular terms, it is Turing-complete - we will look at what this is and why this is the case later on in the project.
-However, it is clear to see that the Calculus is able to simulate many functions of the computer - data storage with pairs (pairs of pairs can be used for storing more than two items of data as shown in \cref{sec:LambdaUnivTape}), conditionals and booleans, integers and arithmetic and, finally, the ability to be continuous (circular) from a finite configuration.
-$\lambda$-calculus is our first attempt to clarify the attributes of a computer, and does so both fundamentally and aesthetically.
 \end{document}

### 2017-04-22 Draft 2/Master.tex
Moved some things to appendices

--- 2017-03-14 Draft 2/Master.tex
@@
 \usepackage{amsthm}
+\usepackage{appendix}
+\usepackage{blindtext}
 \usepackage{bm}
+\usepackage{cleveref}
+\usepackage{hhline}
+\usepackage{listings}
+\usepackage[bb=boondox]{mathalfa}
 \usepackage{multirow, bigdelim}
-\usepackage{hhline}
 \usepackage{tabu}
-\usepackage[bb=boondox]{mathalfa}
 \usepackage{yfonts}
-\usepackage{cleveref}
-\usepackage{listings}
 
@@
 
-In order to achieve this, I must first describe the fundamental attributes a machine must have for it to be called a 'computer'.
-Prior to the war and the development of electronic computation, any human who performed a calculation would  frequently be called a 'computer'.
-However, this specific attribute of computation is difficult to define - to do so, I will be looking at the minimalist  $\lambda$-Calculus developed by Mathematician and Logician Alonzo Church, the famous concept of the Universal Turing Machine created by English Mathematician Alan Turing, and the similarities and differences between these two definitions.
+In the process of defining computability, we shall study the set of problems known as `computable functions' - how to describe them, and how to evaluate them.
 
@@
 
+\subfile{"Appendices"}
+
+\bibliography{bibliography}
+\bibliographystyle{unsrt}
 \end{document}

### 2017-04-22 Draft 2/Section 1 - Lambda Calculus.tex
Moved some things to appendices

--- 2017-04-19 Draft 2/Section 1 - Lambda Calculus.tex
@@
 &= \bm{\mathrm{5}}
-\end{aligned}
-\end{gather*}
-
-Multiplication can also be calculated by defining the function \textbf{M}:
-\cite{rojas2015lambdatutorial}
-\begin{equation*}
-\bm{\mathrm{M}} = \lambda wyx.w(yx)
-\end{equation*}
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{M22}} &= (\lambda wyx.w(yx))(\lambda ab.a(a(b)))(\lambda sz.s(s(z)))\\
-&= \lambda x.(\lambda ab.a(a(b)))[(\lambda sz.s(s(z)))x]\\
-&= \lambda x.(\lambda ab.a(a(b)))[\lambda z.x(x(z))]\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))]([\lambda z.x(x(z))]b))\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))][x(x(b))])\\
-&= \lambda x.(\lambda b.x(x(x(x(b)))))\\
-&= \lambda xb.x(x(x(x(b))))\\
-&= \bm{\mathrm{4}}
-\end{aligned}
-\end{gather*}
-We should rearrange our earlier addition method into an `addition' function of the same format which takes two arguments:
-\begin{equation*}
-\bm{\mathrm{A}} = \lambda ab.b\bm{\mathrm{S}}a
-\end{equation*}
-
-An `exponent' function to find $a^b$can also be defined, of astonishing simplicity:
-\cite{penrose1991emperor}
-\begin{equation*}
-\bm{\mathrm{E}} = \lambda ba.ab
-\end{equation*}
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{E23}} &= (\lambda ab.ab)(\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda z.[\lambda ty.t(t(t(y)))]([\lambda ux.u(u(u(x)))]z))\\
-&= (\lambda z.[\lambda ty.t(t(t(y))][\lambda x.z(z(z(x)))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]y))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([\lambda x.z(z(z(x)))][z(z(z(y)))])])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([z(z(z(z(z(z(y))))))])])\\
-&= (\lambda z.[\lambda y.[z(z(z(z(z(z(z(z(z(y)))))))))]])\\
-&= \lambda zy.z(z(z(z(z(z(z(z(z(y)))))))))\\
-&= \bm{\mathrm{9}} = \bm{\mathrm{3^2}}
 \end{aligned}
@@
 $\lambda$-calculus is our first attempt to clarify the attributes of a computer, and does so both fundamentally and aesthetically.
+
 \end{document}

### 2017-04-25 Draft 2/Section 4 - Zuse's Z3.tex
Added and prepared Sec4

--- 2017-04-22 Draft 2/Appendices.tex
@@
 \begin{document}
-\appendix
-\appendixpage
-\section{Further Arithmetic in $\lambda$-Calculus}
-Multiplication can also be calculated by defining the function \textbf{M}:
-\cite{rojas2015lambdatutorial}
-\begin{equation*}
-\bm{\mathrm{M}} = \lambda wyx.w(yx)
-\end{equation*}  
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{M22}} &= (\lambda wyx.w(yx))(\lambda ab.a(a(b)))(\lambda sz.s(s(z)))\\
-&= \lambda x.(\lambda ab.a(a(b)))[(\lambda sz.s(s(z)))x]\\
-&= \lambda x.(\lambda ab.a(a(b)))[\lambda z.x(x(z))]\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))]([\lambda z.x(x(z))]b))\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))][x(x(b))])\\
-&= \lambda x.(\lambda b.x(x(x(x(b)))))\\
-&= \lambda xb.x(x(x(x(b))))\\
-&= \bm{\mathrm{4}}
-\end{aligned}
-\end{gather*}
-We should rearrange our earlier addition method into an `addition' function of the same format which takes two arguments:
-\begin{equation*}
-\bm{\mathrm{A}} = \lambda ab.b\bm{\mathrm{S}}a
-\end{equation*}
 
-An `exponent' function to find $a^b$can also be defined, of astonishing simplicity:
-\cite{penrose1991emperor}
-\begin{equation*}
-\bm{\mathrm{E}} = \lambda ba.ab
-\end{equation*}
-\begin{gather*}
-\begin{aligned}
-\bm{\mathrm{E23}} &= (\lambda ab.ab)(\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda z.[\lambda ty.t(t(t(y)))]([\lambda ux.u(u(u(x)))]z))\\
-&= (\lambda z.[\lambda ty.t(t(t(y))][\lambda x.z(z(z(x)))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]y))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([\lambda x.z(z(z(x)))][z(z(z(y)))])])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([z(z(z(z(z(z(y))))))])])\\
-&= (\lambda z.[\lambda y.[z(z(z(z(z(z(z(z(z(y)))))))))]])\\
-&= \lambda zy.z(z(z(z(z(z(z(z(z(y)))))))))\\
-&= \bm{\mathrm{9}} = \bm{\mathrm{3^2}}
-\end{aligned}
-\end{gather*}
+\subsection{The Architecture of the Z3}
+
+\subsection{Universality in the Z3}
+
+\subsubsection{}
+
 \end{document}

### 2017-04-25 Draft 2/Section 4 - Zuse's Z3.tex
Added some intro & equations for Z3univ

@@
 \begin{document}
+
+At this point, we have an almost complete definition of 'computer' - a machine which is able to fully implement the concept of effective computability.
+This can be done most simply through the implementation of an effectively computable method of computation, such as Turing Machines.
+However, in order to address the question of whether this was achieved during WW1 we must apply this test to the physical instruments created within this time.
+
+\textit{TODO: Colossus}
+
+However, a few years later on
 
@@
 
-\subsubsection{}
+The first thing that must be considered when looking for universality in a potentially Turing-complete machine is the fact that, by the strict definition of a Turing machine, it must require infinite memory due to the nature of its tape.
+Unfortunately, this is impossible in the physical world as memory is always finite.
+As such, we must revise our definition of Turing-completeness to require only a finite tape.
+
+At first glance, it is unclear that the Z3 can be made into a universal machine due to the fact that it allows for neither conditional branching\footnote{The ability to perform different operations depending on the state of a stored value} nor indirect addressing\footnote{The ability to refer to values stored in memory when the address of that memory is not specifically referred to in the program but is rather obtained from the value of some variable currently in memory}.
+However,
+
+\subsubsection{Conditional Branching}
+
+\begin{gather*}
+\begin{aligned}
+u &= b\ \{op\}\ c \\
+v &= a \cdot t \\
+w &= 1 - t \\
+u &= w \cdot u \\
+a &= v + u
+\end{aligned}
+\end{gather*}
+
+\begin{equation*}
+\mathrm{if\ (}z = i\mathrm{)\ then\ } t = 0 \mathrm{\ else\ } t = 1
+\end{equation*}
+
+\begin{gather*}
+\begin{aligned}
+d &= z - i \\
+d &= d \cdot d \\
+f &= d - e \\
+g &= d\ /\ f \\ \\
+t &= 2^{16} + g \\
+t &= t - 2^{16} \\
+\end{aligned}
+\end{gather*}
+
+\subsubsection{Indirect Addressing}
+
+\subsubsection{State Storage \& Access}
 

### 2017-04-27 Draft 2/Section 4 - Zuse's Z3.tex
Z3 programming model

@@
 
-However, a few years later on
+\textit{TODO: Context of Z3}
 
 \subsection{The Architecture of the Z3}
+
+In this section I shall give a broad functional overview of the Z3.
+I shall explore primarily the function and usage of the machine, the aspects that would be visible to the programmer.
+I shall not go into detail about the operation of the machine itself unless it directly influences the machine's usage.
+All of the description of the machine was derived from \cite{rojas1997z3architecture}.
+
+The Z3 was primarily purposed towards performing simple arithmetical calculations - addition, subtraction, multiplication, division, and the square root operation.
+The operands would be read from memory or from input from a keyboard, and the results would be written to memory or shown on a display.
+Programs would be written as sequences of 8-bit instructions on punched tape, and would be performed as they are read by the machine.
+
+\subsubsection{Data Storage}
+
+\subsubsection{Programming Model}
+
+The instruction set for the Z3 consisted of three types of operation - I/O, memory and arithmetic.
+These instructions would be performed with respect to two floating-point registers, $R_1$ and $R_2$, which act as the two arguments for any arithmetical operation, and could be written to and read from by the non-arithmetical operations.
+
+The two memory instructions, \textbf{Pr} \textit{z} and \textbf{Ps} \textit{z}, load and store respectively the value of registers from and to memory.
+Pr \textit{z} will transfer the data stored at address \textit{z} to $R_1$ if it is clear, otherwise it will be written to $R_2$, overwriting any previous data.
+\textbf{Ps} \textit{z} transfers the value of $R_1$ only to address \textit{z}, and clears both $R_1$ and $R_2$ (such that the next \textbf{Pr} \textit{z} operation will write to $R_1$).
+
+The I/O instructions \textbf{Lu} and \textbf{Ld} respectively store and output values to and from $R_1$.
+\textbf{Lu} halts the machine and stores keyboard input in $R_1$ (clearing $R_2$), while \textbf{Ld} halts the machine and displays $R_1$ on an array of lamps, clearing both registers.
+Both operations require the machine to be restarted in order to continue execution, allowing time for the programmer to input data or write down output.
+
+The arithmetical operations perform as follows:
+\begin{gather*}
+\begin{aligned}
+&Ls_1:\quad	&R_1 &= R_1 \times R_2 \\
+&Ls_2:\quad	&R_1 &= R_1 \div R_2 \\
+&Lm:\quad	&R_1 &= R_1 + R_2 \\
+&Li:\quad	&R_1 &= R_1 - R_2 \\
+&Lw:\quad	&R_1 &= \sqrt{R_1} \\
+\end{aligned}
+\end{gather*}
 
@@
 d &= z - i \\
-d &= d \cdot d \\
+f &= d \cdot d \\
 f &= d - e \\
 g &= d\ /\ f \\ \\
-t &= 2^{16} + g \\
-t &= t - 2^{16} \\
+t &= (2^{16} + g) - 2^{16} \\
 \end{aligned}

### 2017-04-27 Draft 2/Master.tex
Added and prepared Sec4
Improved introduction wording

--- 2017-04-20 Draft 2/Master.tex
@@
 \usepackage{amsthm}
+\usepackage{appendix}
 \usepackage{blindtext}
@@
 \section*{Introduction}
-Computation rules the modern world - from the internet to the rise of automated labour, today's humanity puts colossal value in the hands of computers, taking them for granted as the remarkable machines they are.
+Computation rules the modern world - from the internet to the rise of automated labour, today's humanity puts colossal value in the hands of the remarkable machines that are computers.
 However, the fundamental ideas of computation and calculation lying alongside the transistors and silicon at the heart of this revolution are no less remarkable in themselves, primarily down to their simplicity.
-Furthermore, it is difficult for any modern computer user to see how basic electronics can operate the tasks a computer can perform.
+Furthermore, unlikely that any modern computer user understands remotely how basic electronics can operate the tasks a computer can perform.
 Therefore, I feel the natural way to shed light on this question is to look at the earliest and simplest computers, what they could do and what was distinctive about them.
@@
 In the early 20th Century, prior to developments in this field, any human which evaluated statements through computation was known, logically, as a `computer'.
-As such, we must explore the qualities that an entity - human, machine or other - must have to be able to perform computation.
+As such, we will explore the qualities that an entity - human, machine or other - must have for it to be able to perform computation.
 
@@
 Therefore, in order for a machine to be called a `computer', it must be able to evaluate any member of a set of computable functions.
-However, this is an abstract notion - to clarify it, we must define a simple language to define computable functions, and find a simple method to evaluate them.
+However, this is an abstract notion - to clarify it, we must define a simple language in which we can express computable functions, and find a simple method to evaluate them.
 We shall explore the two most common methods, the $\lambda$-Calculus and the Turing Machine, and evaluate them in terms of their similarities and differences, before exploring how well this definition is fulfilled by early computers.
@@
 \subfile{"Section 3 - Universality"}
+
+\section{Zuse's Z3}
+
+\subfile{"Section 4 - Zuse's Z3"}
+
+\subfile{"Appendices"}
+
 \bibliography{bibliography}

### 2017-04-27 Draft 2/Section 1 - Lambda Calculus.tex
Improved introduction wording

@@
 
-These concepts are the base of conditional branching in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
+These concepts are the base of conditional branching in computation, and in $\lambda$-Calculus operate like \textit{if} statements found in most programming languages.
 For such operations, the concept of a `pair' exists:
@@
 
-However, in order to develop other conditional tests we will need a `predecessor' function - a more complex concept in $\lambda$-calculus.
+However, in order to develop other conditional tests we will need a `predecessor' function - a more complex concept in $\lambda$-Calculus.
 \subsection{Subtraction}
 
-The elusive predecessor function was created by Stephen Kleene, a student of Church's, and was something of a landmark in the development of $\lambda$-calculus.
+The elusive predecessor function was created by Stephen Kleene, a student of Church's, and was something of a landmark in the development of $\lambda$-Calculus.
 
@@
 However, it is clear to see that the Calculus is able to simulate many functions of the computer - data storage with pairs (pairs of pairs can be used for storing more than two items of data as shown in \cref{sec:LambdaUnivTape}), conditionals and booleans, integers and arithmetic and, finally, the ability to be continuous (circular) from a finite configuration.
-$\lambda$-calculus is our first attempt to clarify the attributes of a computer, and does so both fundamentally and aesthetically.
+$\lambda$-Calculus is our first attempt to clarify the attributes of a computer, and does so both fundamentally and aesthetically.
 

### 2017-04-27 Draft 2/Section 2 - Turing Machines.tex
Introduction
Moving from nothing to something
Improved introduction wording

@@
 They are denoted by a lowercase letter and a set of arguments contained in brackets - arguments in gothic script refer to states (or other \textit{m}-functions), and arguments in italics refer to symbols.
-When an \textit{m}-function is triggered, the italic and gothic symbols in the description are substituted by the supplied arguments (similar to application in $\lambda$-calculus).
-An example of an \textit{m}-function would be the function $\mathbb{f}$ below:
+When an \textit{m}-function is triggered, the italic and gothic symbols in the description are substituted by the supplied arguments (similar to application in $\lambda$-Calculus).
+An example of an \textit{m}-function would be the function $\mathbb{f}$ below: \cite{turing1936computablenumbers}
 
@@
 
-As we did in $\lambda$-calculus, we shall define boolean operations.
+As we did in $\lambda$-Calculus, we shall define boolean operations.
 Every operation will take one or many pointers as arguments, and write the evaluated result to another given pointer.
@@
 \medskip
-In each of these, the first argument \textit{a} is observed, and an action which either writes a \texttt{1} or \texttt{0}, or copies or negates from \textit{b} depending on the truth tables, in a very similar manner to $\lambda$-calculus.
+In each of these, the first argument \textit{a} is observed, and an action which either writes a \texttt{1} or \texttt{0}, or copies or negates from \textit{b} depending on the truth tables, in a very similar manner to $\lambda$-Calculus.
 Gradually, the cryptic and simplified language of Turing machines is yielding results similar to that of a computer.
@@
 Turing machines are truly remarkable entities.
-While $\lambda$-calculus was able to mimic the operation of a modern computer (behaving like a purely functional programming language such as Haskell), its beginnings were completely abstract - the mathematical operations of abstraction and application, while being probably more useful than Turing machines in yielding results, were unlike anything which could actually be created in the real world.
+While $\lambda$-Calculus was able to mimic the operation of a modern computer (behaving like a purely functional programming language such as Haskell), its beginnings were completely abstract - the mathematical operations of abstraction and application, while being probably more useful than Turing machines in yielding results, were unlike anything which could actually be created in the real world.
 However, Turing machines are completely grounded in physical reality, and it is totally conceivable how one could create such a machine - despite this, they are able to produce results very similar to that of an imperative programming language such as Java - data storage, typed and referenceable variables, and boolean logic, all performed as a sequence of commands.

### 2017-04-27 Draft 2/Section 3 - Universality.tex
Improved introduction wording

@@
 
-\subsection{Universality in the $\lambda$-calculus}
-Firstly, we shall prove that $\lambda$-calculus is Turing complete by building a universal machine using only $\lambda$-functions.
+\subsection{Universality in the $\lambda$-Calculus}
+Firstly, we shall prove that $\lambda$-Calculus is Turing complete by building a universal machine using only $\lambda$-functions.
 The core of the machine will be a function which calculates a single step in the Turing machine's calculation: It will receive as its parameters the current configuration of the tape and the current state.
@@
 \subsubsection{Emulating the Tape}\label{sec:LambdaUnivTape}
-In order to achieve this, we must define certain new objects in $\lambda$-calculus.
+In order to achieve this, we must define certain new objects in $\lambda$-Calculus.
 First of all, ordered lists - these will be used to describe the current content of the tape.
@@
 
-Unfortunately, the tape which we are currently dealing with is unlike that of a Turing machine, due to the fact that it is of finite length - we cannot write a single list in $\lambda$-calculus which expresses the entire tape.
+Unfortunately, the tape which we are currently dealing with is unlike that of a Turing machine, due to the fact that it is of finite length - we cannot write a single list in $\lambda$-Calculus which expresses the entire tape.
 As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, we will replace it with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as the tail.
@@
 
-We have successfully shown here that $\lambda$-calculus is a Universal, Turing-complete language - it is able to perform every action that a Turing Machine can perform, and as such is at least as powerful as Turing's method of computation.
-Furthermore - and this the reader must take on faith, or rely on intuition - it is possible for a Turing machine to simulate $\lambda$-calculus; Turing machines are Effectively Calculable, and are at least as powerful as the $\lambda$-calculus.
+We have successfully shown here that $\lambda$-Calculus is a Universal, Turing-complete language - it is able to perform every action that a Turing Machine can perform, and as such is at least as powerful as Turing's method of computation.
+Furthermore - and this the reader must take on faith, or rely on intuition - it is possible for a Turing machine to simulate $\lambda$-Calculus; Turing machines are Effectively Calculable, and are at least as powerful as the $\lambda$-Calculus.
 Therefore, these two methods of computation - one based in physical ideas, one based in conceptual ideas, are totally equivalent.

### 2017-05-03 Draft 2/Section 4 - Zuse's Z3.tex
Improved introduction wording
Conditional branching in Z3
Not quite finished, description of z=j to do

@@
 I shall not go into detail about the operation of the machine itself unless it directly influences the machine's usage.
-All of the description of the machine was derived from \cite{rojas1997z3architecture}.
+The description of the machine was derived from \cite{rojas1997z3architecture}.
 
@@
 \end{gather*}
-
+For each operation, the 
 \subsection{Universality in the Z3}
@@
 At first glance, it is unclear that the Z3 can be made into a universal machine due to the fact that it allows for neither conditional branching\footnote{The ability to perform different operations depending on the state of a stored value} nor indirect addressing\footnote{The ability to refer to values stored in memory when the address of that memory is not specifically referred to in the program but is rather obtained from the value of some variable currently in memory}.
-However,
+However, through use of the tool available to the programmer these features can be emulated, and a Turing Machine can be simulated.
 
 \subsubsection{Conditional Branching}
+
+Firstly and fundamentally we shall construct conditional branches using a technique shown in \cite{ibarra1983intdivision} \textit{TODO: Check this ref} which allows the implementation of a form of case statement as found in modern programming languages such as JavaScript.
+Such an operation performs one of a set of different operations depending on the value of a given variable.
+
+Given a positive integer variable $z$, the variable on which the outcome of the statement depends and the set of operations to be performed depending on the value of $z$, $P_1, ...
+, P_n$, we can produce a sequence of operations that will allow only the operation $P_z$ to perform.
+Due to the nature of the Z3 requiring a full sequence of commands to be executed without exception, every one of these operations will be evaluated; however, only operation $P_z$ will be allowed to actually affect memory.
+
+At the start of the switch statement, a sequence of commands check if $z = j$ - if so the flag variable $t$ is set to $0$ (otherwise it is set to $1$).
+Next, for each operation $P_j$ (which will be of the form $a = b\ \{op\}\ c$), we will write in the program a sequence of commands that, if $t$ is $0$, write the value of $b\ \{op\}\ c$ to $a$.
+These statements are shown below:
 
@@
 
+Or, for clarity, $a = (a \cdot t) + (1 - t)(b\ \{op\}\ c)$.
+If $t = 1$, $v$ is set to $t$; otherwise it is set to $0$.
+Furthermore, if $t = 0$, $u$ is set to the outcome of the operation; otherwise it is set to $0$ again.
+Therefore, if $t = 0$, $a$ is set to the outcome of the operation; otherwise it is set back to its original value.
+As such, after this transformation has been put in place for every $P$ operation, and a method to set $t$ at the start of the case statement has been implemented, every new command in this program can be executed - most superfluously - in order to only use the $z$-th command.
+Next we must produce a set of operations that will perform the computation
 \begin{equation*}
@@
 
+This is done using the following piece of code, where $e$ has been pre-set to a value much less than 1 (e.g. 1/1000).
+
 \begin{gather*}
@@
 d &= z - i \\
-f &= d \cdot d \\
+d &= d \cdot d \\
 f &= d - e \\
@@
 
+The variable $d$ is only zero if $z = i$. If not, $d$ is set to a positive value, and $g$ is set to the ratio of $d$ and a value slightly smaller than $d$ - $1$ plus a small fractional part.
+
 \subsubsection{Indirect Addressing}

### 2017-05-03 Draft 2/Section 4 - Zuse's Z3.tex
Finished Conditional branching, fixed some references

@@
 At first glance, it is unclear that the Z3 can be made into a universal machine due to the fact that it allows for neither conditional branching\footnote{The ability to perform different operations depending on the state of a stored value} nor indirect addressing\footnote{The ability to refer to values stored in memory when the address of that memory is not specifically referred to in the program but is rather obtained from the value of some variable currently in memory}.
-However, through use of the tool available to the programmer these features can be emulated, and a Turing Machine can be simulated.
+However, through use of the tools available to the programmer these features can be emulated, and a Turing Machine can be simulated.
+This uses many tecniques explained in \cite{rojas1998z3universal}.
 
@@
 
-Firstly and fundamentally we shall construct conditional branches using a technique shown in \cite{ibarra1983intdivision} \textit{TODO: Check this ref} which allows the implementation of a form of case statement as found in modern programming languages such as JavaScript.
+Firstly and fundamentally we shall construct conditional branches using a technique shown in \cite{ibarra1983control} which allows the implementation of a form of case statement as found in modern programming languages such as JavaScript.
 Such an operation performs one of a set of different operations depending on the value of a given variable.
@@
 f &= d - e \\
-g &= d\ /\ f \\ \\
+g &= d\ /\ f \\[1ex]
 t &= (2^{16} + g) - 2^{16} \\
@@
 
-The variable $d$ is only zero if $z = i$. If not, $d$ is set to a positive value, and $g$ is set to the ratio of $d$ and a value slightly smaller than $d$ - $1$ plus a small fractional part.
+The variable $d$ is only zero if $z = i$.
+If not, $d$ is set to a positive value, and $g$ is set to the ratio of $d$ and a value slightly smaller than $d$ - $1$ plus a small fractional part.
+This value is then rounded down to $1$ by shifting it 16 places to the right such that all but the value in the desired bit are eradicated, before it is shifted back to its correct value.
 

### 2017-05-04 Draft 2/Section 4 - Zuse's Z3.tex
Added code for universal z3

@@
 \documentclass[Master.tex]{subfiles}
+
+\lstdefinelanguage{Zuselang}
+{
+  morekeywords={
+    Pr,
+    Ps,
+    Lu,
+    Ld,
+    Ls,
+    Lm,
+    Li,
+    Lw,
+    case
+  },
+  sensitive=true, % keywords are not case-sensitive
+  morecomment=[l]{//}, % l is for line comment
+  morecomment=[s]{.}{.}, % s is for start and end delimiter
+  morestring=[b]" % defines that strings are enclosed in double quotes
+}
+\lstset{language=Zuselang}
 
@@
 \begin{aligned}
-&Ls_1:\quad	&R_1 &= R_1 \times R_2 \\
+&Ls_1:\quad	&R_1 &= R_1 \cdot R_2 \\
 &Ls_2:\quad	&R_1 &= R_1 \div R_2 \\
@@
 \end{gather*}
-For each operation, the 
+For each operation, the operation is performed on $R_1$ and $R_2$, and the result is written to $R_1$. 
 \subsection{Universality in the Z3}
@@
 This uses many tecniques explained in \cite{rojas1998z3universal}.
+
+For the sake of simplicity, in this section we shall use a more intuitive form to express instructions for the machine. We shall write $a = b\ \mathrm{op}\ c$ to simplify statements of the form:s
+\begin{gather*}
+\begin{aligned}
+&\bm{\mathrm{Pr}}\ b\\
+&\bm{\mathrm{Pr}}\ c\\
+&\textrm{op}\\ 
+&\bm{\mathrm{Ps}}\ a\\
+\end{aligned}
+\end{gather*}
 
@@
 At the start of the switch statement, a sequence of commands check if $z = j$ - if so the flag variable $t$ is set to $0$ (otherwise it is set to $1$).
-Next, for each operation $P_j$ (which will be of the form $a = b\ \{op\}\ c$), we will write in the program a sequence of commands that, if $t$ is $0$, write the value of $b\ \{op\}\ c$ to $a$.
+Next, for each operation $P_j$ (which will be of the form $a = b\ \mathrm{op}\ c$), we will write in the program a sequence of commands that, if $t$ is $0$, write the value of $b\ \mathrm{op}\ c$ to $a$.
 These statements are shown below:
@@
 \begin{aligned}
-u &= b\ \{op\}\ c \\
+u &= b\ \mathrm{op}\ c \\
 v &= a \cdot t \\
@@
 
-Or, for clarity, $a = (a \cdot t) + (1 - t)(b\ \{op\}\ c)$.
+Or, for clarity, $a = (a \cdot t) + (1 - t)(b\ \mathrm{op}\ c)$.
 If $t = 1$, $v$ is set to $t$; otherwise it is set to $0$.
@@
 
+With the Z3's two new-found tools, production of a universal machine is incredibly simple.
+The machine would first be prepared with the initial state (an integer) at the address $s$, and the initial index of the cursor (also an integer, $0$ by default) at the address $h$.
+Then the following program would be run repeatedly with the ends of the tape attached to each other.
+\begin{lstlisting}
+r = (h)
+
+case(s) {
+	...,
+	.n.: .w. = [symbol],
+	...
+}
+case(s) {
+	...,
+	.n.: .t. = [-1/0/1],
+	...
+}
+h = h + t
+
+case(s) {
+	...,
+	.n.: .s. = [new state]
+	...
+}
+\end{lstlisting}
+
 \end{document}

### 2017-05-09 Draft 2/Section 4 - Zuse's Z3.tex
changed lstlisting to gather*

@@
 
-The two memory instructions, \textbf{Pr} \textit{z} and \textbf{Ps} \textit{z}, load and store respectively the value of registers from and to memory.
+The two memory instructions, Pr \textit{z} and Ps \textit{z}, load and store respectively the value of registers from and to memory.
 Pr \textit{z} will transfer the data stored at address \textit{z} to $R_1$ if it is clear, otherwise it will be written to $R_2$, overwriting any previous data.
-\textbf{Ps} \textit{z} transfers the value of $R_1$ only to address \textit{z}, and clears both $R_1$ and $R_2$ (such that the next \textbf{Pr} \textit{z} operation will write to $R_1$).
+Ps \textit{z} transfers the value of $R_1$ only to address \textit{z}, and clears both $R_1$ and $R_2$ (such that the next Pr \textit{z} operation will write to $R_1$).
 
-The I/O instructions \textbf{Lu} and \textbf{Ld} respectively store and output values to and from $R_1$.
-\textbf{Lu} halts the machine and stores keyboard input in $R_1$ (clearing $R_2$), while \textbf{Ld} halts the machine and displays $R_1$ on an array of lamps, clearing both registers.
+The I/O instructions Lu and Ld respectively store and output values to and from $R_1$.
+Lu halts the machine and stores keyboard input in $R_1$ (clearing $R_2$), while Ld halts the machine and displays $R_1$ on an array of lamps, clearing both registers.
 Both operations require the machine to be restarted in order to continue execution, allowing time for the programmer to input data or write down output.
@@
 \begin{aligned}
-&Ls_1:\quad	&R_1 &= R_1 \cdot R_2 \\
-&Ls_2:\quad	&R_1 &= R_1 \div R_2 \\
-&Lm:\quad	&R_1 &= R_1 + R_2 \\
-&Li:\quad	&R_1 &= R_1 - R_2 \\
-&Lw:\quad	&R_1 &= \sqrt{R_1} \\
+&\mathrm{Ls_1}:\quad	&R_1 &= R_1 \cdot R_2 \\
+&\mathrm{Ls_2}:\quad	&R_1 &= R_1 \div R_2 \\
+&\mathrm{Lm}:\quad	&R_1 &= R_1 + R_2 \\
+&\mathrm{Li}:\quad	&R_1 &= R_1 - R_2 \\
+&\mathrm{Lw}:\quad	&R_1 &= \sqrt{R_1} \\
 \end{aligned}
@@
 \begin{aligned}
-&\bm{\mathrm{Pr}}\ b\\
-&\bm{\mathrm{Pr}}\ c\\
+&\mathrm{Pr}\ b\\
+&\mathrm{Pr}\ c\\
 &\textrm{op}\\ 
-&\bm{\mathrm{Ps}}\ a\\
+&\mathrm{Ps}\ a\\
 \end{aligned}
@@
 
+Using this method to produce case statements, we can produce an equivalent to an indirect addressing operation.
+This operation is of form $n = (x)$, which sets $n$ to the value at address location $x$, where $x$ is an integer $n_a \leq x \leq n_b$, $n_a$ and $n_b$ being integer constants representing the limits of the region of memory that can be addressed by this function.
+This function is equivalent to:
+
 \subsubsection{State Storage \& Access}
@@
 With the Z3's two new-found tools, production of a universal machine is incredibly simple.
-The machine would first be prepared with the initial state (an integer) at the address $s$, and the initial index of the cursor (also an integer, $0$ by default) at the address $h$.
+The machine would first be prepared with the initial state (an integer) at the address $s$, and the initial index of the cursor (also an integer, $a$ by default) at the address $h$.
 Then the following program would be run repeatedly with the ends of the tape attached to each other.
-\begin{lstlisting}
-r = (h)
-
-case(s) {
-	...,
-	.n.: .w. = [symbol],
-	...
-}
-case(s) {
-	...,
-	.n.: .t. = [-1/0/1],
-	...
-}
-h = h + t
-
-case(s) {
-	...,
-	.n.: .s. = [new state]
-	...
-}
-\end{lstlisting}
+\begin{gather*}
+\begin{aligned}
+&r = (h)						\\
+&p = k 							\\
+&\mathrm{case}\ (s)\ \{			\\
+&\qquad	... ,					\\
+&\qquad	n:\ w = [symbol],		\\
+&\qquad	...						\\
+&\}								\\
+&\mathrm{case}\ (s)\ \{			\\
+&\qquad	...,					\\
+&\qquad	n:\ t = [-1/0/1],		\\
+&\qquad	...						\\
+&\}								\\
+&h = h + t						\\
+&\mathrm{case}\ (s)\ \{			\\
+&\qquad ...,					\\
+&\qquad	n:\ s = [new\ state],	\\
+&\qquad	...						\\
+&\}								\\
+\end{aligned}
 

### 2017-06-04 Draft 2/Section 4 - Zuse's Z3.tex
dEaDlInE ;iN 1~5 .dAyS wHaT'

@@
 At this point, we have an almost complete definition of 'computer' - a machine which is able to fully implement the concept of effective computability.
-This can be done most simply through the implementation of an effectively computable method of computation, such as Turing Machines.
-However, in order to address the question of whether this was achieved during WW1 we must apply this test to the physical instruments created within this time.
-
+This can be done most simply through the implementation of an effectively computable method of computation, such as a Turing Machine.
+In order to address the question of whether this was achieved during WW1 we must apply this test to the physical instruments created during this period.
 \textit{TODO: Colossus}
@@
 In this section I shall give a broad functional overview of the Z3.
-I shall explore primarily the function and usage of the machine, the aspects that would be visible to the programmer.
+I shall explore primarily the function and usage of the machine, i.e.
+the aspects that would be visible to the programmer.
 I shall not go into detail about the operation of the machine itself unless it directly influences the machine's usage.
@@
 
-The Z3 was primarily purposed towards performing simple arithmetical calculations - addition, subtraction, multiplication, division, and the square root operation.
+The Z3 was primarily purposed towards performing simple arithmetical calculations - addition, subtraction, multiplication, division, and square root.
 The operands would be read from memory or from input from a keyboard, and the results would be written to memory or shown on a display.
-Programs would be written as sequences of 8-bit instructions on punched tape, and would be performed as they are read by the machine.
+Programs could be written as sequences of 8-bit instructions on punched tape, and would be performed as they are read by the machine.
 
@@
 
-The two memory instructions, Pr \textit{z} and Ps \textit{z}, load and store respectively the value of registers from and to memory.
-Pr \textit{z} will transfer the data stored at address \textit{z} to $R_1$ if it is clear, otherwise it will be written to $R_2$, overwriting any previous data.
+The two memory instructions Pr \textit{z} and Ps \textit{z} load and store respectively the value of registers from and to memory.
+Pr \textit{z} transfers the data stored at address \textit{z} to $R_1$ if $R_1$ is clear; otherwise it is written to $R_2$, overwriting any previous data.
 Ps \textit{z} transfers the value of $R_1$ only to address \textit{z}, and clears both $R_1$ and $R_2$ (such that the next Pr \textit{z} operation will write to $R_1$).
@@
 
-For the sake of simplicity, in this section we shall use a more intuitive form to express instructions for the machine. We shall write $a = b\ \mathrm{op}\ c$ to simplify statements of the form:s
+For the sake of simplicity, in this section we shall use a more intuitive form to express instructions for the machine. We shall write $a = b\ \mathrm{op}\ c$ to simplify statements of the form:
 \begin{gather*}
@@
 
-Firstly and fundamentally we shall construct conditional branches using a technique shown in \cite{ibarra1983control} which allows the implementation of a form of case statement as found in modern programming languages such as JavaScript.
+Firstly and fundamentally we shall construct conditional branches using a technique shown in \cite{ibarra1983control} which allows the implementation of a form of switch statement as found in many modern C-like programming languages.
 Such an operation performs one of a set of different operations depending on the value of a given variable.
 
-Given a positive integer variable $z$, the variable on which the outcome of the statement depends and the set of operations to be performed depending on the value of $z$, $P_1, ...
-, P_n$, we can produce a sequence of operations that will allow only the operation $P_z$ to perform.
+Given a positive integer variable $z$ on which the outcome of the statement depends and the set of operations to be performed depending on the value of $z$, $P_1, ...
+, P_n$, we can produce a sequence of commands that will allow only the operation $P_z$ to perform.
 Due to the nature of the Z3 requiring a full sequence of commands to be executed without exception, every one of these operations will be evaluated; however, only operation $P_z$ will be allowed to actually affect memory.
@@
 Therefore, if $t = 0$, $a$ is set to the outcome of the operation; otherwise it is set back to its original value.
-As such, after this transformation has been put in place for every $P$ operation, and a method to set $t$ at the start of the case statement has been implemented, every new command in this program can be executed - most superfluously - in order to only use the $z$-th command.
+As such, after this transformation has been put in place for every $P$ operation, and a method to set $t$ at the start of the switch statement has been implemented, every new command in this program can be executed - most superfluously - in order to only use the $z$-th command.
 Next we must produce a set of operations that will perform the computation
@@
 
-Using this method to produce case statements, we can produce an equivalent to an indirect addressing operation.
-This operation is of form $n = (x)$, which sets $n$ to the value at address location $x$, where $x$ is an integer $n_a \leq x \leq n_b$, $n_a$ and $n_b$ being integer constants representing the limits of the region of memory that can be addressed by this function.
-This function is equivalent to:
-
-\subsubsection{State Storage \& Access}
-
-With the Z3's two new-found tools, production of a universal machine is incredibly simple.
-The machine would first be prepared with the initial state (an integer) at the address $s$, and the initial index of the cursor (also an integer, $a$ by default) at the address $h$.
-Then the following program would be run repeatedly with the ends of the tape attached to each other.
+Using this method to emulate switch statements, we can produce an equivalent to an indirect addressing operation.
+This operation is of form $y = (x)$, which sets $n$ to the value at address location $x$, where $x$ is an integer $n_a \leq x \leq n_b$, $n_a$ and $n_b$ being integer constants representing the limits of the region of memory that can be addressed by this function.
+$x$ could potentially be the output from a previous arithmetical operation.
+Relying on the fact that this region is finite (and furthermore that the tape length is also finite), this can be done using a switch statement with a case for every address $z$ between $n_a$ and $n_b$ as shown.
 \begin{gather*}
 \begin{aligned}
-&r = (h)						\\
-&p = k 							\\
-&\mathrm{case}\ (s)\ \{			\\
+&\bm{\mathrm{switch}}\ (x)\ \{	\\
 &\qquad ... ,					\\
-&\qquad	n:\ w = [symbol],		\\
-&\qquad	...						\\
-&\}								\\
-&\mathrm{case}\ (s)\ \{			\\
-&\qquad	...,					\\
-&\qquad	n:\ t = [-1/0/1],		\\
-&\qquad	...						\\
-&\}								\\
-&h = h + t						\\
-&\mathrm{case}\ (s)\ \{			\\
-&\qquad ...,					\\
-&\qquad	n:\ s = [new\ state],	\\
+&\qquad z:\	\mathrm{Pr}\ z;\ \mathrm{Ps}\ a			\\
 &\qquad ... 					\\
@@
 \end{aligned}
+\end{gather*}
+At this point, it becomes very clear the extent to which the Z3 is not suited to universal computation.
+When every single applicable memory address must be specified individually, with five operations per address to implement the case, each operation consisting of four instructions, it is obvious that the Z3 is in no way a \textit{practical} universal machine.
 
+To emulate a Turing machine using these new tools, one considers the tape to be the region of memory between $n_a$ and $n_b$, and 
 \end{document}

### 2017-06-12 Draft 2/Appendices.tex
*Tick Tock Tick Tock* 6 days to goooo yayyy
Yeh I did loads of changes and things, look at the log if you REALLY care that much

@@
 \end{gather*}
-We should rearrange our earlier addition method into an `addition' function of the same format which takes two arguments:
-\begin{equation*}
-\bm{\mathrm{A}} = \lambda ab.b\bm{\mathrm{S}}a
-\end{equation*}
 
 An `exponent' function to find $a^b$can also be defined, of astonishing simplicity:
-\cite{penrose1991emperor}
+\cite{barendregt1984introduction}
 \begin{equation*}
@@
 \end{gather*}
+
+\section{Explanation of Example Turing Machine}\label{appendix:turingexampleexp}
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+    \textit{state} & \textit{symbol} & \textit{transition function} & \textit{final state} \\
+    \hhline{====}
+    \multirow{1}{*}{$\mathbb{Q}$} & Any        & P\texttt{e}, R P\texttt{e}, R,  P\texttt{0}, R, R, P\texttt{0}, L, L & $\mathbb{A}$ \\
+    \hhline{----}
+    \multirow{2}{*}{$\mathbb{A}$} & \texttt{0} & R, P\texttt{x}, L, L, L                   & $\mathbb{A}$ \\
+                                  & \texttt{1} &                                  & $\mathbb{B}$ \\
+    \hhline{----}
+    \multirow{2}{*}{$\mathbb{B}$} & Any        & R, R                             & $\mathbb{B}$ \\
+                                  & None       & P\texttt{1}, L                            & $\mathbb{C}$ \\
+    \hhline{----}
+    \multirow{3}{*}{$\mathbb{C}$} & \texttt{x} & E, R                             & $\mathbb{B}$ \\
+                                  & \texttt{e} & R                                & $\mathbb{D}$ \\
+                                  & None       & L, L                             & $\mathbb{C}$ \\
+    \hhline{----}
+    \multirow{2}{*}{$\mathbb{D}$} & Any        & R, R                             & $\mathbb{D}$ \\
+                                  & None       & P\texttt{0}, L, L                         & $\mathbb{A}$ \\
+\end{tabu}
+
+\noindent $\Rightarrow \mathbb{Q}$
+
+\medskip
+
+Producing the sequence \texttt{010110111011110111110...}, this machine operates by first printing the symbols \texttt{e e 0} at the start of the tape, before printing the first \texttt{0} of the sequence on the fifth cell, finishing on the third cell and moving to state $\mathbb{A}$.
+
+If $\mathbb{A}$ is triggered, every \texttt{1} consecutively to the left of the cursor inclusively will be marked with \texttt{x}, $\rightarrow \mathbb{B}$.
+
+If $\mathbb{B}$ is triggered, the symbol \texttt{1} is appended to the output sequence, $\rightarrow \mathbb{C}$.
+
+If $\mathbb{C}$ is triggered, the cursor moves leftwards through the labels: if an \texttt{x} is found it is erased and $\rightarrow \mathbb{B}$; if the cursor reaches the beginning (an \texttt{e} is found) $\rightarrow \mathbb{D}$.
+
+If $\mathbb{D}$ is triggered, the symbol \texttt{0} is appended to the output sequence, the cursor moves to the previous value cell and $\rightarrow \mathbb{A}$.
+
+The workings of this algorithm are mostly in states $\mathbb{A}$ and $\mathbb{C}$: after the \texttt{0} is drawn $\mathbb{A}$ draws a number of \texttt{x} symbols equal to the previous number of \texttt{1} symbols drawn.
+$\mathbb{C}$ triggers $\mathbb{B}$ a number of times equal to the number of found \texttt{x} symbols before drawing a \texttt{0} - as $\mathbb{B}$ has already been triggered once, a number of \texttt{1} symbols will be drawn which is one more than the previous number drawn.
+For clarity in the comprehension of this somewhat abstract algorithm, some of the early states have been listed on the next page.
+Empty squares are represented by dots ($\cdot$) and the tape states continue in columns.
+An ellipsis marks the omission of a set of states which are implied or trivial.
+
+\begin{equation*}
+\begin{aligned}
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{A}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 1\ x\ 0} & \rightarrow \mathbb{A}\\
+&\mathtt{e\ e\ 0\ \underset{\uparrow}{\cdot}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 1\ x\ 0} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ x\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ x\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \underset{\uparrow}{x}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{A}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{A}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ x\ 0} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{x}\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{x}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & ...&\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
+&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{D}\\
+&...& &...&\\
+&\mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\\
+&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{D}\\
+\end{aligned}
+\end{equation*}
+
+\clearpage
+
+\section{Detailed Demonstration of the Universality of $\lambda$-Calculus}\label{appendix:lambdauniversaldemo}
+
+\subsection{Standard Turing Description Form}
+
+First, the description table shall be formally defined, as shown by Turing in \cite{turing1936computablenumbers}.
+Looking at the first table described, one can see that any transition function follows a similar format: E; [E, R]; [E, L]; P\textit{a}; [P\textit{a}, R]; [P\textit{a}, L] or no entry at all.
+More complex transition functions such as those found in later tables can always be put into one of these forms through the addition of intermediary states which are called in sequence.
+
+Next, let us rename the states as $q_0$, $q_1$, $q_2$, $...$, $q_n$ (the initial state shall always be called $q_0$).
+Furthermore, the symbols shall be renamed $S_0$, $S_1$, $S_2$, $...$, $S_n$ - in this case, $S_0$ will represent the blank square, $S_1$ will represent \texttt{0} and $S_2$ will represent \texttt{1}.
+The movement operations L and R will be renamed $M_L$, $M_R$, and the operation to keep the tape stationary is simply $M_S$.
+Our tables are now of form:
+
+\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+    \textit{state} & \textit{symbol} & \textit{transition function} & \textit{final state} \\
+    \hhline{====}
+    $q_i$ & $S_i$ & P$S_k$, $M_{L/R/S}$ & $q_m$ \\
+    \hhline{----}
+\end{tabu}
+
+\medskip\medskip
+
+Lines such as
+
+\noindent\begin{tabu} to \textwidth{XXXX}
+    $q_i$ & $S_i$ & E, $M_{L/R/S}$ & $q_m$ \\
+\end{tabu}
+\medskip
+
+\noindent are to be written as
+
+\noindent\begin{tabu} to \textwidth{XXXX}
+    $q_i$ & $S_i$ & P$S_0$, $M_{L/R/S}$ & $q_m$ \\
+\end{tabu}
+\medskip
+
+\noindent and lines such as
+
+\noindent\begin{tabu} to \textwidth{XXXX}
+    $q_i$ & $S_i$ & $M_{L/R/S}$ & $q_m$ \\
+\end{tabu}
+\medskip
+
+\noindent are to be written as
+
+\noindent\begin{tabu} to \textwidth{XXXX}
+    $q_i$ & $S_i$ & P$S_i$, $M_{L/R/S}$ & $q_m$ \\
+\end{tabu}
+\medskip
+
+\noindent in order for all lines to be written in the first format.
+As the number of symbols used for a machine is always finite, it is possible to enumerate under every single state an action for every single symbol $S_i$ that the machine could be reading.
+As such, `All' and `Not \textit{a}' may be portrayed in this format.
+This idea also allows the last simplification shown in the table above to work.
+
+This expanded and generalised configuration is much more helpful to us, as while any Turing machine configuration (including using \textit{m}-functions) can be written in this format, it is very concise and regular.
+This allows it to be given as input to our universal machines.
+
+\subsection{Emulating the Tape}\label{sec:LambdaUnivTape}
+To allow for storage of large sequences of data in $\lambda$-Calculus, ordered lists must be defined.
+These will be used to store the content of the tape.
+These are defined as a sequence of nodes, where each node is a pair with the first element as the content of the node and the second element is the next node in the sequence (as shown in \cite{tromp2007binary}).
+The final node will have \textbf{0} as its first element to signify the end of the list - the second element will never be referred to; as such \textbf{0} will be used as a placeholder (of course this only works if the list is not designed to contain any values of zero or true, as they will be indistinguishable from the end marker - I shall use \textbf{1} to represent $S_0$, \textbf{2} to represent $S_1$ and so on).
+For example, the list [a,b,c,d,e] would be represented as:
+\begin{equation*}
+\lambda l.la(\lambda m.mb(\lambda n.nc(\lambda o.od(\lambda p.pe(\lambda z.z\bm{\mathrm{00}})))))
+\end{equation*}
+In order to obtain the first element (head), the argument \textbf{T} would be applied to the list; to get the remaining elements (tail) the \textbf{F} argument would be applied. 
+Furthermore, to prepend an element $x$ to the start of a list $l$:
+\begin{equation*}
+\bm{\mathrm{:}} = \lambda xlf.f[x][l]
+\end{equation*}
+
+The tape of the machine extends infinitely in both directions either side of the cursor.
+This shal be represented as a pair of lists: $T_p$ as the list of all the predecessors to the cursor and $T_s$ as the list of all the successors to the cursor.
+The predecessors shall be listed in reverse order, such that the head of $T_p$ is the symbol directly to the left of the cursor.
+The head of $T_s$ is the symbol considered to be `under' the cursor, the next element is the symbol to the right of that, and so on.
+\begin{equation*}
+T_a = \lambda f.f T_p T_s
+\end{equation*}
+
+\subsection{Movement Operations}
+To emulate cursor movement, transformation functions shall be defined for the tape. These operations will shift the tape by moving the head of $T_s$ to the head of $T_p$ or vice versa.
+
+\begin{gather*}
+\begin{aligned}
+\bm{M}_L &= \lambda t_a f.f\ [(t_a\bm{\mathrm{T}})\bm{\mathrm{F}}]\ [\bm{\mathrm{:}}([t_a\bm{\mathrm{T}}]\bm{\mathrm{T}})\ (t_a\bm{\mathrm{F}})]\\
+\bm{M}_R &= \lambda t_a f.f\ [\bm{\mathrm{:}}([t_a\bm{\mathrm{F}}]\bm{\mathrm{T}})\ (t_a\bm{\mathrm{T}})]\ [(t_a\bm{\mathrm{F}})\bm{\mathrm{F}}]\\
+\bm{M}_S &= \lambda t_a.t_a\\
+\end{aligned}
+\end{gather*}
+The $\bm{M}_L$ function produces a new tape pair, after taking the original tape pair as parameter $t_a$.
+The first element of this new pair is simply the tail of $T_p$ ($T_p$ being found at $T_a\bm{\mathrm{T}})$.
+The second element is the head of $T_p$ prepended to the entirety of $T_s$ (found at $T_a\bm{\mathrm{T}})$.
+$\bm{M}_R$ will do the effective opposite, prepending the head of $T_s$ to $T_p$ and producing the tail of $T_s$.
+$\bm{M}_S$ will keep the tape in its current state.
+
+\subsection{Infinite-Length Tape}
+
+Unfortunately, the tape which that is currently being dealt with is unlike that of a Turing machine, due to the fact that it is of finite length - one cannot write a single list in $\lambda$-Calculus which expresses the entire tape.
+As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, it shall be replaced with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as the tail.
+To do this, another transformation function shall be used which will check if either head element of the tape pair is \textbf{0}, and if so, will replace it with an empty square node $\bm{\epsilon}$ - otherwise it will simply be replaced with the original head:
+
+\begin{gather*}
+\begin{aligned}
+\bm{\epsilon} &= \lambda g.g\ [\bm{\textbf{1}}]\ [\lambda d.d\bm{\mathrm{0}}\bm{\mathrm{0}}] \\
+\bm{C} &= \lambda t_a g.g\ [\bm{\mathrm{Z}}(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})\ (\bm{\epsilon})(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})]\ [\bm{\mathrm{Z}}(t_a\bm{\mathrm{F}}\bm{\mathrm{T}})\ (\bm{\epsilon})(t_a\bm {\mathrm{F}}\bm{\mathrm{T}})]
+\end{aligned}
+\end{gather*}
+This transformation will be applied after every tape movement operation.
+
+\subsection{Printing to the Tape}
+
+The operation function that writes a given symbol to the square beneath the cursor is not a particularly complex transformation - it simply replaces the current head of $T_s$ with the given numeral $a$.
+
+\begin{equation*}
+\bm{W} = \lambda a t_a p.p\ [t_a\bm{\mathrm{T}}]\ [\mathrm{\bm{:}} a\  (t_a \bm{\mathrm{FF}})]
+\end{equation*}
+
+\subsection{Storing \& Accessing states}
+%\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}
+Once again, in order to store the symbols, transition functions and final states associated with each state,  a list shall be used.
+The first element of the list shall represent $q_0$, the second $q_1$ and so on.
+Each element of the list will be a list in itself.
+Each element of this nested list shall refer to a single line described by the symbol aspect of the configuration.
+These elements are pairs: the first element being the symbol to be found (a numeral), the second being the action to be performed under this configuration.
+
+The action itself will be yet another pair.
+The first element is the transition function that should be executed on the tape - this will be of the form $(\bm{C})(\bm{M}_{L/R/S})(\bm{W}a)$, which applies first a write operation before a movement operation and the tape length correction operation.
+The second element is a function which, when given the description of the machine, finds the given state.
+These state references shall be described as shown, with the example of the reference to $q_3$:
+\begin{equation*}
+\bm{Q}_3 = \lambda l.l\bm{\textbf{FFFT}}
+% * <mxpen26@gmail.com> 10:30:46 06 Jun 2017 UTC+0100:
+% Checked up to here; TODO continue
+\end{equation*}
+This gets the fourth head of the given list, which refers to $q_3$.
+
+%As an example, here is the description for the first machine described, which generates the sequence \texttt{01010101...} (for simplicity, this version does not leave \textit{s}-squares blank).
+For reference, here is the enumerated table:
+%\medskip\noindent\begin{tabu} to \textwidth{XXXX}
+%    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
+%    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
+%    \hhline{====}
+%    $q_0$ & $S_0$ & PS_1       & $\mathbb{A}$ \\
+%    $q_0$ & $S_1$ & PS_2 & $\mathbb{A}$ \\ 
+%    $q_0$ & \texttt{1}    & R, R, P\texttt{0} & $\mathbb{A}$ \\ 
+%\end{tabu}
+%We shall represent this table as such:
+%\begin{gather*}
+%\begin{aligned}
+%\bm{d}
+%\end{aligned}
+%\end{gather*}
+
+%[I cba to do this now]
+
+In order to find which action should be performed given a certain configuration, one can use the following function which produces a pair of a list transition function and a state reference from a current state, the current symbol, and the description function.
+As part of this function, the recursive function $\bm{\rho}$ must be used in conjunction with the \textbf{Y} combinator, which returns the action aspect of the first pair under symbol $s$ in list $l$ (the $r$ argument is the argument which would represent the function as a whole, and is recursively called by the \textbf{Y} combinator)
+
+\begin{gather*}
+\begin{aligned}
+\bm{\rho} &= \lambda rls.(\bm{\doteq}(l\bm{\mathrm{TT}})s)(l\bm{\mathrm{TF}})(r(l\bm{\mathrm{F}})s)\\
+\bm{I} &= \lambda qsd.\bm{\mathrm{Y}\rho}(qd)s
+\end{aligned}
+\end{gather*}
+
+\subsection{Universal Machine State Change Operation}
+
+At last, all these functions to create a single operation which transforms a given machine configuration (state, $T_p$ \& $T_s$, and the description table) into the machine configuration for the next state.
+This configuration shall be represented as a pair, the first element being a pair of the state reference and the tape, and the second element as the description table.
+The $\bm{\nu}$ function gets the action function from the given machine configuration.
+
+\begin{gather*}
+\begin{aligned}
+\bm{\nu} &= \lambda c.\bm{I}(c\bm{\mathrm{TT}})([c\bm{\mathrm{TF}}]\bm{\mathrm{FT}})(c\bm{\mathrm{F}})\\
+\bm{X} &= \lambda cf.f[\lambda g.g[(\bm{\nu}c)\bm{\mathrm{F}}][((\bm{\nu}c)\bm{\mathrm{T}})(c\bm{\mathrm{TF}})]]c
+\end{aligned}
+\end{gather*}
+
+\subsection{Universal Machine State Generator}
+
+Finally, a single recursive function shall be defined, which produces every consecutive state by running $\bm{X}$ on itself repeatedly.
+When this is evaluated, each iteration of the machine shall be passed into the \textbf{Y} combinator, leading to each consecutive state being found during evaluation.
+
+\begin{gather*}
+\begin{aligned}
+\bm{\omega} &= \lambda uc.u(\bm{X}c) \\
+\bm{U} &= \lambda c.\bm{\mathrm{Y}}\bm{\omega}c
+\end{aligned}
+\end{gather*}
+
+%\section{Full description of a Turing Machine in the Z3}\label{appendix:z3turingcode}
+
 \end{document}

### 2017-06-12 Draft 2/Master.tex
*Tick Tock Tick Tock* 6 days to goooo yayyy
Yeh I did loads of changes and things, look at the log if you REALLY care that much

@@
 \usepackage{tabu}
+\usepackage{url}
 \usepackage{yfonts}
@@
 
+\renewcommand{\arraystretch}{1.5}
+
 \begin{document}
@@
 \maketitle
-\tableofcontents
-\clearpage
+%\tableofcontents
+\medskip
+
+\begin{abstract}
+Computability, or the potential for a device to solve any solvable problem given to it, is an informal notion.
+Its definition can be refined with use of the $\lambda$-Calculus or Turing machines, theoretical computational devices which while having simple definitions have functionality similar to that of a computer.
+Hence, a computer can be defined as a machine which emulates either of these devices fully.
+It will then be shown that the Z3 computer built by Konrad Zuse implements computability with some success.
+\end{abstract}
 
@@
 However, the fundamental ideas of computation and calculation lying alongside the transistors and silicon at the heart of this revolution are no less remarkable in themselves, primarily down to their simplicity.
-Furthermore, unlikely that any modern computer user understands remotely how basic electronics can operate the tasks a computer can perform.
+Furthermore, few modern computer users understand remotely how basic electronics can operate the complex tasks a computer can perform.
 Therefore, I feel the natural way to shed light on this question is to look at the earliest and simplest computers, what they could do and what was distinctive about them.
@@
 
-\textit{(Leibniz's ideas of computation, all effectively computable statements could be expressed in terms of a simple language \& a method to evaluate these statements - highlighting ideas of solving problems)}
+The 18th Century German polymanth Gottfreid Leibniz proposed the ideal of a `Characteristica Universalis', a universal language in which any possible problem can be expressed, and a decision method which could evaluate any problem in this language \cite{barendregt1984introduction}.
+This idea neatly defines what a computer is - a machine which when given a statement in this universal language is able to evaluate it\footnote{In fact, it can be shown that there are problems in a universal language which cannot be solved.
+This was proven indipendently by Alan Turing \cite{turing1936computablenumbers} \& Alonzo Church in 1936, and is known as the Entscheidungsproblem.}.
+The ideal of producing a simple system which can evaluate any `effectively computable' statment is the main challenge of computation.
+% * <mxpen26@gmail.com> 09:38:23 07 Jun 2017 UTC+0100:
+% Footnote to Godel's Incompleteness theorum?
 
-Therefore, in order for a machine to be called a `computer', it must be able to evaluate any member of a set of computable functions.
-However, this is an abstract notion - to clarify it, we must define a simple language in which we can express computable functions, and find a simple method to evaluate them.
-We shall explore the two most common methods, the $\lambda$-Calculus and the Turing Machine, and evaluate them in terms of their similarities and differences, before exploring how well this definition is fulfilled by early computers.
+Therefore, in order for a machine to be called a `computer', it must be able to evaluate any member of a set of `computable functions' (problems expressed in the universal tongue).
+However, this is an abstract notion - to clarify it, a simple language in which we can express computable functions must be defined, and a simple method to evaluate them must be found.
+The two most common methods, $\lambda$-Calculus and the Turing Machine, shall be explored and evaluated in terms of their similarities and differences, before applying this understanding to the early computers.
 
@@
 \subfile{"Section 2 - Turing Machines"}
-
-\section{Universality}
-
-\subfile{"Section 3 - Universality"}
 

### 2017-06-12 Draft 2/Section 1 - Lambda Calculus.tex
*Tick Tock Tick Tock* 6 days to goooo yayyy
Yeh I did loads of changes and things, look at the log if you REALLY care that much

@@
 
-The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability, far from the very real and mechanical world of Turing.
-It deals with a set of objects - for our purposes denoted with single symbolic characters - which define what school mathematics or common computer science would call `functions'.
+The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability.
+It deals with a set of objects - for our purposes denoted by single symbolic characters - which define what school mathematics or common computer science would call `functions'.
 These functions take as their arguments (other objects which the functions act upon) functions alone, and can also output only functions.
@@
 \end{equation*}
-This particular function $f$ applies the function $a$ to the function $b$.
-Note that while commonly we would use the syntax $a(b)$ to express the same thing, it greatly simplifies expression to use this format.
-Church defines these functions through the method of `abstraction' - let us look at a different function to illustrate:
+This particular function $f$ `applies' the function $a$ to the function $b$.
+Note that while the syntax $a(b)$ would normally be used, it greatly simplifies expression if the brackets are omitted.
+Church defines these functions through the method of `abstraction' - to illustrate:
 \begin{equation*}
@@
 It then applies the function $t$ to $u$ and outputs the result.
-For example, if we were to apply this function to the function $a$:
+For example, if this was to be applied to the function $a$:
 \begin{equation*}
@@
 
-Church uses this medium to define a variety of concepts we are already familiar with - firstly, that of positive integers.
+The most basic entities that can be defined in this medium are the natural numbers:
 \cite{church1941lambda}
@@
 \end{equation*}
-Here it can be seen that for each number \textit{n} the argument $s$ is applied to the argument $z$ \textit{n} times - the $s$ functions representing \textit{n} successors to zero ($z$).
+Here it can be seen that for each number \textit{n} the argument $s$ is applied to the argument $z$, \textit{n} times - the $s$ functions representing \textit{n} successors to zero ($z$).
 
-From this, it is not difficult to define an operation that takes a number as input and increments it by 1 - such a function would take three arguments (the first being the number, and the second two being the arguments $s$ and $z$ for the number) and would apply the argument $s$ to the number:
+From this, it is not difficult to define an operation that increments a given number by 1.
+Such a function takes an argument $w$, representing the number to be incremented, and returns a number which is equal to $w$ with the $s$ argument (here represented by $y$) applied to it once.
 \cite{rojas2015lambdatutorial}
 \begin{equation*}
-\bm{\mathrm{S}} = \lambda wyx.y(wyx)
+\begin{aligned}
+\bm{\mathrm{S}} &= \lambda w.\lambda yx.y(wyx)\\
+&= \lambda wyx.y(wyx)
+\end{aligned}
 \end{equation*}
@@
 
-From this concept, we are not far from the nursery-school concept of addition.
-Remembering that each number applies the function $s$ to $z$ \textit{n} times, and that addition is simply incrementing \textit{a} \textit{b} times, addition is as simple as:
+Observing that each number applies the function $s$ to $z$ \textit{n} times, and that addition is simply incrementing \textit{a} \textit{b} times, addition is as simple as:
 \cite{rojas2015lambdatutorial}
@@
 \end{equation*}
-Let us test this by summing \textbf{2} and \textbf{3}:
+This can be tested by summing \textbf{2} and \textbf{3}:
 \begin{gather*}
@@
 
-Church defines functions to operate boolean logic, most significantly defining True and False:
+Church defines functions to operate boolean logic, fundamentally defining True and False to be:
 \cite{rojas2015lambdatutorial}
@@
 \begin{aligned}
-\bm{\mathrm{T}} &= \lambda ab.a,
+\bm{\mathrm{T}} &= \lambda ab.a
   & % seperation
@@
 \end{equation*}
-Bearing in mind the predeces sor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b\geq a$.
+Bearing in mind the predecessor of \textbf{0} is \textbf{0}, this will produce \textbf{0} if $b\geq a$.
 \subsection{Further Conditional Logic}
@@
 
-So far, Church's $\lambda$-Calculus is very close to the operation of a modern programming language.
-It has representation for boolean values, for conditional statements, for positive integers (signed integers can be expressed as a pair of positive integers where the difference is the value to be represented) and arithmetic, as well as set operations for booleans and comparators for integers - In fact, we are very close to our definition of computability, save one thing.
-Continuity and repetition is one of the most significant aspects of computers, the power of this being the ability to transform a finite configuration into a potentially infinite result.
-This is done through one of the most remarkable functions in $\lambda$-Calculus, the \textbf{Y} combinator:
+Continuity is one of the most significant aspects of computation, the power of this being the ability to transform a finite configuration into a potentially infinite result.
+This is done in $\lambda$-Calculus through the use of one of the most remarkable functions, the \textbf{Y} combinator:
 \cite{rojas2015lambdatutorial}
 \begin{equation*}
-\bm{\mathrm{Y}} = \lambda y.(\lambda x.y(xx))(\lambda x.y(xx))
+\bm{\mathrm{Y}} = \lambda y.(\lambda x.y[xx])\ (\lambda x.y[xx])
 \end{equation*}
@@
 \begin{aligned}
-\bm{\mathrm{Y}}a &= (\lambda x.a(xx))[\lambda x.a(xx)]\\
-&= a([\lambda x.a(xx)][\lambda x.a(xx)])\\
-&= a(\bm{\mathrm{Y}}a)
+\bm{\mathrm{Y}}a &= (\lambda x.a[xx])\ (\lambda x.a[xx])\\
+&= a\ [(\lambda x.a[xx])\ (\lambda x.a[xx])]\\
+&= a\ [\bm{\mathrm{Y}}a]
 \end{aligned}
 \end{equation*}
-This function is remarkable as it is a `fixpoint operator' - it is able to easily generate a `fixpoint' of any given function (a value $x$ is a fixpoint of the function $f$ if and only if $fx = x$) by applying the function as the first parameter of the \textbf{Y} combinator.
+This function is remarkable because it is a `fixpoint operator' - it is able to easily generate a `fixpoint' of any given function (a value $x$ is a fixpoint of the function $f$ if and only if $fx = x$) by applying the function as the first parameter of the \textbf{Y} combinator.
 
@@
 \bm{\mathrm{Y\xi 3}} &= \bm{\mathrm{\xi}}(\bm{\mathrm{Y\xi}})\bm{\mathrm{3}}\\
-&= \bm{\mathrm{Z31}}[\bm{\mathrm{M3}}([\bm{\mathrm{Y\xi}}][\bm{\mathrm{P3}}])]\\
+&= \bm{\mathrm{Z3}}\ [\bm{\mathrm{1}}]\ [\bm{\mathrm{M3}}([\bm{\mathrm{Y\xi}}][\bm{\mathrm{P3}}])]\\
 &= \bm{\mathrm{M3}}(\bm{\mathrm{Y\xi}}\bm{2})\\
@@
 $\lambda$-Calculus was described by Church as an `effectively calculable' system, in that it could perform any calculable calculation.
-In more popular terms, it is Turing-complete - we will look at what this is and why this is the case later on in the project.
+In more common terms, it is Turing-complete - we will look at what this is and why this is the case later on.
 However, it is clear to see that the Calculus is able to simulate many functions of the computer - data storage with pairs (pairs of pairs can be used for storing more than two items of data as shown in \cref{sec:LambdaUnivTape}), conditionals and booleans, integers and arithmetic and, finally, the ability to be continuous (circular) from a finite configuration.
-$\lambda$-Calculus is our first attempt to clarify the attributes of a computer, and does so both fundamentally and aesthetically.
+$\lambda$-Calculus is our first attempt to clarify the attributes of a computer, and does so both simply and aesthetically.
 

### 2017-06-12 Draft 2/Section 2 - Turing Machines.tex
*Tick Tock Tick Tock* 6 days to goooo yayyy
Yeh I did loads of changes and things, look at the log if you REALLY care that much

@@
 \lstset{language=Turlang}
+
 \begin{document}
-\renewcommand{\arraystretch}{1.5}
 
-At roughly the same time, the English mathematician Alan Turing was constructing a method to achieve the same goal, but in an entirely different way.
-Rather than building a basic and strongly theoretical system, the concept used was far more physical and far closer to the mechanical computers that eventually implemented this idea.
+At roughly the same time, the English mathematician Alan Turing was constructing a totally different method of achieving the same goal: rather than a basic and heavily theoretical system, it was far more physical and far closer to the mechanical computers that eventually implemented the idea.
 
@@
 Firstly, an ordered set of \textit{cells} of infinite\footnote{Many definitions of Turing Machines have the tape extending infinitely in one direction only - in fact for full functionality a tape extending infinitely in both directions is unnecessary.} length known as \textit{tape}.
-On each of these cells one of a finite set of \textit{symbols} - either alphanumeric characters or the symbol which represents an empty cell.
+On each of these cells is one of a finite set of \textit{symbols} - either alphanumeric characters or the symbol which represents an empty cell.
 At a given point on this tape is a \textit{tape head} (or cursor) which is able to write symbols to the current cell.
 Secondly, a finite set of instructions known as \textit{states} contain finite-length sequences of operations known as the \textit{transition function} which the cursor enacts, and the states that the machine moves to after performing those operations.
-An example description of a set of states would be: \cite{turing1936computablenumbers}
+An example \textit{description} of a set of states would be: \cite{turing1936computablenumbers}
 
@@
 
-This table format shall be used to describe Turing Machine configurations.
-First of all, the last line describes the starting state ($\mathbb{A}$).
-When the machine begins an iteration on any one of these states, it first checks if the symbol aspect of the configuration is equal to the \textit{symbol} currently under the cursor on the tape.
+This description table format shall be used to describe Turing Machine configurations.
+First of all, the final line describes the starting state ($\mathbb{A}$).
+When the machine begins an iteration on any one of these states, it first checks if the symbol aspect of the configuration is equal to the symbol currently under the cursor on the tape.
 If this condition is met, the transition function is carried out - P\textit{n} for any symbol \textit{n} prints the symbol \textit{n} on the tape under the cursor; E erases any symbol under the cursor\footnote{More formally, prints the empty cell symbol}; L moves the cursor to the left; R moves the cursor to the right.
-When these operations are completed, the state is set to that described in the last column.
+When these operations are completed, the state is set to that described in the last column (in future I shall describe this using the $\rightarrow$ symbol, for example $\rightarrow \mathbb{B}$).
 The machine then moves to the next iteration.
@@
 
-The operation of such a machine is significantly more complex than the earlier one.
-Key to the operation is the fact that cells are paired into value cells (odd-numbered cells) on which the symbols of the output sequence are printed.
+The operation of such a machine is significantly more complex than the earlier one - a full explanation of its operation can be found in appendix \ref{appendix:turingexampleexp}.
+Key to the operation is the fact that the tape begins with the sequence \texttt{e e 0} at the start of the tape (this method shall be used in future), and that cells are seperated into value cells and marker cells.
+On value cells (odd-numbered cells) the symbols of the output sequence are printed.
 Only the symbols \texttt{0} and \texttt{1} will ever be printed on these cells.
@@
 
-This machine operates by first printing the symbols \texttt{e e 0} at the start of the tape, before printing the first \texttt{0} of the sequence on the fifth cell, finishing on the third cell and moving to state $\mathbb{A}$.
-(in future I shall represent this finishing state as $\rightarrow \mathbb{A}$).
-
-If $\mathbb{A}$ is triggered, every \texttt{1} consecutively to the left of the cursor inclusively will be marked with \texttt{x}, $\rightarrow \mathbb{B}$.
-
-If $\mathbb{B}$ is triggered, the symbol \texttt{1} is appended to the output sequence, $\rightarrow \mathbb{C}$.
-
-If $\mathbb{C}$ is triggered, the cursor moves leftwards through the labels: if an \texttt{x} is found it is erased and $\rightarrow \mathbb{B}$; if the cursor reaches the beginning (an \texttt{e} is found) $\rightarrow \mathbb{D}$.
-
-If $\mathbb{D}$ is triggered, the symbol \texttt{0} is appended to the output sequence, the cursor moves to the previous value cell and $\rightarrow \mathbb{A}$.
-
-The workings of this algorithm are mostly in states $\mathbb{A}$ and $\mathbb{C}$: after the \texttt{0} is drawn $\mathbb{A}$ draws a number of \texttt{x} symbols equal to the previous number of \texttt{1} symbols drawn.
-$\mathbb{C}$ triggers $\mathbb{B}$ a number of times equal to the number of found \texttt{x} symbols before drawing a \texttt{0} - as $\mathbb{B}$ has already been triggered once, a number of \texttt{1} symbols will be drawn which is one more than the previous number drawn.
-For clarity in the comprehension of this somewhat abstract algorithm, some of the early states have been listed on the next page.
-Empty squares are represented by dots ($\cdot$) and the tape states continue in columns.
-An ellipsis marks the omission of a set of states which are implied or trivial.
-
-\begin{equation*}
-\begin{aligned}
-&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{A}\ \ \ \ \ \ \ \ \ \ & ...&\\
-&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\\
-&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{A}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{A}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 1\ x\ 0} & \rightarrow \mathbb{A}\\
-&\mathtt{e\ e\ 0\ \underset{\uparrow}{\cdot}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 1\ x\ 0} & \rightarrow \mathbb{B}\\
-&\mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & ...&\\
-&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ x\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
-&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ x\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \underset{\uparrow}{x}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{B}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{A}\ \ \ \ \ \ \ \ \ \ & ...&\\
-&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{A}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
-&\mathtt{e\ e\ 0\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1\ x\ 0} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ x\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}\ x\ 0} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & ...&\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ \underset{\uparrow}{0}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{x}\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{B}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ x\ 0\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & ...&\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{x}\ 0\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{0}\ \cdot\ 1} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ \underset{\uparrow}{1}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & ...&\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{B}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\\
-&\mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \underset{\uparrow}{\cdot}\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{D}\\
-&...& &...&\\
-&\mathtt{e\ \underset{\uparrow}{e}\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{C}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{\cdot}} & \rightarrow \mathbb{D}\\
-&\mathtt{e\ e\ \underset{\uparrow}{0}\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1} & \rightarrow \mathbb{D}\ \ \ \ \ \ \ \ \ \ & \mathtt{e\ e\ 0\ \cdot\ 0\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ 0\ \cdot\ 1\ \cdot\ 1\ \cdot\ \underset{\uparrow}{1}\ \cdot\ 0} & \rightarrow \mathbb{D}\\
-\end{aligned}
-\end{equation*}
-
-\clearpage
-
 It is clear from this example that the operation of the Turing Machine is very different from that of an ordinary computer.
@@
 The end result is the same - a solution is produced in the form of the computable sequence written on the value squares, and the machine can continue this sequence without halting indefinitely.
-Unfortunately, the operation of this machine is somewhat complex and involved.
+Unfortunately, the operation of this machine is somewhat complex and obfuscated.
 To simplify this, we will introduce a type of function for the Turing machine.
@@
 
-\textit{M}-functions are effectively an extension of states described by Turing in \cite{turing1936computablenumbers}.
+\textit{M}-functions, described by Turing in \cite{turing1936computablenumbers}, are effectively an extension of states.
 They are denoted by a lowercase letter and a set of arguments contained in brackets - arguments in gothic script refer to states (or other \textit{m}-functions), and arguments in italics refer to symbols.
@@
 The function $\mathbb{f}$ takes three arguments - the states \textfrak{C} and \textfrak{E} and the symbol \textit{a}.
-It is not difficult to see that if $\rightarrow \mathbb{f}$($\mathbb{A}$,$\mathbb{B}$,x) the cursor would trigger $\mathbb{A}$ at the leftmost occurrence of \texttt{x}.
+It is not difficult to see that if $\rightarrow \mathbb{f}$($\mathbb{A}$, $\mathbb{B}$, x) the cursor would trigger $\mathbb{A}$ at the first occurrence of \texttt{x}.
 If no symbols \texttt{x} were found, \textfrak{E} would be triggered on the marker of the first empty value square.
@@
     \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
-    \textit{state} & \textit{symbol} & \textit{transition function} & \textit{final state} \\
+    \textit{state} & \textit{symbol} & \textit{transition\qquad function} & \textit{final state} \\
     \hhline{====}
@@
     \hhline{----}
-    $\mathbb{ps}$(\textit{s},\textfrak{C}, \textfrak{E}) & - & P\textit{s} & \textfrak{C} & Prints \textit{s} \\
+    $\mathbb{p}$(\textit{s},\textfrak{C}, \textfrak{E}) & - & P\textit{s} & \textfrak{C} & Prints \textit{s} \\
     \hhline{====}
@@
 At this point, the similarity between Turing machines and modern computers becomes very clear.
-The machine is able to store more complex information, from integers to strings of characters to images, as binary sequences of value square \texttt{0}s and \texttt{1}s - these shall be stored on the tape as memory.
+The machine is able to store information, from integers to strings of characters to images, as binary sequences of value square \texttt{0}s and \texttt{1}s - these shall be stored on the tape as memory.
 The first data structure we shall define is the simple boolean - only 1 bit (1 value square) long.
@@
 \subsection{Scripted Configurations}
-As we have moved into more and more complex Turing machine functions, it can be noted that the middle two columns of the description are becoming gradually more scarce - this is due to the fact that their operation can be entirely represented within \textit{m}-functions.
+As we have moved into more and more complex Turing machine functions, it can be noted that the middle two columns of the description are becoming gradually more empty - this is due to the fact that their operation can be entirely represented within \textit{m}-functions.
 We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, and $\mathbb{p1}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.
@@
 
-The function $\mathbb{if}$ takes a symbol argument, which is compared to the symbol under the cursor - if they are the same, the machine $\rightarrow$ \textfrak{O}; if not the machine $\rightarrow$ \textfrak{O}.
+The function $\mathbb{if}$ takes a symbol argument, which is compared to the symbol under the cursor - if they are the same, the machine $\rightarrow$ \textfrak{I}; if not the machine $\rightarrow$ \textfrak{O}.
 Since we have now entirely defined the operation of the machine in terms of \textit{m}-functions, we no longer have any need for the central two table columns.
@@
 ifp(r, c, I, O, E) = fl(r,
-    if(c, I, O), E
+    if(c, I, O),
+    E
 )
@@
 
-\subsection{Conclusion}
+\subsection{Universality}
 
 Turing machines are truly remarkable entities.
-While $\lambda$-Calculus was able to mimic the operation of a modern computer (behaving like a purely functional programming language such as Haskell), its beginnings were completely abstract - the mathematical operations of abstraction and application, while being probably more useful than Turing machines in yielding results, were unlike anything which could actually be created in the real world.
-However, Turing machines are completely grounded in physical reality, and it is totally conceivable how one could create such a machine - despite this, they are able to produce results very similar to that of an imperative programming language such as Java - data storage, typed and referenceable variables, and boolean logic, all performed as a sequence of commands.
+While $\lambda$-Calculus was able to mimic the operation of a modern computer (behaving like a purely functional programming language such as Haskell), its axioms were completely abstract - the conceptual operations of abstraction and application, while being probably more useful than Turing machines in terms of yielding practical results, were unlike anything which could actually be created in the real world.
+However, Turing machines are entirely grounded in physical reality, and it is totally conceivable how one could create such a machine, while still being able to produce results very similar to that of an imperative programming language such as C - data storage, typed and referenceable variables, and boolean logic, all performed as a sequence of commands.
 From these building blocks, integers and more complex concepts can be produced.
 This is the truly remarkable thing about Turing machines - they illustrate clearly how mechanisms can in fact solve computable problems.
-As such, it is most useful to define a computer as something which is able to behave like a Turing machine - in effect, a computer is distinguished by the fact that it can simulate a Turing machine.
-A machine with this ability shall be called 'Turing-complete'
+
+However, up to this point, computational ability has been measured by the potential of a machine to perform a variety of tasks that appear to demonstrate computation.
+This is not a sufficiently rigorous definition - a machine which seems to behave like a computer is not necessarily able to evaluate any computable function.
+For practicality's sake, it seems natural for Turing Machines to be chosen to be the pinnacle of computability: any machine that can be programmed in such a way that it emulates a Turing machine shall be called a  `Turing-complete' computer, and any problem a Turing machine can solve is a computable function.
+
+It is unseemly that the abstract notion of computability relies necessarily on the specific design of the Turing machine: the idea of computability is a robust, almost Platonic reality, that Turing machines, $\lambda$-Calculus and all other effectively calculable devices, physical or theoretical, participate within equally.
+In fact, the idea of Turing-completeness presented earlier achieves this aim.
+This is the concept of Universality.
+
+The main idea behind Universality is the concept of the Universal Machine, a machine which is able to entirely emulate another given system.
+As shown in \cite{turing1936computablenumbers}, a Turing machine can be configured in such a way that it emulates a Turing machine; this machine reads a description table from the start of the tape, and then produces the output that the machine described in the pre-written table would produce.
+Furthermore, $\lambda$-Calculus is also Turing-complete - this is demonstrated entirely in appendix \ref{appendix:lambdauniversaldemo}.
+This is done by producing a function that takes the current configuration of a Turing machine (in terms of the tape, state and description table) as input, and transforms it into the next configuration in sequence that a Turing machine would produce.
+This function would then be run repeatedly on the configuration using the \textbf{Y} combinator, hence emulating the action of Turing machines.
+Hence the $\lambda$-Calculus can produce a Universal Machine for Turing machines.
+
+Most remarkably, Turing machines are in fact able to also emulate $\lambda$-Caluculus.
+This shall not be demonstrated directly, but it seems intuitive that a Turing machine could carry out processes of abstraction and application since they are at heart simple algorithmic processes; a Turing macihne would evaluate $\lambda$-terms in a similar way to how the human mind would.
+This leads us onto the remarkable fact that since Turing machines and $\lambda$-Calculus can produce Universal Machines for each other, each has the potential to perform any task the other can perform, and hence they are equal in power.
+Furthermore, many other theoretical methods of computation such as Kurt G\"odel's General Recursive Functions also share this equivalence \cite{copeland2002ctt}.
+
+It therefore seems that the informal notion of computability can be formally defined with the use of one of these equivalent computational systems - this is a truly remarkable result, which produces a very strong basis for computability.
+With this test for computability in place, the question of whether World War 2 produced computing machines becomes apparently trivial.
 

### 2017-06-12 Draft 2/Section 3 - Universality.tex
*Tick Tock Tick Tock* 6 days to goooo yayyy
Yeh I did loads of changes and things, look at the log if you REALLY care that much

@@
 
-\renewcommand{\arraystretch}{1.5}
 So far, we have explored how our two methods of computation can perform many common operations, including data manipulation \& storage, on top of looping and conditional branching.
-Unfortunately, it is too vague to simply define a 'comuputer' as a system which can perform a somewhat arbitrary set of operations - we must refine this to a simple set of functions.
-The easiest way of doing this is by assuming that a certain system can perform every operation a computer can perform.
-For this purpose, we have chosen Turing machines, due to the fact that they are easy to realise physically.
-Now, in order to prove that any system is a 'computer', we must simply prove that it can perform any operation a Turing machine can perform - in essence, it must be able to fully emulate the operation of a Turing machine.
+However, having an arbitrary set of abilities that mimic computation is not necessarily the same as a machine being able to evaluate any computable statement; they must participate in the abstract concept of computability.
+For practicality's sake, we have chosen Turing Machines to be the pinnacle of computability; hence, any machine that can be programmed in such a way that it emulates a Turing machine shall be called a computer.
+In this section we shall discover that the definition does not rely on Turing machines alone; rather, the idea of computability is a robust, almost Platonic reality, that Turing machines, $\lambda$-Calculus and all other computers, physical or theoretical, participate within.
+This is the idea of Universality.
 
- This essentially means that a machine, given a specific Turing machine starting configuration, should be able to produce every consecutive following state (i.e.
+A Universal machine is a machine which participates in this ideal - it is able to emulate a Turing machine.
+This essentially means that a Universal machine, given a specific Turing machine starting configuration, should be able to produce every consecutive following state (i.e.
 it takes a machine's description table as input, and generates an infinite sequence of the following tape configurations \& the corresponding finishing state for that step).
-Any machine that can do this shall be called a \textit{Universal Machine}.
-
-\subsection{Standard Turing Description Form}
-
-First, we must define what we actually mean by a description table - we shall do this by describing a standard form for these tables, as shown by Turing in \cite{turing1936computablenumbers}.
-Looking at the first table described, we can see that any transition function follows a similar format: E; [E, R]; [E, L]; P\textit{a}; [ P\textit{a}, R]; [ P\textit{a}, L] or no entry at all.
-More complex transition functions such as those found in later tables can always be put into one of these forms through the addition of intermediary states which are called in sequence.
-
-Next, let us rename the states as $q_0$, $q_1$, $q_2$, $...$, $q_n$ for clarity (the initial state shall always be called $q_0$, the second $q_1$ and so on).
-Furthermore, the symbols shall be renamed $S_0$, $S_1$, $S_2$, $...$, $S_n$ - in this case, $S_0$ will represent the blank square, $S_1$ will represent \texttt{0} and $S_2$ will represent \texttt{1}.
-The movement operations L and R will be renamed $M_L$, $M_R$, and the operation to keep the tape stationary is simply $M_S$.
-Our tables are now of form:
-
-\medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
-    \textit{state} & \textit{symbol} & \textit{transition function} & \textit{final state} \\
-    \hhline{====}
-    $q_i$ & $S_i$ & P$S_k$, $M_{L/R/S}$ & $q_m$ \\
-    \hhline{----}
-\end{tabu}
-
-\medskip
-
-Lines such as
-
-\medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    $q_i$ & $S_i$ & E, $M_{L/R/S}$ & $q_m$ \\
-\end{tabu}
-\medskip
-are to be written as
-
-\medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    $q_i$ & $S_i$ & P$S_0$, $M_{L/R/S}$ & $q_m$ \\
-\end{tabu}
-\medskip
-and lines such as
-
-\medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    $q_i$ & $S_i$ & $M_{L/R/S}$ & $q_m$ \\
-\end{tabu}
-\medskip
-are to be written as
-
-\medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    $q_i$ & $S_i$ & P$S_i$, $M_{L/R/S}$ & $q_m$ \\
-\end{tabu}
-\medskip
-in order for all lines to be written in the first format.
-As the number of symbols used for a machine is always finite, it is possible to enumerate under every single state an action for every single symbol $S_i$ that the machine could be reading.
-In this way, "All" and "Not \textit{a}" will be portrayed in this format as the enumerated behaviours for every relevant symbol.
-This idea also allows the last simplification shown in the table above to work.
-
-This expanded and generalised configuration is much more helpful to us, as while any Turing machine configuration (including using \textit{m}-functions) can be written in this format, it is very concise and regular.
-This allows it to be given as input to our universal machines.
+Any machine that can achieve this shall be called a computer.
 
 \subsection{Universality in the $\lambda$-Calculus}
-Firstly, we shall prove that $\lambda$-Calculus is Turing complete by building a universal machine using only $\lambda$-functions.
+We shall prove that $\lambda$-Calculus is Turing complete by building a universal machine using only $\lambda$-functions.
 The core of the machine will be a function which calculates a single step in the Turing machine's calculation: It will receive as its parameters the current configuration of the tape and the current state.
-As this function will be unique to the specific machine that is being emulated, the entire behaviour of the machine based on this configuration (i.e.
-the machine's table) shall be contained within this function.
 The function will then be applied to itself repeatedly to produce the sequences of states.
-
-\subsubsection{Emulating the Tape}\label{sec:LambdaUnivTape}
-In order to achieve this, we must define certain new objects in $\lambda$-Calculus.
-First of all, ordered lists - these will be used to describe the current content of the tape.
-These are defined as a sequence of nodes, where each node is a pair with the first element as the content of the node and the second element is the next node in the sequence (as shown in \cite{tromp2007binary}).
-The final node will have \textbf{0} as its first element to signify the end of the list - the second element will never be referred to; as such \textbf{0} will be used as a placeholder (of course this only works if the list is not designed to contain any values of zero or true, as they will be indistinguishable from the end marker - I shall use \textbf{1} to represent $S_0$, \textbf{2} to represent $S_1$ and so on).
-For example, the list [a,b,c,d,e] would be represented as:
-\begin{equation*}
-\lambda l.la(\lambda m.mb(\lambda n.nc(\lambda o.od(\lambda p.pe(\lambda z.z\bm{\mathrm{00}})))))
-\end{equation*}
-In order to obtain the first element (head), the argument \textbf{T} would be applied to the list; to get the remaining elements (tail) the \textbf{F} argument would be applied. 
-Furthermore, to prepend an element to the start of a list:
-\begin{equation*}
-\bm{\mathrm{:}} = \lambda xlf.f[x][l]
-\end{equation*}
-This takes an element to prepend $x$, and a list $l$, and constructs a new pair with the given element as the first element and the original list as the second.
-
-The tape of the machine extends infinitely in both directions either side of the cursor.
-We shall represent this as a pair of lists: $T_p$ as the list of all the predecessors to the cursor and $T_s$ as the list of all the successors to the cursor.
-The predecessors shall be listed in reverse order, such that the head of $T_p$ is the symbol directly to the left of the cursor.
-The head of $T_s$ is the symbol considered to be `under' the cursor, the next element is the symbol to the right of that, and so on.
-These tapes will begin as a single node, and as the machine requires further squares in either direction further nodes will be added.
-\begin{equation*}
-T_a = \lambda f.f T_p T_s
-\end{equation*}
-
-\subsubsection{Movement Operations}
-To emulate cursor movement, we will create transformation functions for the tape. These operations will shift the tape by moving the head of $T_s$ to the head of $T_p$ or vice versa.
-
-\begin{gather*}
-\begin{aligned}
-\bm{M}_L &= \lambda t_a f.f [(t_a\bm{\mathrm{T}})\bm{\mathrm{F}}] [\bm{\mathrm{:}}([t_a\bm{\mathrm{T}}]\bm{\mathrm{T}})(t_a\bm{\mathrm{F}})]\\
-\bm{M}_R &= \lambda t_a f.f [\bm{\mathrm{:}}([t_a\bm{\mathrm{F}}]\bm{\mathrm{T}})(t_a\bm{\mathrm{T}})] [(t_a\bm{\mathrm{F}})\bm{\mathrm{F}}]\\
-\bm{M}_S &= \lambda t_a.t_a\\
-\end{aligned}
-\end{gather*}
-The $\bm{M}_L$ function produces a new tape pair, after taking the original tape pair as parameter $t_a$.
-The first element of this new pair is simply the tail of $T_p$ ($T_p$ being found at $T_a\bm{\mathrm{T}})$.
-The second element is the head of $T_p$ prepended to the entirety of $T_s$ (found at $T_a\bm{\mathrm{T}})$.
-$\bm{M}_R$ will do the effective opposite, prepending the head of $T_s$ to $T_p$ and producing the tail of $T_s$.
-$\bm{M}_S$ Will keep the tape in its current state.
-
-\subsubsection{Infinite-Length Tape}
-
-Unfortunately, the tape which we are currently dealing with is unlike that of a Turing machine, due to the fact that it is of finite length - we cannot write a single list in $\lambda$-Calculus which expresses the entire tape.
-As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, we will replace it with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as the tail.
-To do this, we will have another transformation function which will check if either head element of the tape pair is \textbf{0}, and if so, will replace it with an empty square node $\bm{\epsilon}$ - otherwise it will simply be replaced with the original head:
-
-\begin{gather*}
-\begin{aligned}
-\bm{\epsilon} &= \lambda g.g[\bm{\textbf{1}}][\lambda d.d\bm{\mathrm{0}}\bm{\mathrm{0}}] \\
-\bm{C} &= \lambda t_a g.g[\bm{\mathrm{Z}}(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})(\bm{\epsilon})(t_a\bm{\mathrm{T}}\bm{\mathrm{T}})][\bm{\mathrm{Z}}(t_a\bm{\mathrm{F}}\bm{\mathrm{T}})(\bm{\epsilon})(t_a\bm {\mathrm{F}}\bm{\mathrm{T}})]
-\end{aligned}
-\end{gather*}
-This transformation will be applied after every tape movement operation.
-
-\subsubsection{Printing to the Tape}
-
-The operation function that writes a given symbol to the square beneath the cursor is not a particularly complex transformation - it simply replaces the current head of $T_s$ with the given numeral $a$.
-
-\begin{equation*}
-\bm{W} = \lambda a t_a p.p[t_a\bm{\mathrm{T}}][\mathrm{\bm{:}} a (t_a \bm{\mathrm{FF}})]
-\end{equation*}
-
-\subsubsection{Storing \& Accessing states}
-%\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}
-Once again, in order to store the symbol, transition function and final state associated with each states, we shall use a list.
-The first element of the list shall represent $q_0$, the second $q_1$ and so on.
-Each element of the list will be a list in itself.
-Each element of this nested list shall refer to a single line described by the symbol aspect of the configuration.
-These elements are pairs: the first element being the symbol to be found (a numeral), the second being the action to be performed under this configuration.
-
-The action itself will be yet another pair.
-The first element is the transition function that should be executed on the tape - this will be of the form $(\bm{C})(\bm{M}_{L/R/S})(\bm{W}a)$, which applies first a write operation before a movement operation and the tape length correction operation.
-The second element is a function which, when given the description of the machine, finds the given state.
-We shall note these m-configuration references as shown, with the example of the reference to $q_3$:
-\begin{equation*}
-\bm{Q}_3 = \lambda l.l\bm{\textbf{FFFT}}
-\end{equation*}
-This gets the fourth head of the given list, which refers to $q_3$.
-
-%As an example, here is the description for the first machine described, which generates the sequence \texttt{01010101...} (for simplicity, this version does not leave \textit{s}-squares blank).
-For reference, here is the enumerated table:
-%\medskip\noindent\begin{tabu} to \textwidth{XXXX}
-%    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
-%    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
-%    \hhline{====}
-%    $q_0$ & $S_0$ & PS_1       & $\mathbb{A}$ \\
-%    $q_0$ & $S_1$ & PS_2 & $\mathbb{A}$ \\ 
-%    $q_0$ & \texttt{1}    & R, R, P\texttt{0} & $\mathbb{A}$ \\ 
-%\end{tabu}
-%We shall represent this table as such:
-%\begin{gather*}
-%\begin{aligned}
-%\bm{d}
-%\end{aligned}
-%\end{gather*}
-
-%[I cba to do this now]
-
-In order to find which action should be performed given a certain configuration, we shall use the following function which produces a pair of a list transition function and an state reference from a current state, the current symbol, and the description function.
-As part of this function, the recursive function $\bm{\rho}$ must be used in conjunction with the \textbf{Y} combinator, which returns the action aspect of the first pair under symbol $s$ in list $l$ (the $r$ argument is the argument which would represent the function as a whole, and is recursively called by the \textbf{Y} combinator)
-
-\begin{gather*}
-\begin{aligned}
-\bm{\rho} &= \lambda rls.(\bm{\doteq}(l\bm{\mathrm{TT}})s)(l\bm{\mathrm{TF}})(r(l\bm{\mathrm{F}})s)\\
-\bm{I} &= \lambda qsd.\bm{\mathrm{Y}\rho}(qd)s
-\end{aligned}
-\end{gather*}
-
-\subsubsection{Universal Machine State Change Operation}
-
-At last, we can involve all of these functions to create a single operation which transforms a given machine configuration (state, $T_p$ \& $T_s$, and the description table) into the machine configuration for the next state.
-This configuration shall be represented as a pair, the first element being a pair of the state reference and the tape, and the second element as the description table.
-The $\bm{\nu}$ function gets the action function from the given machine configuration.
-
-\begin{gather*}
-\begin{aligned}
-\bm{\nu} &= \lambda c.\bm{I}(c\bm{\mathrm{TT}})([c\bm{\mathrm{TF}}]\bm{\mathrm{FT}})(c\bm{\mathrm{F}})\\
-\bm{X} &= \lambda cf.f[\lambda g.g[(\bm{\nu}c)\bm{\mathrm{F}}][((\bm{\nu}c)\bm{\mathrm{T}})(c\bm{\mathrm{TF}})]]c
-\end{aligned}
-\end{gather*}
-
-\subsubsection{Universal Machine State Generator}
-
-Finally, we shall define a recursive function which produces every consecutive state by running $\bm{X}$ on itself repeatedly.
-When this is evaluated, each iteration of the machine shall be passed into the \textbf{Y} combinator, leading to each consecutive state being found during evaluation.
-
-\begin{gather*}
-\begin{aligned}
-\bm{\omega} &= \lambda uc.u(\bm{X}c) \\
-\bm{U} &= \lambda c.\bm{\mathrm{Y}}\bm{\omega}c
-\end{aligned}
-\end{gather*}
+Due to the complexity of this idea, not every step will be explained in full here; however, a full explanation can be found in appendix \ref{appendix:lambdauniversaldemo}.
 

### 2017-06-12 Draft 2/Section 4 - Zuse's Z3.tex
*Tick Tock Tick Tock* 6 days to goooo yayyy
Yeh I did loads of changes and things, look at the log if you REALLY care that much

@@
     Lw,
-    case
+    case,
+    switch
   },
-  sensitive=true, % keywords are not case-sensitive
+  sensitive=true, % keywords are case-sensitive
   morecomment=[l]{//}, % l is for line comment
@@
 
-At this point, we have an almost complete definition of 'computer' - a machine which is able to fully implement the concept of effective computability.
-This can be done most simply through the implementation of an effectively computable method of computation, such as a Turing Machine.
+At this point, we have a complete definition of `computer' - a device which is able to fully implement the concept of effective computability.
+This can be done most simply through the emulation of an effectively computable method of computation, such as a Turing Machine.
 In order to address the question of whether this was achieved during WW1 we must apply this test to the physical instruments created during this period.
-\textit{TODO: Colossus}
 
-\textit{TODO: Context of Z3}
+The Z3, completed in Berlin in 1941 by Konrad Zuse, was arguably the first programmable computer ever built.
+A far faster and more reliable version of its two predecessors, the Z1 and Z2, the Z3 was advanced because of its ability to carry out long sequences of calculations, written as instructions on punched tape, with the potential to store values in memory.
+While still very simplistic, and not directly intended for universal computation, the Z3 is structurally far closer to achieving this aim than other machines of the time; Hence, in this section I shall attempt to implement a Universal machine in the Z3 in order to determine its nature as a computing machine.
 
@@
 Using this method to emulate switch statements, we can produce an equivalent to an indirect addressing operation.
-This operation is of form $y = (x)$, which sets $n$ to the value at address location $x$, where $x$ is an integer $n_a \leq x \leq n_b$, $n_a$ and $n_b$ being integer constants representing the limits of the region of memory that can be addressed by this function.
-$x$ could potentially be the output from a previous arithmetical operation.
-Relying on the fact that this region is finite (and furthermore that the tape length is also finite), this can be done using a switch statement with a case for every address $z$ between $n_a$ and $n_b$ as shown.
+This operation is of form $y = (x)$, which sets $y$ to the value at address location $x$, where $x$ is an integer $n_a \leq x \leq n_b$, $n_a$ and $n_b$ being integer constants representing the limits of the region of memory that can be addressed by this function.
+$x$ could potentially be the output from a previous arithmetical operation, which could be read from memory.
+Relying on the fact that this region is finite (and furthermore that the tape length is also finite), this can be done most simply with a switch statement with a case for every address $z$ between $n_a$ and $n_b$ as shown.
 \begin{gather*}
@@
 &\qquad ... ,                                   \\
-&\qquad z:\	\mathrm{Pr}\ z;\ \mathrm{Ps}\ a			\\
+&\qquad z:\	\mathrm{Pr}\ z;\ \mathrm{Ps}\ a,    \\
 &\qquad ... 					                \\
@@
 \end{gather*}
+These cases are enumerated within the switch for all $n_a \leq z \leq n_b$; hence, when the statement is executed, the only case where the contents of address $z$ will be written to $a$ is the case where $x=z$; hence, $a$ will be set to the contents of address $x$.
 At this point, it becomes very clear the extent to which the Z3 is not suited to universal computation.
 When every single applicable memory address must be specified individually, with five operations per address to implement the case, each operation consisting of four instructions, it is obvious that the Z3 is in no way a \textit{practical} universal machine.
+\subsection{The Z3 as a Turing Machine}
 
-To emulate a Turing machine using these new tools, one considers the tape to be the region of memory between $n_a$ and $n_b$, and 
+The fact that the Z3 can be extended in such ways as to allow for conditional branching and indirect addressing makes the jump to Turing-completeness small.
+The tape can be said to represent the region of memory between $n_a$ and $n_b$ with an integer variable between $n_a$ and $n_b$ which represents the index of the cursor, which can be moved by adding or subtracting 1.
+The symbol beneath the cursor can be read through the indirect addressing operator, and new values for the symbol beneath the cursor and the movement of the cursor can be extracted from a description through the use of conditional branches.
+
+The result of this section, that arithmetic alone can produce universality, is surprising and counterintuitive.
+However, the fundamental concept behind this is that within each arithmetical operation are conditional branches that the processor performs; Turing-completeness is embedded within the Z3's operation, albeit invisible to the programmer.
+These operations are intended to lift this branching to the surface level so they can control the program's flow.
+
+The primary criticism of this techique is that it slows down computation enormously.
+Running at roughly 5.33Hz with 3 cycles for addition, 4-5 for subtraction and 16 for multiplication (from \cite{rojas1997z3architecture}), to perform each case statement within a switch the Z3 would take up to $\sim$7.5 seconds on top of the time for the operation itself; for the indirect addressing operation alone, when this occurs for every single addressable memory slot it is clear that for a single iteration of the Turing machine the Z3 would take an unfeasably long time.
+From a purely theoretical point of view this is irrelevant - it is clear that this particular programming of the Z3 is useless in the same way that using a Turing Machine to solve real-world problems would be totally impractical.
+
+Therefore, we can say that from a totally abstract, totally theoretical perspective, World War 2 did in fact produce an equivalent to a modern computer.
+However, like many of the computers of this period, while effectively equivalent to a modern computer, the Z3 was entirely unlike anything one would encounter today and as such would not be suited to perform anything beyond its simplistic intended use.
+
+The major breakthrough in computation which allowed for the first clearly universal machines was the implementation of a Von Neumann Architecture, which allowed computers to run programs from memory\footnote{Of course, because Turing Machines are themselves Universal machines (see \cite{turing1936computablenumbers}), this was theoretically achieved with the Z3; Von Neumann machines were oriented towards performing in such a way.}.
+The first machine to implement this was the Manchester Small Scale Experimental Machine (SSEM), or 'Baby' \cite{napperWEB17baby}, which stored data using the Williams-Kilburn Tube, a type of cathode ray tube.
+Its successor, the Manchester Mark 1 contained a more advanced instruction set - however, it must be noted that in terms of our definition, the Mark 1 was no more of a computer than the SSEM.
 \end{document}

### 2017-06-14 Draft 2/Master.tex
Looks like we're done here
Oh wait I'm 3000 words over the limit dearie me

@@
 
+\section*{The Limits of Computation}
+
+In our journey, we began with the abstract philosophical concept of computability, knowing nothing beyond roughly what we aim to achieve with it.
+Defining $\lambda$-Calculus, we were able to see that computation in all its power follows simply from the very natural concept of functions.
+Defining Turing machines, we saw that this abstract concept is not distant from a physical realisation; and exploring the functionality of Z3, that even relatively simplistic machines can demonstrate computation.
+It has become clear that the target of computability is not as difficicult to achive as it could appear, and that it was achived before the end of World War 2.
+
+The fact that we have been able to provide a unified definition of logical decision-making along the way is, in my opinion, the most remarkable result of this study.
+We must consider, however, that there are limits to computation - firstly, there is a set of so called 'undecideable' problems with solutions which cannot be solved algorithmically, including finding integer solutions to Diophantine equations \cite{matiyasevich1993hilbert} and the Halting problem, which would determine whether a given computer program runs indefinitely \cite{turing1936computablenumbers}.
+Furthermore, when the solution to a problem is probabalistic (e.g.
+in simulation of quantum processes - see \cite{feynman1982simulating}) as all computation produces the same solution given a problem.
+As such, despite effective computability being a simple, beautiful and practical theory, it does not achieve Leibniz's aim of a Universal Language; in truth, I believe that the existance of an algorithmic description of everything would be a surprising result.
+Of course, Mathematics is filled with surprises.
+
 \subfile{"Appendices"}

### 2017-06-14 Draft 2/Section 4 - Zuse's Z3.tex
Looks like we're done here
Oh wait I'm 3000 words over the limit dearie me

--- 2017-06-04 Draft 2/Section 4 - Zuse's Z3.tex
@@
 
-At this point, we have an almost complete definition of 'computer' - a machine which is able to fully implement the concept of effective computability.
-This can be done most simply through the implementation of an effectively computable method of computation, such as a Turing Machine.
+At this point, we have a complete definition of `computer' - a device which is able to fully implement the concept of effective computability.
+This can be done most simply through the emulation of an effectively computable method of computation, such as a Turing Machine.
 In order to address the question of whether this was achieved during WW1 we must apply this test to the physical instruments created during this period.
-\textit{TODO: Colossus}
+The
 
-\textit{TODO: Context of Z3}
+Z3, completed in Berlin in 1941 by Konrad Zuse, was arguably the first programmable computer ever built.
+A far faster and more reliable version of its two predecessors, Z1 and Z2, Z3 was advanced because of its ability to carry out long sequences of calculations, written as instructions on punched tape, with the potential to store values in memory.
+While still very simplistic, and not directly intended for universal computation, Z3 is structurally far closer to achieving this aim than other machines of the time; Hence, in this section I shall attempt to implement a Universal machine in Z3 in order to determine its nature as a computing machine.
 
-\subsection{The Architecture of the Z3}
+\subsection{The Architecture of Z3}
 
-In this section I shall give a broad functional overview of the Z3.
+In this section I shall give a broad functional overview of Z3.
 I shall explore primarily the function and usage of the machine, i.e.
@@
 
-The Z3 was primarily purposed towards performing simple arithmetical calculations - addition, subtraction, multiplication, division, and square root.
+Z3 was primarily purposed towards performing simple arithmetical calculations - addition, subtraction, multiplication, division, and square root.
 The operands would be read from memory or from input from a keyboard, and the results would be written to memory or shown on a display.
@@
 
+\textit{Basically it can store decimals, and these integers are referred to by a numeric 'address'. for the moment we'll use letters instead of numbers because we're cool like that}
+
 \subsubsection{Programming Model}
 
-The instruction set for the Z3 consisted of three types of operation - I/O, memory and arithmetic.
+The instruction set for Z3 consisted of three types of operation - I/O, memory and arithmetic.
 These instructions would be performed with respect to two floating-point registers, $R_1$ and $R_2$, which act as the two arguments for any arithmetical operation, and could be written to and read from by the non-arithmetical operations.
@@
 For each operation, the operation is performed on $R_1$ and $R_2$, and the result is written to $R_1$. 
-\subsection{Universality in the Z3}
+\subsection{Universality in Z3}
 
@@
 
-At first glance, it is unclear that the Z3 can be made into a universal machine due to the fact that it allows for neither conditional branching\footnote{The ability to perform different operations depending on the state of a stored value} nor indirect addressing\footnote{The ability to refer to values stored in memory when the address of that memory is not specifically referred to in the program but is rather obtained from the value of some variable currently in memory}.
+At first glance, it is unclear that Z3 can be made into a universal machine due to the fact that it allows for neither conditional branching\footnote{The ability to perform different operations depending on the state of a stored value} nor indirect addressing\footnote{The ability to refer to values stored in memory when the address of that memory is not specifically referred to in the program but is rather obtained from the value of some variable currently in memory}.
 However, through use of the tools available to the programmer these features can be emulated, and a Turing Machine can be simulated.
@@
 , P_n$, we can produce a sequence of commands that will allow only the operation $P_z$ to perform.
-Due to the nature of the Z3 requiring a full sequence of commands to be executed without exception, every one of these operations will be evaluated; however, only operation $P_z$ will be allowed to actually affect memory.
+Due to the nature of Z3 requiring a full sequence of commands to be executed without exception, every one of these operations will be evaluated; however, only operation $P_z$ will be allowed to actually affect memory.
 
@@
 \end{gather*}
-At this point, it becomes very clear the extent to which the Z3 is not suited to universal computation.
-When every single applicable memory address must be specified individually, with five operations per address to implement the case, each operation consisting of four instructions, it is obvious that the Z3 is in no way a \textit{practical} universal machine.
+These cases are enumerated within the switch for all $n_a \leq z \leq n_b$; hence, when the statement is executed, the only case where the contents of address $z$ will be written to $a$ is the case where $x=z$; hence, $a$ will be set to the contents of address $x$.
+At this point, it becomes very clear the extent to which  is not suited to universal computation.
+When every single applicable memory address must be specified individually, with five operations per address to implement the case, each operation consisting of four instructions, it is obvious that Z3 is in no way a \textit{practical} universal machine.
 
-To emulate a Turing machine using these new tools, one considers the tape to be the region of memory between $n_a$ and $n_b$, and 
+\subsection{Z3 as a Turing Machine}
+
+With these new methods implemented in Z3, construction of a Universal machine seems trivial.
+As shown in \cite{harel1980folk}, a Turing machine can be produced using only a single continuous loop and the functionality of Z3.
+The ends of the instruction tape can be attached to each other as they are run through the machine, allowing for a continuous loop.
+The tape is represented as the memory region between $n_a$ and $n_b$, and the cursor index is stored as an integer that can be moved through incrementation or decrementation.
+The tape can be read through indirect addressing, and the transition can be derived from the state and read symbol through conditional branching.
+
+The result of this section, that arithmetic alone can produce universality, is surprising and counterintuitive.
+However, the fundamental concept behind this is that within each arithmetical operation are conditional branches that the processor performs; Turing-completeness is embedded within Z3's operation, albeit invisible to the programmer.
+These tools are intended to lift this branching to the surface level so they can control the program's flow.
+
+A clear criticism of this techique is that it slows down computation enormously.
+Running at roughly 5.33Hz with 3 cycles for addition, 4-5 for subtraction and 16 for multiplication (from \cite{rojas1997z3architecture}), to perform each case statement within a switch Z3 would take up to $\sim$7.5 seconds on top of the time for the operation itself; for the indirect addressing operation alone, when this occurs for every single addressable memory slot it is clear that for a single iteration of the Turing machine Z3 would take an unfeasably long time.
+From a purely theoretical point of view this is irrelevant - it is clear that this particular programming of Z3 is useless in the same way that using a Turing Machine to solve real-world problems would be totally impractical.
+
+Therefore, we can say that from a totally abstract, totally theoretical perspective, World War 2 did in fact produce an equivalent to a modern computer.
+However, like many of the computers of this period, while effectively equivalent to a modern computer, Z3 was entirely unlike anything one would encounter today and as such would not be suited to perform anything beyond its simplistic intended use.
+
+The major breakthrough in computation which allowed for the first clearly universal machines was the implementation of a Von Neumann Architecture, which allowed computers to run programs from memory\footnote{Of course, because Turing Machines are themselves Universal machines (see \cite{turing1936computablenumbers}), this was theoretically achieved with Z3; Von Neumann machines were oriented towards performing in such a way.}.
+The first machine to implement this was the Manchester Small Scale Experimental Machine (SSEM), or `Baby' \cite{napperWEB17baby}, which stored data using the Williams-Kilburn Tube, a type of cathode ray tube.
+Its successor, the Manchester Mark 1 contained a more advanced instruction set, and was significantly more powerful.
+
 \end{document}

### 2017-06-15 Draft 2/Appendices.tex
Okay so when I say done this time I mean REALLY done

@@
 
-\section{Explanation of Example Turing Machine}\label{appendix:turingexampleexp}
+\section{Turing Machine Demonstrating Value \& Marker Squares}\label{appendix:turingexampleexp}
 
@@
 
-Producing the sequence \texttt{010110111011110111110...}, this machine operates by first printing the symbols \texttt{e e 0} at the start of the tape, before printing the first \texttt{0} of the sequence on the fifth cell, finishing on the third cell and moving to state $\mathbb{A}$.
+Producing the sequence \texttt{010110111011110111110...} on primary squares, this machine operates by first printing the symbols \texttt{e e 0} at the start of the tape, before printing the first \texttt{0} of the sequence on the fifth cell, finishing on the third cell and moving to state $\mathbb{A}$.
 

### 2017-06-15 Draft 2/Master.tex
Okay so when I say done this time I mean REALLY done

@@
 \title{Did WW2 Produce an Equivalent to a Modern Computer?}
-\date{February 23, 2017}
 \author{Max Penrose}
@@
 Computability, or the potential for a device to solve any solvable problem given to it, is an informal notion.
-Its definition can be refined with use of the $\lambda$-Calculus or Turing machines, theoretical computational devices which while having simple definitions have functionality similar to that of a computer.
+Its definition can be refined with use of the $\lambda$-Calculus or Turing machines, theoretical computational devices which while having simple definitions produce functionality similar to that of a computer.
 Hence, a computer can be defined as a machine which emulates either of these devices fully.
@@
 \section*{Introduction}
-Computation rules the modern world - from the internet to the rise of automated labour, today's humanity puts colossal value in the hands of the remarkable machines that are computers.
+Computation rules the modern world - from the internet to the rise of automated labour, today's humanity puts colossal value in the hands of these remarkable machines.
 However, the fundamental ideas of computation and calculation lying alongside the transistors and silicon at the heart of this revolution are no less remarkable in themselves, primarily down to their simplicity.
@@
 The most significant problem in answering this question is the actual definition of `computer'.
-In the early 20th Century, prior to developments in this field, any human which evaluated statements through computation was known, logically, as a `computer'.
-As such, we will explore the qualities that an entity - human, machine or other - must have for it to be able to perform computation.
+In the early 20th Century, prior to developments in this field, any human which evaluated statements through computation was known, as a `computer'.
+We will therefore explore the qualities that an entity - human, machine or other - must have for it to be able to perform computation.
 
 The 18th Century German polymanth Gottfreid Leibniz proposed the ideal of a `Characteristica Universalis', a universal language in which any possible problem can be expressed, and a decision method which could evaluate any problem in this language \cite{barendregt1984introduction}.
-This idea neatly defines what a computer is - a machine which when given a statement in this universal language is able to evaluate it\footnote{In fact, it can be shown that there are problems in a universal language which cannot be solved.
-This was proven indipendently by Alan Turing \cite{turing1936computablenumbers} \& Alonzo Church in 1936, and is known as the Entscheidungsproblem.}.
+This idea is a final aim for computation - a system which when given a statement in this universal language is able to evaluate it.
 The ideal of producing a simple system which can evaluate any `effectively computable' statment is the main challenge of computation.
-% * <mxpen26@gmail.com> 09:38:23 07 Jun 2017 UTC+0100:
-% Footnote to Godel's Incompleteness theorum?
 
@@
 However, this is an abstract notion - to clarify it, a simple language in which we can express computable functions must be defined, and a simple method to evaluate them must be found.
-The two most common methods, $\lambda$-Calculus and the Turing Machine, shall be explored and evaluated in terms of their similarities and differences, before applying this understanding to the early computers.
+The two most common methods, $\lambda$-Calculus and the Turing Machine, shall be explored and evaluated in terms of their similarities and differences, before they are used to evaluate early computers.
 
@@
 
-\section*{The Limits of Computation}
+\section*{Epilogue: Limitations of Computation}
 

### 2017-06-15 Draft 2/Section 2 - Turing Machines.tex
Okay so when I say done this time I mean REALLY done

@@
 
-An example of a more complex Turing machine is shown below, which generates the sequence \texttt{010110111011110111110...} again on alternate cells, beginning at the fifth cell.
-\cite{turing1936computablenumbers}
-
-\medskip\noindent\begin{tabu} to \textwidth{XXXX}
-    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
-    \textit{state} & \textit{symbol} & \textit{transition function} & \textit{final state} \\
-    \hhline{====}
-    \multirow{1}{*}{$\mathbb{Q}$} & Any        & P\texttt{e}, R P\texttt{e}, R,  P\texttt{0}, R, R, P\texttt{0}, L, L & $\mathbb{A}$ \\
-    \hhline{----}
-    \multirow{2}{*}{$\mathbb{A}$} & \texttt{0} & R, P\texttt{x}, L, L, L                   & $\mathbb{A}$ \\
-                                  & \texttt{1} &                                  & $\mathbb{B}$ \\
-    \hhline{----}
-    \multirow{2}{*}{$\mathbb{B}$} & Any        & R, R                             & $\mathbb{B}$ \\
-                                  & None       & P\texttt{1}, L                            & $\mathbb{C}$ \\
-    \hhline{----}
-    \multirow{3}{*}{$\mathbb{C}$} & \texttt{x} & E, R                             & $\mathbb{B}$ \\
-                                  & \texttt{e} & R                                & $\mathbb{D}$ \\
-                                  & None       & L, L                             & $\mathbb{C}$ \\
-    \hhline{----}
-    \multirow{2}{*}{$\mathbb{D}$} & Any        & R, R                             & $\mathbb{D}$ \\
-                                  & None       & P\texttt{0}, L, L                         & $\mathbb{A}$ \\
-\end{tabu}
-
-\noindent $\Rightarrow \mathbb{Q}$
-
-\medskip
-
-The operation of such a machine is significantly more complex than the earlier one - a full explanation of its operation can be found in appendix \ref{appendix:turingexampleexp}.
-Key to the operation is the fact that the tape begins with the sequence \texttt{e e 0} at the start of the tape (this method shall be used in future), and that cells are seperated into value cells and marker cells.
+To aid the operation of Turing machines, the tape shall begin with the sequence \texttt{e e 0}, and cells shall be seperated into value cells and marker cells.
 On value cells (odd-numbered cells) the symbols of the output sequence are printed.
 Only the symbols \texttt{0} and \texttt{1} will ever be printed on these cells.
-To the right of each value cell is a label cell (an even-numbered cell).
-These cells will either be left empty or will contain a 'marker' symbol, which labels the symbol on the value cell to the left.
-These symbols can be erased and overwritten, and are not part of the output sequence.
-Only one label cell is needed to contain multiple markers, or more descriptive markers for a single value cell, as this can be achieved with a sufficiently rich variety of marker symbols.
-This method is frequently used by Alan Turing in \cite{turing1936computablenumbers}.
-
-It is clear from this example that the operation of the Turing Machine is very different from that of an ordinary computer.
-However, the core components are still mostly present - conditionals in the form of the symbol tests in the second column, variables in the form of labels, and continuity and looping when a state triggers itself - a form of recursion.
-The end result is the same - a solution is produced in the form of the computable sequence written on the value squares, and the machine can continue this sequence without halting indefinitely.
-Unfortunately, the operation of this machine is somewhat complex and obfuscated.
-To simplify this, we will introduce a type of function for the Turing machine.
+To the right of each value cell is a label cell.
+These cells will either be left empty or will contain a 'marker' symbol, which labels the symbol on the value cell to the left; these are not part of the output sequence.
+This method is frequently used by Alan Turing in \cite{turing1936computablenumbers}, and an example machine can be found in appendix \ref{appendix:turingexampleexp}.
 
@@
 Of course, any table description that includes or refers to \textit{m}-functions can be written as an ordinary table as described in \cref{sec:TMacIntro}.
-This is possible because of the finite nature of both states and symbols; simply by listing in separate rows under the same state every permutation of the finite symbols and states that the function could possibly take substituted in.
+This is possible because of the finite nature of both states and symbols.
 
 \subsubsection{Common Operations}
-
-In this section a set of common and useful \textit{m}-functions are defined that will be used regularly in future.
 
@@
 At this point, the similarity between Turing machines and modern computers becomes very clear.
-The machine is able to store information, from integers to strings of characters to images, as binary sequences of value square \texttt{0}s and \texttt{1}s - these shall be stored on the tape as memory.
+The machine is able to store information, from integers to strings of characters to images, as binary sequences of value square \texttt{0}s and \texttt{1}s.
 The first data structure we shall define is the simple boolean - only 1 bit (1 value square) long.
@@
 Most remarkably, Turing machines are in fact able to also emulate $\lambda$-Caluculus.
-This shall not be demonstrated directly, but it seems intuitive that a Turing machine could carry out processes of abstraction and application since they are at heart simple algorithmic processes; a Turing macihne would evaluate $\lambda$-terms in a similar way to how the human mind would.
+This shall not be demonstrated directly, but it seems intuitive that a Turing machine could carry out processes of abstraction and application since they are at heart simple algorithmic processes; a Turing machine would evaluate $\lambda$-terms in a similar way to how the human mind would.
 This leads us onto the remarkable fact that since Turing machines and $\lambda$-Calculus can produce Universal Machines for each other, each has the potential to perform any task the other can perform, and hence they are equal in power.

### 2017-06-15 Draft 2/Section 4 - Zuse's Z3.tex
Okay so when I say done this time I mean REALLY done

@@
 
-At this point, we have a complete definition of `computer' - a device which is able to fully implement the concept of effective computability.
-This can be done most simply through the emulation of an effectively computable method of computation, such as a Turing Machine.
-In order to address the question of whether this was achieved during WW1 we must apply this test to the physical instruments created during this period.
-The
-
+In order to address the question of whether this was achieved during WW1 we must explore how well this concept was implemented in the machines of this period.
 Z3, completed in Berlin in 1941 by Konrad Zuse, was arguably the first programmable computer ever built.
-A far faster and more reliable version of its two predecessors, Z1 and Z2, Z3 was advanced because of its ability to carry out long sequences of calculations, written as instructions on punched tape, with the potential to store values in memory.
-While still very simplistic, and not directly intended for universal computation, Z3 is structurally far closer to achieving this aim than other machines of the time; Hence, in this section I shall attempt to implement a Universal machine in Z3 in order to determine its nature as a computing machine.
+A far more reliable version of its predecessors, Z1 and Z2, Z3 was advanced because of its ability to carry out long sequences of calculations written as instructions on punched tape, on top of its ability to store values in memory.
+While still very simplistic, and not directly intended for universal computation, Z3 was structurally far closer to achieving this aim than other machines of the time.
+In this section I shall therefore attempt to implement a Universal machine in Z3 in order to determine its nature as a computing machine.
 
@@
 
-\subsubsection{Data Storage}
-
-\textit{Basically it can store decimals, and these integers are referred to by a numeric 'address'. for the moment we'll use letters instead of numbers because we're cool like that}
+Z3 was able to store floating-point decimals in its memory\footnote{Each 22-bit floating-point number was stored through the use of metal rods which could be in one of two states to represent bits.
+In  something similar to standard form, each number was composed of an `exponent' representing the order of magnitude of the number, and a `significand' that represented the digits of the number; see \cite{rojas1997z3architecture} for details.}, which could be referred to by the programmer through the use of a numeric address of a particular data slot.
+For the sake of clarity, we shall use single lowercase letters to represent addresses rather than the 6-bit unisgned integers of Z3.
 

### 2017-06-18 Draft 2/Appendices.tex
Hmm looks like we're all done here
WIth 17 hours 42 minutes to go as well, I'm impressed

@@
 \appendixpage
-\section{Further Arithmetic in $\lambda$-Calculus}
-Multiplication can also be calculated by defining the function \textbf{M}:
-\cite{rojas2015lambdatutorial}
+\section{Further Arithmetic in $\lambda$-Calculus}\label{appendix:lambdaarithmetic}
+
+\subsection{Exponents}
+
+An `exponent' function to find $a^b$ of astonishing simplicity can be defined:
+\cite{barendregt1984introduction}
 \begin{equation*}
-\bm{\mathrm{M}} = \lambda wyx.w(yx)
+\bm{\mathrm{E}} = \lambda ab.ba
 \end{equation*}
@@
 \begin{aligned}
-\bm{\mathrm{M22}} &= (\lambda wyx.w(yx))(\lambda ab.a(a(b)))(\lambda sz.s(s(z)))\\
-&= \lambda x.(\lambda ab.a(a(b)))[(\lambda sz.s(s(z)))x]\\
-&= \lambda x.(\lambda ab.a(a(b)))[\lambda z.x(x(z))]\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))]([\lambda z.x(x(z))]b))\\
-&= \lambda x.(\lambda b.[\lambda z.x(x(z))][x(x(b))])\\
-&= \lambda x.(\lambda b.x(x(x(x(b)))))\\
-&= \lambda xb.x(x(x(x(b))))\\
-&= \bm{\mathrm{4}}
+\bm{\mathrm{E32}} &= (\lambda ab.ba)\ (\lambda sz.s(s(s(z))))\ (\lambda ty.t(t(y)))\\
+&= \lambda ty.t(t(y)))\ (\lambda sz.s(s(s(z)))\\
+&= \lambda y.[\lambda sz.s(s(s(z)))]\ ([\lambda ux.u(u(u(x)))]\ y)\\
+&= \lambda y.[\lambda sz.s(s(s(z)))]\ [\lambda x.y(y(y(x)))]\\
+&= \lambda y.[\lambda z.[\lambda x.y(y(y(x)))]\ ([\lambda x.y(y(y(x)))]\ ([\lambda x.y(y(y(x)))]\ z))]\\
+&= \lambda y.[\lambda z.[\lambda x.y(y(y(x)))]\ ([\lambda x.y(y(y(x)))]\ [y(y(y(z)))])]\\
+&= \lambda y.[\lambda z.[\lambda x.y(y(y(x))]\ ([y(y(y(y(y(y(z))))))])]\\
+&= \lambda y.[\lambda z.[y(y(y(y(y(y(y(y(y(z)))))))))]]\\
+&= \lambda yz.y(y(y(y(y(y(y(y(y(z)))))))))\\
+&= \bm{\mathrm{9}} = \bm{\mathrm{3^2}}
 \end{aligned}
@@
 
-An `exponent' function to find $a^b$can also be defined, of astonishing simplicity:
-\cite{barendregt1984introduction}
-\begin{equation*}
-\bm{\mathrm{E}} = \lambda ba.ab
-\end{equation*}
+\subsection{Integers}
+
+Integers are defined as a pair of natural numbers, whose difference is the value of the integer (any function that outputs an integer shall be written with a bar):
 \begin{gather*}
 \begin{aligned}
-\bm{\mathrm{E23}} &= (\lambda ab.ab)(\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda sz.s(s(z)))(\lambda ty.t(t(t(y))))\\
-&= (\lambda z.[\lambda ty.t(t(t(y)))]([\lambda ux.u(u(u(x)))]z))\\
-&= (\lambda z.[\lambda ty.t(t(t(y))][\lambda x.z(z(z(x)))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]([\lambda x.z(z(z(x)))]y))])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([\lambda x.z(z(z(x)))][z(z(z(y)))])])\\
-&= (\lambda z.[\lambda y.[\lambda x.z(z(z(x))]([z(z(z(z(z(z(y))))))])])\\
-&= (\lambda z.[\lambda y.[z(z(z(z(z(z(z(z(z(y)))))))))]])\\
-&= \lambda zy.z(z(z(z(z(z(z(z(z(y)))))))))\\
-&= \bm{\mathrm{9}} = \bm{\mathrm{3^2}}
+\lvari{-1} &= \lambda x.x\ \lvar{01} &= \lambda x.x\ \lvar{12}\\
+\lvari{-2} &= \lambda x.x\ \lvar{02} &= \lambda x.x\ \lvar{13}
+\end{aligned}    
+\end{gather*}
+
+\begin{gather*}
+\begin{aligned}
+\lvari{S} &= \lambda nx.x\ [\lvar{S}(n\lvar{T})][n\lvar{F}] \\
+\lvari{P} &= \lambda nx.x\ [n\lvar{T}][\lvar{S}(n\lvar{F})]
+\end{aligned}    
+\end{gather*}
+
+\begin{gather*}
+\begin{aligned}
+\lvari{A} &= \lambda abx.x\ [(a\lvar{T})\lvar{S}(b\lvar{T})]\ [(a\lvar{F})\lvar{S}(b\lvar{F})] \\
+\lvari{D} &= \lambda abx.x\ [(a\lvar{T})\lvar{S}(b\lvar{F})]\ [(a\lvar{F})\lvar{S}(b\lvar{T})] \\
+\lvari{M} &= \lambda abx.x\ [(\lvar{M}\ [a\lvar{T}][b\lvar{T}])\ \lvar{S}\ (\lvar{M}\ [a\lvar{F}][b\lvar{F}])]\ [(\lvar{M}\ [a\lvar{T}][b\lvar{F}])\ \lvar{S}\ (\lvar{M}\ [a\lvar{F}][b\lvar{T}])] \\
+\end{aligned}    
+\end{gather*}
+
+The \textbf{$\pm$} function outputs \textbf{T} for positive integers and \textbf{F} for negative integers ($\lvari{0}$ is considered to be positive), and the \textbf{$|$} function calculates the absolute value of the given integer.
+
+\begin{gather*}
+\begin{aligned}
+\lvar{\pm} &= \lambda i.(\lvar{\geq}\ [i\lvar{T}]\ [i\lvar{F}]) \\
+\lvar{|} &= \lambda i. (\lvar{\pm}i)\ [D\ (i\lvar{T}) (i\lvar{F})]\ [D\ (i\lvar{F}) (i\lvar{T})]
+\end{aligned}    
+\end{gather*}
+
+Rational numbers can be represented in a similar way as a fraction of two integers.
+
+\subsection{Division of Natural Numbers}
+
+The \textbf{Q} function (which of course stands for quotient) calculates the number of times $a$ is contained within $b$ recursively: \cite{allisonWEB17integers}
+
+\begin{gather*}
+\begin{aligned}
+\lvar{\delta} &= \lambda dpq.(\lvar{\geq}pq)\ [\lvar{S}\ (d\ [\lvar{D}pq]\ q)]\ [\lvar{0}] \\
+\lvar{Q} &= \lambda ab.\lvar{Y\delta}ab
 \end{aligned}    
@@
 
-Producing the sequence \texttt{010110111011110111110...} on primary squares, this machine operates by first printing the symbols \texttt{e e 0} at the start of the tape, before printing the first \texttt{0} of the sequence on the fifth cell, finishing on the third cell and moving to state $\mathbb{A}$.
+Producing the sequence \texttt{010110111011110111110...} on primary squares \cite{turing1936computablenumbers}, this machine operates by first printing the symbols \texttt{e e 0} at the start of the tape, before printing the first \texttt{0} of the sequence on the fifth cell, finishing on the third cell and moving to state $\mathbb{A}$.
 
@@
 
-\section{Detailed Demonstration of the Universality of $\lambda$-Calculus}\label{appendix:lambdauniversaldemo}
+\section{Demonstration of the Universality of $\lambda$-Calculus}\label{appendix:lambdauniversaldemo}
 
@@
     \hhline{====}
-    $q_i$ & $S_i$ & P$S_k$, $M_{L/R/S}$ & $q_m$ \\
+    $q_i$ & $S_j$ & P$S_k$, $M_{L/R/S}$ & $q_m$ \\
     \hhline{----}
@@
 \noindent\begin{tabu} to \textwidth{XXXX}
-    $q_i$ & $S_i$ & E, $M_{L/R/S}$ & $q_m$ \\
+    $q_i$ & $S_j$ & E, $M_{L/R/S}$ & $q_m$ \\
 \end{tabu}
@@
 \noindent\begin{tabu} to \textwidth{XXXX}
-    $q_i$ & $S_i$ & P$S_0$, $M_{L/R/S}$ & $q_m$ \\
+    $q_i$ & $S_j$ & P$S_0$, $M_{L/R/S}$ & $q_m$ \\
 \end{tabu}
@@
 \noindent\begin{tabu} to \textwidth{XXXX}
-    $q_i$ & $S_i$ & $M_{L/R/S}$ & $q_m$ \\
+    $q_i$ & $S_j$ & $M_{L/R/S}$ & $q_m$ \\
 \end{tabu}
@@
 \noindent\begin{tabu} to \textwidth{XXXX}
-    $q_i$ & $S_i$ & P$S_i$, $M_{L/R/S}$ & $q_m$ \\
+    $q_i$ & $S_j$ & P$S_j$, $M_{L/R/S}$ & $q_m$ \\
 \end{tabu}
@@
 \noindent in order for all lines to be written in the first format.
-As the number of symbols used for a machine is always finite, it is possible to enumerate under every single state an action for every single symbol $S_i$ that the machine could be reading.
+As the number of symbols used for a machine is always finite, it is possible to enumerate under every single state an action for every single symbol $S_j$ that the machine could be reading.
 As such, `All' and `Not \textit{a}' may be portrayed in this format.
@@
 \subsection{Emulating the Tape}\label{sec:LambdaUnivTape}
-To allow for storage of large sequences of data in $\lambda$-Calculus, ordered lists must be defined.
+To allow for storage of large sequences of data in $\lambda$-calculus, ordered lists must be defined.
 These will be used to store the content of the tape.
@@
 The tape of the machine extends infinitely in both directions either side of the cursor.
-This shal be represented as a pair of lists: $T_p$ as the list of all the predecessors to the cursor and $T_s$ as the list of all the successors to the cursor.
+This shall be represented as a pair of lists: $T_p$ as the list of all the predecessors to the cursor and $T_s$ as the list of all the successors to the cursor.
 The predecessors shall be listed in reverse order, such that the head of $T_p$ is the symbol directly to the left of the cursor.
@@
 
-Unfortunately, the tape which that is currently being dealt with is unlike that of a Turing machine, due to the fact that it is of finite length - one cannot write a single list in $\lambda$-Calculus which expresses the entire tape.
+Unfortunately, the tape which that is currently being dealt with is unlike that of a Turing machine, due to the fact that it is of finite length - one cannot write a single list in $\lambda$-calculus which expresses the entire tape.
 As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, it shall be replaced with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as the tail.
@@
 
-In order to find which action should be performed given a certain configuration, one can use the following function which produces a pair of a list transition function and a state reference from a current state, the current symbol, and the description function.
-As part of this function, the recursive function $\bm{\rho}$ must be used in conjunction with the \textbf{Y} combinator, which returns the action aspect of the first pair under symbol $s$ in list $l$ (the $r$ argument is the argument which would represent the function as a whole, and is recursively called by the \textbf{Y} combinator)
+In order to find which action should be performed given a certain configuration, one can use the following function which produces a pair of a list transition function and a state reference from a current state $q$, the current symbol $s$, and the description function $d$
+.
+As part of this function, the recursive function $\bm{\rho}$ must be used in conjunction with the \textbf{Y} combinator, which returns the action aspect of the first pair under symbol $s$ in list $l$ (the $r$ argument is the argument which would represent the function as a whole, and is recursively called by the \textbf{Y} combinator).
 

### 2017-06-18 Draft 2/Master.tex
Hmm looks like we're all done here
WIth 17 hours 42 minutes to go as well, I'm impressed

@@
 \documentclass {article}
-\usepackage[a4paper, total={6in, 8in}]{geometry}
+\usepackage[a4paper, total={6in, 8in}, top=1.3in, bottom=1.5in]{geometry}
 \usepackage[utf8]{inputenc}
@@
 \renewcommand{\arraystretch}{1.5}
+\newcommand*\lvar[1]{\bm{\mathrm{#1}}}
+\newcommand*\lvari[1]{\overline{\bm{\mathrm{#1}}}}
 
@@
 \medskip
+\medskip
 
@@
 Computability, or the potential for a device to solve any solvable problem given to it, is an informal notion.
-Its definition can be refined with use of the $\lambda$-Calculus or Turing machines, theoretical computational devices which while having simple definitions produce functionality similar to that of a computer.
+Its definition can be refined with use of the $\lambda$-calculus or Turing machines, theoretical computational devices which while having simple definitions produce functionality similar to that of a computer.
 Hence, a computer can be defined as a machine which emulates either of these devices fully.
-It will then be shown that the Z3 computer built by Konrad Zuse implements computability with some success.
+It will then be shown that the Z3 computer built by Konrad Zuse during World War 2 implements computability with some success.
 \end{abstract}
@@
 The most significant problem in answering this question is the actual definition of `computer'.
-In the early 20th Century, prior to developments in this field, any human which evaluated statements through computation was known, as a `computer'.
+In the early 20th Century, prior to developments in this field, any human who evaluated statements through computation was known as a `computer'.
 We will therefore explore the qualities that an entity - human, machine or other - must have for it to be able to perform computation.
 
-The 18th Century German polymanth Gottfreid Leibniz proposed the ideal of a `Characteristica Universalis', a universal language in which any possible problem can be expressed, and a decision method which could evaluate any problem in this language \cite{barendregt1984introduction}.
+The 18th Century German polymath Gottfreid Leibniz proposed the ideal of a `Characteristica Universalis', a universal language in which any possible problem can be expressed, and a decision method which could evaluate any problem in this language \cite{barendregt1984introduction}.
 This idea is a final aim for computation - a system which when given a statement in this universal language is able to evaluate it.
-The ideal of producing a simple system which can evaluate any `effectively computable' statment is the main challenge of computation.
+The ideal of producing a simple system which can evaluate any `effectively computable' statement is the main challenge of computation.
 
-Therefore, in order for a machine to be called a `computer', it must be able to evaluate any member of a set of `computable functions' (problems expressed in the universal tongue).
+Therefore in order for a machine to be called a `computer' it must be able to evaluate any member of a set of `computable functions' (problems expressed in the universal tongue).
 However, this is an abstract notion - to clarify it, a simple language in which we can express computable functions must be defined, and a simple method to evaluate them must be found.
-The two most common methods, $\lambda$-Calculus and the Turing Machine, shall be explored and evaluated in terms of their similarities and differences, before they are used to evaluate early computers.
+The two most common methods, $\lambda$-
+and the Turing machine, shall be explored, before they are used to evaluate early computers.
+
+Throughout this paper any equation, table or code listing which is not clearly cited can be considered my own work.
+
+\clearpage
 
@@
 In our journey, we began with the abstract philosophical concept of computability, knowing nothing beyond roughly what we aim to achieve with it.
-Defining $\lambda$-Calculus, we were able to see that computation in all its power follows simply from the very natural concept of functions.
-Defining Turing machines, we saw that this abstract concept is not distant from a physical realisation; and exploring the functionality of Z3, that even relatively simplistic machines can demonstrate computation.
-It has become clear that the target of computability is not as difficicult to achive as it could appear, and that it was achived before the end of World War 2.
+Defining $\lambda$-calculus, we were able to see that computation in all its power follows simply from the very natural concept of functions.
+Defining Turing machines, we saw that this abstract concept is not distant from a physical realisation; and exploring the functionality of Z3 we found that even relatively simplistic machines can demonstrate computation.
+It has become clear that the target of computability is not as difficult to achieve as it could appear, and that it was achieved before the end of World War 2.
 
 The fact that we have been able to provide a unified definition of logical decision-making along the way is, in my opinion, the most remarkable result of this study.
-We must consider, however, that there are limits to computation - firstly, there is a set of so called 'undecideable' problems with solutions which cannot be solved algorithmically, including finding integer solutions to Diophantine equations \cite{matiyasevich1993hilbert} and the Halting problem, which would determine whether a given computer program runs indefinitely \cite{turing1936computablenumbers}.
-Furthermore, when the solution to a problem is probabalistic (e.g.
-in simulation of quantum processes - see \cite{feynman1982simulating}) as all computation produces the same solution given a problem.
-As such, despite effective computability being a simple, beautiful and practical theory, it does not achieve Leibniz's aim of a Universal Language; in truth, I believe that the existance of an algorithmic description of everything would be a surprising result.
+We must consider, however, that there are limits to computation - firstly, there is a set of so called `undecideable' problems with solutions which cannot be solved algorithmically, including finding integer solutions to Diophantine equations \cite{matiyasevich1993hilbert} and the Halting problem, which would determine whether a given computer program runs indefinitely \cite{turing1936computablenumbers}.
+Furthermore, computation fails when the solution to a problem is probabilistic (e.g.
+in simulation of quantum processes - see \cite{feynman1982simulating}) as all algorithms produce the same solution given a problem.
+As such, despite effective computability being a simple, beautiful and practical theory, it does not achieve Leibniz's aim of a Universal Language; in truth, I believe that the existence of an algorithmic description of everything would be a surprising result.
 Of course, Mathematics is filled with surprises.
@@
 \subfile{"Appendices"}
-
+\clearpage
 \bibliography{bibliography}

### 2017-06-18 Draft 2/Section 1 - Lambda Calculus.tex
Hmm looks like we're all done here
WIth 17 hours 42 minutes to go as well, I'm impressed

@@
 
-The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s, as a purely mathematical and abstract definition of computability.
-It deals with a set of objects - for our purposes denoted by single symbolic characters - which define what school mathematics or common computer science would call `functions'.
+The simplest, and in my opinion the most beautiful definition of effective calculability was introduced by the American mathematician Alonzo Church in the 1930s as a purely mathematical and abstract definition of computability.
+%It deals with a set of objects - for our purposes denoted by single symbolic characters - which define what school mathematics or common computer science would call `functions'.
 These functions take as their arguments (other objects which the functions act upon) functions alone, and can also output only functions.
 Take, for example the function $f$:
-\begin{equation*}
-f = ab
-\end{equation*}
-This particular function $f$ `applies' the function $a$ to the function $b$.
+%\begin{equation*}
+%f = ab
+%\end{equation*}
+%This particular function $f$ `applies' the function $a$ to the function $b$.
 Note that while the syntax $a(b)$ would normally be used, it greatly simplifies expression if the brackets are omitted.
 Church defines these functions through the method of `abstraction' - to illustrate:
-\begin{equation*}
-\lambda u.tu
-\end{equation*}
-This function takes one single argument, which it names the abstract name $u$.
+%\begin{equation*}
+%\lambda u.tu
+%\end{equation*}
+%This function takes one single argument, which it names the abstract name $u$.
 It then applies the function $t$ to $u$ and outputs the result.
 For example, if this was to be applied to the function $a$:
+%\begin{equation*}
+%(\lambda u.tu) a = ta	
+%\end{equation*}
+
+%Functions can take multiple arguments through the use of nesting:
+%\begin{gather*}
+%\begin{aligned}
+%\lambda a.(\lambda b.ba) &=  \lambda ab.ba \\
+%[\lambda a.(\lambda b.ba)]uv &= (\lambda b.bu)v \\ &= vu
+%\end{aligned}
+%\end{gather*}
+\subsection{Abstraction}
+
+Every entity in Church's $\lambda$-calculus is a function \cite{church1941lambda}.
+Numbers, mathematical operations and conditionals are all simply functions; no other objects exist in their own right.
+Functions are defined as objects that take an input, and map it to an output.
+Consider the following function:
+
 \begin{equation*}
-(\lambda u.tu) a = ta	
+    f(x) = 3x^2 - 1
 \end{equation*}
 
-Functions can take multiple arguments through the use of nesting:
+This function is called $f$; it takes an input $x$, known as an `argument', performs some operations on it and outputs it.
+In this case, $x$ means nothing outside the function, and is only a placeholder for any input; it is an `abstract' name.
+
+Church defines this syntax for this idea as follows (this is known as `abstraction'):
+
+\begin{equation*}
+    \bm{\mathrm{f}} = \lambda x.3x^2-1
+\end{equation*}
+
+This has the same meaning as the function above; the name of the abstract argument goes between the $\lambda$ and $.$ symbols, and the operation on the argument comes after.
+This is helpful because it removes the need for a name; the action of the function is described entirely within the $\lambda$-term, hence the name shall only be used to represent the function and changes nothing about its operation.
+Of course, the idea of $3x^2-1$ is totally meaningless in $\lambda$-calculus because ideas of `$-$' or `$3$' have not been defined; integers and operations shall be defined in terms of functions later in the section.
+
+\subsection{Application}
+
+When functions are applied to entities (or rather, other functions), the abstract argument of the function is replaced throughout the expression; $f(2) = 3 \times 2^2 - 1 = 11$.
+This is done in $\lambda$-calculus by writing the entity to be given as the argument to the direct right of the abstraction (brackets are employed to separate expressions as usual):
+
 \begin{gather*}
 \begin{aligned}
-\lambda a.(\lambda b.ba) &=  \lambda ab.ba \\
-[\lambda a.(\lambda b.ba)]uv &= (\lambda b.bu)v \\ &= vu
+\bm{\mathrm{f}}\ 2 &= (\lambda x.3x^2-1)\ 2\\
+&= 3 \times 2^2 - 1\\
+&= 11
 \end{aligned}
@@
 
+Functions that take more than one argument take the entities to the right of the abstraction and input them all into the expression (from left to right).
+This can be done through the abstraction outputting a second abstraction when the first argument is applied, into which the second argument is inputted:
+
+\begin{gather*}
+\begin{aligned}
+&(\lambda u.\lambda v. vu)\ f\ \mathrm{g}\\
+&= (\lambda v.vf)\ \mathrm{g}\\
+&= g\ f
+\end{aligned}
+\end{gather*}
+We shall write this as:
+\begin{equation*}
+\lambda uv.vu = \lambda u.\lambda v. vu
+\end{equation*}
+
 \subsection{Arithmetical definitions}
 
+In order to make $\lambda$-calculus useful to us, we must use this simplistic language of functions to define tangible entities.
 The most basic entities that can be defined in this medium are the natural numbers:
@@
 \begin{aligned}
-\bm{\mathrm{S2}} &= (\lambda wyx.y(wyx)) (\lambda sz.s(s(z)))\\
-&= \lambda yx.y([\lambda sz.(s(s(z)))]yx)\\
-&= \lambda yx.y(y(y(z)))\\
+\bm{\mathrm{S2}} &= (\lambda wyx.y(wyx))\ [\lambda sz.s(s(z))]\\
+&= \lambda yx.y([\lambda sz.(s(s(z)))]\ yx)\\
+&= \lambda yx.y(y(y(x)))\\
 &= \lambda sz.s(s(s(z)))\\
@@
 
+Multiplication can also be calculated by defining the function \textbf{M}:
+\cite{rojas2015lambdatutorial}
+\begin{gather*}
+\begin{aligned}
+\bm{\mathrm{M}} &= \lambda wy.\lambda x.w(yx) \\
+&= \lambda wyx.w(yx)
+\end{aligned}
+\end{gather*}  
+\begin{gather*}
+\begin{aligned}
+\bm{\mathrm{M22}} &= (\lambda wyx.w(yx))(\lambda ab.a(a(b)))(\lambda sz.s(s(z)))\\
+&= \lambda x.(\lambda ab.a(a(b)))\ [(\lambda sz.s(s(z)))\ x]\\
+&= \lambda x.(\lambda ab.a(a(b)))\ [\lambda z.x(x(z))]\\
+&= \lambda x.(\lambda b.[\lambda z.x(x(z))]\ ([\lambda z.x(x(z))]\ b))\\
+&= \lambda x.(\lambda b.[\lambda z.x(x(z))]\ [x(x(b))])\\
+&= \lambda x.(\lambda b.x(x(x(x(b)))))\\
+&= \lambda xb.x(x(x(x(b))))\\
+&= \bm{\mathrm{4}}
+\end{aligned}
+\end{gather*}
+
 \subsection{Boolean Logic}
@@
 
-These concepts are the base of conditional branching in computation, and in $\lambda$-Calculus operate like \textit{if} statements found in most programming languages.
+These concepts are the base of conditional branching in computation, and in $\lambda$-calculus operate like \textit{if} statements found in most programming languages.
 For such operations, the concept of a `pair' exists:
@@
 If the first argument is \textbf{T} the function will always return \textbf{T}, as it is the first argument.
-If the first argument is \textbf{F} on the other hand, the value of the second argument will be returned (the $\vee$ function is dependant on at least one argument being \textbf{T} - if this is not the first argument, the outcome is simply whether the second argument is \textbf{T} or not).
+If the first argument is \textbf{F} on the other hand, the value of the second argument will be returned (the $\vee$ function is dependent on at least one argument being \textbf{T} - if this is not the first argument, the outcome is simply whether the second argument is \textbf{T} or not).
 The remaining functions work in a similar way.
@@
 
-However, in order to develop other conditional tests we will need a `predecessor' function - a more complex concept in $\lambda$-Calculus.
+However, in order to develop other conditional tests we will need a `predecessor' function - a more complex concept in $\lambda$-calculus.
 \subsection{Subtraction}
 
-The elusive predecessor function was created by Stephen Kleene, a student of Church's, and was something of a landmark in the development of $\lambda$-Calculus.
+The elusive predecessor function was created by Stephen Kleene, a student of Church's, and was something of a landmark in the development of $\lambda$-calculus.
 
@@
 \begin{equation*}
-\bm{\mathrm{P}} = \lambda n.[n \bm{\psi} (\lambda x.\bm{\mathrm{00}})] \bm{\mathrm{F}} 
+\bm{\mathrm{P}} = \lambda n.[n \bm{\psi} (\lambda x.x\bm{\mathrm{00}})] \bm{\mathrm{F}} 
 \end{equation*}
@@
 \begin{aligned}
-\bm{\mathrm{P3}} &= (\lambda n.n [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}] \bm{\mathrm{F}}) [\lambda sz.s(s(s(z)))]\\
-&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
-&= ([\lambda sz.s(s(s(z)))] [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})] [\lambda x.\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda x.\bm{\mathrm{00}}]))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c(\bm{\mathrm{S}}[\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})([\lambda x.\bm{\mathrm{00}}]\bm{\mathrm{T}})))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})]([\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})](\lambda c.c\bm{\mathrm{10}}))\bm{\mathrm{F}}\\
-&= [\lambda pc.c(\bm{\mathrm{S}}(p\bm{\mathrm{T}}))(p\bm{\mathrm{T}})][\lambda c.c\bm{\mathrm{21}}]\bm{\mathrm{F}}\\
-&= [\lambda c.c\bm{\mathrm{32}} ])\bm{\mathrm{F}}\\
+\bm{\mathrm{P3}} &= (\lambda n.n \bm{\psi} [\lambda x.x\bm{\mathrm{00}}] \bm{\mathrm{F}}) [\lambda sz.s(s(s(z)))]\\
+&= ([\lambda sz.s(s(s(z)))]\ [\bm{\psi}] [\lambda x.x\bm{\mathrm{00}}]) \bm{\mathrm{F}}\\
+&= (\bm{\psi}(\bm{\psi}(\bm{\psi}[\lambda x.x\bm{\mathrm{00}}])))\bm{\mathrm{F}}\\
+&= (\bm{\psi}(\bm{\psi}(\lambda c.c(\bm{\mathrm{S}}[\lambda x.x\bm{\mathrm{00}}]\bm{\mathrm{T}})([\lambda x.x\bm{\mathrm{00}}]\bm{\mathrm{T}}))))\bm{\mathrm{F}}\\
+&= (\bm{\psi}(\bm{\psi}(\lambda c.c\bm{\mathrm{10}})))\bm{\mathrm{F}}\\
+&= (\bm{\psi}(\lambda c.c\bm{\mathrm{21}}))\bm{\mathrm{F}}\\
+&= (\lambda c.c\bm{\mathrm{32}})\bm{\mathrm{F}}\\
 &= \bm{\mathrm{2}}
@@
 Continuity is one of the most significant aspects of computation, the power of this being the ability to transform a finite configuration into a potentially infinite result.
-This is done in $\lambda$-Calculus through the use of one of the most remarkable functions, the \textbf{Y} combinator:
+This is done in $\lambda$-calculus through the use of one of the most remarkable functions, the \textbf{Y} combinator:
 \cite{rojas2015lambdatutorial}
@@
 \end{equation*}
-This function is remarkable because it is a `fixpoint operator' - it is able to easily generate a `fixpoint' of any given function (a value $x$ is a fixpoint of the function $f$ if and only if $fx = x$) by applying the function as the first parameter of the \textbf{Y} combinator.
+This function is remarkable because it is a `fixpoint operator' - it is able to generate a `fixpoint' of any given function (a value $x$ is a fixpoint of the function $f$ if and only if $fx = x$) by applying the function as the first parameter of the \textbf{Y} combinator.
 
@@
 \bm{\mathrm{\xi}} &= \lambda fa.\bm{\mathrm{Z}}a\bm{\mathrm{1}}[\bm{\mathrm{M}}a(f[\bm{\mathrm{P}}a])]\\
-\bm{!} &= \bm{\xi}!
+\bm{!} &= \bm{\xi}\bm{!}
 \end{aligned}
@@
 the factorial function is the $\bm{\xi}$ function with itself as the argument $f$.
-Unfortunately such a definition is illegal under $\lambda$-Calculus as all functions are strictly anonymous - this is where the \textbf{Y} combinator comes into play.
+Unfortunately such a definition is illegal under $\lambda$-calculus as all functions are strictly anonymous - this is where the \textbf{Y} combinator comes into play.
 To find the factorial of \textbf{3}:
@@
 \end{equation*}
-The \textbf{Y} combinator allows for \textbf{Y}$\bm{\xi}$ to be applied as the first argument to the $\bm{\xi}$ function - as a result, the procedure also processes \textbf{2} and \textbf{1}, before stopping at \textbf{0} (which produces simply \textbf{1}.
+The \textbf{Y} combinator allows for \textbf{Y}$\bm{\xi}$ to be applied as the first argument to the $\bm{\xi}$ function - as a result, the procedure also processes \textbf{2} and \textbf{1}, before stopping at \textbf{0} (which produces simply \textbf{1}).
 To simplify, the factorial function:
@@
 
-Our brief stroll through the key aspects of $\lambda$-Calculus is complete.
-We have shown that many basic necessary concepts in a common programming language can be defined through the use of two simple axioms - that of the concept of functions, and the operation of substitution.
-$\lambda$-Calculus was described by Church as an `effectively calculable' system, in that it could perform any calculable calculation.
-In more common terms, it is Turing-complete - we will look at what this is and why this is the case later on.
-However, it is clear to see that the Calculus is able to simulate many functions of the computer - data storage with pairs (pairs of pairs can be used for storing more than two items of data as shown in \cref{sec:LambdaUnivTape}), conditionals and booleans, integers and arithmetic and, finally, the ability to be continuous (circular) from a finite configuration.
+In this section, we have shown that many basic necessary concepts in a common programming language can be defined through the use of two simple axioms.
+The calculus is able to simulate many functions of the computer; data storage with pairs (pairs of pairs can be used for storing more than two items of data as shown in \cref{sec:LambdaUnivTape}), conditionals and booleans, integers and arithmetic (further arithmetic can be found in appendix \ref{appendix:lambdaarithmetic}) and, finally, the ability to be continuous (circular) from a finite configuration.
 $\lambda$-Calculus is our first attempt to clarify the attributes of a computer, and does so both simply and aesthetically.

### 2017-06-18 Draft 2/Section 2 - Turing Machines.tex
Hmm looks like we're all done here
WIth 17 hours 42 minutes to go as well, I'm impressed

@@
 
-At roughly the same time, the English mathematician Alan Turing was constructing a totally different method of achieving the same goal: rather than a basic and heavily theoretical system, it was far more physical and far closer to the mechanical computers that eventually implemented the idea.
+At roughly the same time, the English mathematician Alan Turing was constructing a totally different method of achieving the same goal: a far more physical system that was far closer to the mechanical computers that eventually implemented the idea.
 
 \subsection{Examples of simple Turing Machines}\label{sec:TMacIntro}
-The Turing Machine is composed of two parts.
-Firstly, an ordered set of \textit{cells} of infinite\footnote{Many definitions of Turing Machines have the tape extending infinitely in one direction only - in fact for full functionality a tape extending infinitely in both directions is unnecessary.} length known as \textit{tape}.
-On each of these cells is one of a finite set of \textit{symbols} - either alphanumeric characters or the symbol which represents an empty cell.
-At a given point on this tape is a \textit{tape head} (or cursor) which is able to write symbols to the current cell.
-Secondly, a finite set of instructions known as \textit{states} contain finite-length sequences of operations known as the \textit{transition function} which the cursor enacts, and the states that the machine moves to after performing those operations.
+The Turing machine is composed of two parts.
+Firstly, an ordered set of \textit{cells} of infinite\footnote{Many definitions of Turing machines have the tape extending infinitely in one direction only - in fact for full functionality a tape extending infinitely in both directions is unnecessary.} length known as \textit{tape} exists; on each of these cells one of a finite set of \textit{symbols} (either alphanumeric characters or the symbol which represents an empty cell) can be written.
+Above a given cell on this tape is a \textit{tape head} (or cursor) which is able to read the symbol on the cell below it, and can also write a new symbol or erase the current symbol.
+The cursor can move to the left or right.
+Secondly, a finite set of \textit{states} exist as a instructions for the machine: when the machine is in a certain state, it will read the cell under the cursor and perform a set of operations (the \textit{transition function}) which is dependent on that specific state and symbol.
+When the transition function has completed, the machine will be given a new state; the sequence then repeats itself.
 An example \textit{description} of a set of states would be: \cite{turing1936computablenumbers}
@@
 
-This description table format shall be used to describe Turing Machine configurations.
+This description table format shall be used to describe Turing machine descriptions.
 First of all, the final line describes the starting state ($\mathbb{A}$).
-When the machine begins an iteration on any one of these states, it first checks if the symbol aspect of the configuration is equal to the symbol currently under the cursor on the tape.
-If this condition is met, the transition function is carried out - P\textit{n} for any symbol \textit{n} prints the symbol \textit{n} on the tape under the cursor; E erases any symbol under the cursor\footnote{More formally, prints the empty cell symbol}; L moves the cursor to the left; R moves the cursor to the right.
+When the machine begins an iteration on any one of these states, it first checks if the symbol aspect of the description is equal to the symbol currently under the cursor on the tape.
+If this condition is met, the transition function is carried out - P\textit{n} for any symbol \textit{n} prints the symbol \textit{n} on the tape under the cursor; E erases any symbol under the cursor\footnote{More formally, prints the empty cell symbol}; L moves the cursor one square to the left; R moves the cursor one square to the right.
 When these operations are completed, the state is set to that described in the last column (in future I shall describe this using the $\rightarrow$ symbol, for example $\rightarrow \mathbb{B}$).
@@
 
-In this case, it is not difficult to see that as the machine runs, it leaves a sequence of alternating 0s and 1s on every other cell on the tape.
+In this case as the machine runs it leaves a sequence of alternating 0s and 1s on every other cell on the tape.
 With the use of the \textit{symbol} condition, this table can be simplified: \cite{turing1936computablenumbers}
@@
 
-It is again not difficult to see that this produces the same output as the previous machine, but this time using only one state.
+This produces the same output as the previous machine, but this time using only one state.
 
-To aid the operation of Turing machines, the tape shall begin with the sequence \texttt{e e 0}, and cells shall be seperated into value cells and marker cells.
+To aid the operation of Turing machines, the tape shall begin with the sequence \texttt{e e 0}, and cells shall be separated into value cells and marker cells.
 On value cells (odd-numbered cells) the symbols of the output sequence are printed.
@@
 To the right of each value cell is a label cell.
-These cells will either be left empty or will contain a 'marker' symbol, which labels the symbol on the value cell to the left; these are not part of the output sequence.
-This method is frequently used by Alan Turing in \cite{turing1936computablenumbers}, and an example machine can be found in appendix \ref{appendix:turingexampleexp}.
+These cells will either be left empty or will contain a `marker' symbol, which labels the symbol on the value cell to the left; these are not part of the output sequence.
+This method is frequently used by Turing in \cite{turing1936computablenumbers}, and an example machine can be found in appendix \ref{appendix:turingexampleexp}.
 
@@
 They are denoted by a lowercase letter and a set of arguments contained in brackets - arguments in gothic script refer to states (or other \textit{m}-functions), and arguments in italics refer to symbols.
-When an \textit{m}-function is triggered, the italic and gothic symbols in the description are substituted by the supplied arguments (similar to application in $\lambda$-Calculus).
+When an \textit{m}-function is triggered, the italic and gothic symbols in the description are substituted by the supplied arguments (similar to application in $\lambda$-calculus).
 An example of an \textit{m}-function would be the function $\mathbb{f}$ below: \cite{turing1936computablenumbers}
@@
 The function $\mathbb{f}$ takes three arguments - the states \textfrak{C} and \textfrak{E} and the symbol \textit{a}.
-It is not difficult to see that if $\rightarrow \mathbb{f}$($\mathbb{A}$, $\mathbb{B}$, x) the cursor would trigger $\mathbb{A}$ at the first occurrence of \texttt{x}.
+If $\rightarrow \mathbb{f}$(\texttt{x}, $\mathbb{A}$, $\mathbb{B}$) the cursor would trigger $\mathbb{A}$ at the first occurrence of \texttt{x}.
 If no symbols \texttt{x} were found, \textfrak{E} would be triggered on the marker of the first empty value square.
@@
     \hhline{====}
-    $\mathbb{l}$(\textfrak{C}, \textfrak{E}) & - & L & \textfrak{C} & Moves cursor left\\
+    $\mathbb{l}$(\textfrak{C}) & - & L & \textfrak{C} & Moves cursor left\\
     \hhline{----}
-    $\mathbb{r}$(\textfrak{C}, \textfrak{E}) & - & R & \textfrak{C} & Moves cursor right\\
+    $\mathbb{r}$(\textfrak{C}) & - & R & \textfrak{C} & Moves cursor right\\
     \hhline{====}
@@
     \hhline{====}
-    $\mathbb{p0}$(\textfrak{C}, \textfrak{E}) & - & P\texttt{0} & \textfrak{C} & Prints \texttt{0} \\
+    $\mathbb{p0}$(\textfrak{C}) & - & P\texttt{0} & \textfrak{C} & Prints \texttt{0} \\
     \hhline{----}
-    $\mathbb{p1}$(\textfrak{C}, \textfrak{E}) & - & P\texttt{1} & \textfrak{C} & Prints \texttt{1} \\
+    $\mathbb{p1}$(\textfrak{C}) & - & P\texttt{1} & \textfrak{C} & Prints \texttt{1} \\
     \hhline{----}
-    $\mathbb{p}$(\textit{s},\textfrak{C}, \textfrak{E}) & - & P\textit{s} & \textfrak{C} & Prints \textit{s} \\
+    $\mathbb{p}$(\textit{s}, \textfrak{C}) & - & P\textit{s} & \textfrak{C} & Prints \textit{s} \\
     \hhline{====}
@@
 The first data structure we shall define is the simple boolean - only 1 bit (1 value square) long.
-In order to identify these sequences on the tape as booleans, we shall label the first character of the boolean with an identifier (we shall call these pointers) unique to that boolean variable - for example the symbol \texttt{\textbf{B}myvar} (bear in mind this is one symbol, not six) would mark a boolean named \textit{myvar}.
+In order to identify these sequences on the tape as booleans, we shall label the first character of the structure with an identifier (we shall call these pointers) unique to that variable - for example the symbol \texttt{\textbf{B}myvar} (bear in mind this is one symbol, not six) would mark a boolean named \textit{myvar}.
 Let us define some \textit{m}-functions to define and assign values to variables of the boolean type:
@@
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p0}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p1}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\ 
+    \multirow{3}{*}{$\mathbb{\mathbf{b}copy}_1$(\textit{w},\textfrak{C},\textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p0}$(\textfrak{C}), \textfrak{E}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p1}$(\textfrak{C}), \textfrak{E}) \\ 
                                                                                        & Other & - & \textfrak{E} \\
@@
 
-The first takes one pointer \textit{p}, finds the first free bit (value square) on the tape, writes the dummy value of \texttt{0} to it and marks it with \textit{p}.
-This method of appending makes the assumption that no value squares are left empty across the used tape - in order to preserve this, we shall only append to value squares directly at the end of the used tape, and we shall never erase (only overwrite fully) value squares.
+The first takes one pointer \textit{p}, finds the first free bit (value square) on the tape, writes the value of \texttt{0} to it and marks it with \textit{p}\footnote{This method of appending makes the assumption that no value squares are left empty across the used tape - in order to preserve this, we shall only append to value squares directly at the end of the used tape, and we shall never erase (only overwrite fully) value squares}.
 The second very simply finds the bit at pointer \textit{r}, and branches to write either \texttt{0} or \texttt{1} at the bit at the pointer \textit{w}.
@@
 
-As we did in $\lambda$-Calculus, we shall define boolean operations.
+As we did in $\lambda$-calculus, we shall define boolean operations.
 Every operation will take one or many pointers as arguments, and write the evaluated result to another given pointer.
@@
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}not}_1$(\textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p1}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p0}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\ 
+    \multirow{3}{*}{$\mathbb{\mathbf{b}not}_1$(\textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p1}$(\textfrak{C}), \textfrak{E}) \\
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p0}$(\textfrak{C}), \textfrak{E}) \\ 
                                                                                        & Other & - & \textfrak{E} \\
@@
 \medskip
-This is almost identical to the copying function, but inverting the written symbols. The definition of the remaining logical functions based on truth tables now becomes simple:
+This is almost identical to the copying function, but inverting the written symbols. The definition of the remaining logical functions based on truth tables is as follows:
 
@@
     \hhline{----}
-    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p0}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\
+    \multirow{3}{*}{$\mathbb{\mathbf{b}and}_1$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E})} & \texttt{0} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p0}$(\textfrak{C}), \textfrak{E}) \\
                                                                                        & \texttt{1} & - & $\mathbb{\mathbf{b}copy}$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}) \\ 
@@
                                                                                        & \texttt{0} & - & $\mathbb{\mathbf{b}copy}$(\textit{b}, \textit{w}, \textfrak{C}, \textfrak{E}) \\
-                                                                                       & \texttt{1} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p1}$(\textfrak{C}, \textfrak{E}), \textfrak{E}) \\ 
+                                                                                       & \texttt{1} & - & $\mathbb{fl}$(\textit{w}, $\mathbb{p1}$(\textfrak{C}), \textfrak{E}) \\ 
                                                                                        & Other & - & \textfrak{E} \\
@@
 \medskip
-In each of these, the first argument \textit{a} is observed, and an action which either writes a \texttt{1} or \texttt{0}, or copies or negates from \textit{b} depending on the truth tables, in a very similar manner to $\lambda$-Calculus.
-Gradually, the cryptic and simplified language of Turing machines is yielding results similar to that of a computer.
+In each of these, the first argument \textit{a} is observed and an action either writes a \texttt{1} or \texttt{0} or copies or negates from \textit{b} depending on the truth tables in a very similar manner to $\lambda$-calculus.
+Gradually, the cryptic and obfuscated language of Turing machines is yielding results similar to that of a computer.
 
@@
 As we have moved into more and more complex Turing machine functions, it can be noted that the middle two columns of the description are becoming gradually more empty - this is due to the fact that their operation can be entirely represented within \textit{m}-functions.
-We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, and $\mathbb{p1}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.
+We have started doing so with the functions $\mathbb{l}$, $\mathbb{r}$, $\mathbb{p0}$, $\mathbb{p1}$, and $\mathbb{p}$ - furthermore, it is not difficult to create conditional functions to replicate the operation of the second column.
 
@@
 Therefore, we will use our function method to define what is effectively a list of commands for the machine which will be executed in order.
-The main difference in this system is that, as the \textfrak{C} argument is always the function that must be run when that function is completed (except in the case of the conditional function), on interpretation of the language the entire operation of the machine after that point must be passed as the \textfrak{C} argument to that function in order for the functions to be called sequentially\footnote{For clarity, I have ignored error handling (i.e.
+The main difference in this system is that, as the \textfrak{C} argument is always the function that must be run when that function is completed (except in the case of the conditional function), on interpretation of the language the entire operation of the machine after that point must be passed as the \textfrak{C} argument to that function in order for the functions to be called sequentially\footnote{For simplicity, I have ignored error handling (i.e.
 omitted the E argument).}.
@@
 Turing machines are truly remarkable entities.
-While $\lambda$-Calculus was able to mimic the operation of a modern computer (behaving like a purely functional programming language such as Haskell), its axioms were completely abstract - the conceptual operations of abstraction and application, while being probably more useful than Turing machines in terms of yielding practical results, were unlike anything which could actually be created in the real world.
+While $\lambda$-calculus was able to mimic the operation of a modern computer (behaving like a purely functional programming language such as Haskell), its axioms were completely abstract - the conceptual operations of abstraction and application, while being probably more useful than Turing machines in terms of yielding practical results, were unlike anything which could actually be created in the real world.
 However, Turing machines are entirely grounded in physical reality, and it is totally conceivable how one could create such a machine, while still being able to produce results very similar to that of an imperative programming language such as C - data storage, typed and referenceable variables, and boolean logic, all performed as a sequence of commands.
@@
 This is not a sufficiently rigorous definition - a machine which seems to behave like a computer is not necessarily able to evaluate any computable function.
-For practicality's sake, it seems natural for Turing Machines to be chosen to be the pinnacle of computability: any machine that can be programmed in such a way that it emulates a Turing machine shall be called a  `Turing-complete' computer, and any problem a Turing machine can solve is a computable function.
+For practicality's sake, it seems natural for Turing machines to be chosen as the pinnacle of computability: any machine that can be programmed in such a way that it emulates a Turing machine shall be called a  `Turing-complete' computer, and any problem a Turing machine can solve is a computable function.
 
-It is unseemly that the abstract notion of computability relies necessarily on the specific design of the Turing machine: the idea of computability is a robust, almost Platonic reality, that Turing machines, $\lambda$-Calculus and all other effectively calculable devices, physical or theoretical, participate within equally.
-In fact, the idea of Turing-completeness presented earlier achieves this aim.
+It is unseemly that the abstract notion of computability relies necessarily on the specific design of the Turing machine: the idea of computability is a robust, almost Platonic reality, that Turing machines, $\lambda$-calculus and all other effectively calculable devices, physical or theoretical, participate within equally.
+In fact, the idea of Turing-completeness achieves this aim.
 This is the concept of Universality.
 
-The main idea behind Universality is the concept of the Universal Machine, a machine which is able to entirely emulate another given system.
+The main idea behind Universality is the Universal Machine, a machine which is able to entirely emulate another given system.
 As shown in \cite{turing1936computablenumbers}, a Turing machine can be configured in such a way that it emulates a Turing machine; this machine reads a description table from the start of the tape, and then produces the output that the machine described in the pre-written table would produce.
-Furthermore, $\lambda$-Calculus is also Turing-complete - this is demonstrated entirely in appendix \ref{appendix:lambdauniversaldemo}.
+Furthermore, $\lambda$-calculus is also Turing-complete - this is demonstrated entirely in appendix \ref{appendix:lambdauniversaldemo}.
 This is done by producing a function that takes the current configuration of a Turing machine (in terms of the tape, state and description table) as input, and transforms it into the next configuration in sequence that a Turing machine would produce.
-This function would then be run repeatedly on the configuration using the \textbf{Y} combinator, hence emulating the action of Turing machines.
-Hence the $\lambda$-Calculus can produce a Universal Machine for Turing machines.
+This function would then be run repeatedly on the configuration using the \textbf{Y} combinator, thus emulating the action of a Turing machine.
+Hence the $\lambda$-calculus can produce a Universal Machine for Turing machines.
 
-Most remarkably, Turing machines are in fact able to also emulate $\lambda$-Caluculus.
+Most remarkably, Turing machines are in fact able to also emulate $\lambda$-calculus.
 This shall not be demonstrated directly, but it seems intuitive that a Turing machine could carry out processes of abstraction and application since they are at heart simple algorithmic processes; a Turing machine would evaluate $\lambda$-terms in a similar way to how the human mind would.
-This leads us onto the remarkable fact that since Turing machines and $\lambda$-Calculus can produce Universal Machines for each other, each has the potential to perform any task the other can perform, and hence they are equal in power.
-Furthermore, many other theoretical methods of computation such as Kurt G\"odel's General Recursive Functions also share this equivalence \cite{copeland2002ctt}.
+This leads us onto the remarkable fact that since Turing machines and $\lambda$-calculus can produce Universal Machines for each other, each has the potential to perform any task the other can perform, and hence they are equal in power.
+Furthermore, many other theoretical methods of computation such as $\mu$-Recursive Functions also share this equivalence \cite{copeland2002ctt}.
 
-It therefore seems that the informal notion of computability can be formally defined with the use of one of these equivalent computational systems - this is a truly remarkable result, which produces a very strong basis for computability.
+The coincidence of these varied computational models make it appear that the informal notion of computability can be formally defined with the use of one of any one of these equivalent computational systems.his is a truly remarkable result, which produces a very strong basis for computability.
 With this test for computability in place, the question of whether World War 2 produced computing machines becomes apparently trivial.

### 2017-06-18 Draft 2/Section 4 - Zuse's Z3.tex
Hmm looks like we're all done here
WIth 17 hours 42 minutes to go as well, I'm impressed

@@
 While still very simplistic, and not directly intended for universal computation, Z3 was structurally far closer to achieving this aim than other machines of the time.
-In this section I shall therefore attempt to implement a Universal machine in Z3 in order to determine its nature as a computing machine.
+I shall therefore attempt to implement a Universal machine in Z3 in order to determine its nature as a computing machine.
 
@@
 In  something similar to standard form, each number was composed of an `exponent' representing the order of magnitude of the number, and a `significand' that represented the digits of the number; see \cite{rojas1997z3architecture} for details.}, which could be referred to by the programmer through the use of a numeric address of a particular data slot.
-For the sake of clarity, we shall use single lowercase letters to represent addresses rather than the 6-bit unisgned integers of Z3.
+For the sake of clarity, we shall use single lowercase letters to represent addresses rather than the 6-bit unsigned integers of Z3.
 
@@
 The instruction set for Z3 consisted of three types of operation - I/O, memory and arithmetic.
-These instructions would be performed with respect to two floating-point registers, $R_1$ and $R_2$, which act as the two arguments for any arithmetical operation, and could be written to and read from by the non-arithmetical operations.
+These instructions would be performed with respect to two floating-point registers, $R_1$ and $R_2$, which act as the two arguments for any arithmetical operation and could be written to and read from by the non-arithmetical operations.
 
@@
 The first thing that must be considered when looking for universality in a potentially Turing-complete machine is the fact that, by the strict definition of a Turing machine, it must require infinite memory due to the nature of its tape.
-Unfortunately, this is impossible in the physical world as memory is always finite.
-As such, we must revise our definition of Turing-completeness to require only a finite tape.
+Unfortunately, this is impossible in the physical world, so we must revise our definition of Turing-completeness to require only a finite yet extendable tape.
 
-At first glance, it is unclear that Z3 can be made into a universal machine due to the fact that it allows for neither conditional branching\footnote{The ability to perform different operations depending on the state of a stored value} nor indirect addressing\footnote{The ability to refer to values stored in memory when the address of that memory is not specifically referred to in the program but is rather obtained from the value of some variable currently in memory}.
-However, through use of the tools available to the programmer these features can be emulated, and a Turing Machine can be simulated.
-This uses many tecniques explained in \cite{rojas1998z3universal}.
+At first glance, it is unclear that Z3 can be made into a universal machine due to the fact that it allows for neither conditional branching nor indirect addressing (the ability to retrieve a value from memory using an address whose numeric value is not directly specified in the program i.e.
+is read from memory or calculated).
+However, through use of the tools available to the programmer these features can be emulated, and a Turing machine can be simulated.
+This uses many techniques explained in \cite{rojas1998z3universal}.
 
@@
 Or, for clarity, $a = (a \cdot t) + (1 - t)(b\ \mathrm{op}\ c)$.
-If $t = 1$, $v$ is set to $t$; otherwise it is set to $0$.
-Furthermore, if $t = 0$, $u$ is set to the outcome of the operation; otherwise it is set to $0$ again.
-Therefore, if $t = 0$, $a$ is set to the outcome of the operation; otherwise it is set back to its original value.
+If $t = 0$, $a$ is set to the outcome of the operation; if $t = 0$ $a$ is set to its original value.
 As such, after this transformation has been put in place for every $P$ operation, and a method to set $t$ at the start of the switch statement has been implemented, every new command in this program can be executed - most superfluously - in order to only use the $z$-th command.
@@
 
-This is done using the following piece of code, where $e$ has been pre-set to a value much less than 1 (e.g. 1/1000).
+This is done using the following piece of code, where $e$ has been preset to a value much less than 1 (e.g. 1/1000).
 
@@
 $x$ could potentially be the output from a previous arithmetical operation, which could be read from memory.
-Relying on the fact that this region is finite (and furthermore that the tape length is also finite), this can be done most simply with a switch statement with a case for every address $z$ between $n_a$ and $n_b$ as shown.
+Relying on the fact that this region is finite (and furthermore that the tape length is also finite), this can be done most simply using a switch statement with a case for every address $z$ between $n_a$ and $n_b$ as shown.
 \begin{gather*}
@@
 These cases are enumerated within the switch for all $n_a \leq z \leq n_b$; hence, when the statement is executed, the only case where the contents of address $z$ will be written to $a$ is the case where $x=z$; hence, $a$ will be set to the contents of address $x$.
-At this point, it becomes very clear the extent to which  is not suited to universal computation.
+
+At this point it becomes very clear the extent to which Z3 is not suited to universal computation.
 When every single applicable memory address must be specified individually, with five operations per address to implement the case, each operation consisting of four instructions, it is obvious that Z3 is in no way a \textit{practical} universal machine.
@@
 The tape is represented as the memory region between $n_a$ and $n_b$, and the cursor index is stored as an integer that can be moved through incrementation or decrementation.
-The tape can be read through indirect addressing, and the transition can be derived from the state and read symbol through conditional branching.
+The tape can be read through indirect addressing, and the transition function can be derived from the state and read symbol through conditional branching.
 
@@
 
-A clear criticism of this techique is that it slows down computation enormously.
-Running at roughly 5.33Hz with 3 cycles for addition, 4-5 for subtraction and 16 for multiplication (from \cite{rojas1997z3architecture}), to perform each case statement within a switch Z3 would take up to $\sim$7.5 seconds on top of the time for the operation itself; for the indirect addressing operation alone, when this occurs for every single addressable memory slot it is clear that for a single iteration of the Turing machine Z3 would take an unfeasably long time.
-From a purely theoretical point of view this is irrelevant - it is clear that this particular programming of Z3 is useless in the same way that using a Turing Machine to solve real-world problems would be totally impractical.
+A clear criticism of th  is technique is that it slows down computation enormously.
+Running at roughly 5.33Hz with 3 cycles for addition, 4-5 for subtraction and 16 for multiplication (from \cite{rojas1997z3architecture}), to perform each case statement within a switch Z3 would take up to $\sim$7.5 seconds on top of the time for the operation itself; for the indirect addressing operation alone, when this occurs for every single addressable memory slot it is clear that for a single iteration of the Turing machine Z3 would take an unfeasibly long time.
+From a purely theoretical point of view this is irrelevant - it is clear that this particular programming of Z3 is useless in the same way that using a Turing machine to solve real-world problems would be totally impractical.
 
@@
 
-The major breakthrough in computation which allowed for the first clearly universal machines was the implementation of a Von Neumann Architecture, which allowed computers to run programs from memory\footnote{Of course, because Turing Machines are themselves Universal machines (see \cite{turing1936computablenumbers}), this was theoretically achieved with Z3; Von Neumann machines were oriented towards performing in such a way.}.
+The major breakthrough in computation which allowed for the first clearly universal machines was the implementation of a Von Neumann Architecture, which allowed computers to run programs from memory\footnote{Of course, because Turing machines are themselves Universal machines (see \cite{turing1936computablenumbers}), this was theoretically achieved with Z3; Von Neumann machines were oriented towards performing in such a way.}.
 The first machine to implement this was the Manchester Small Scale Experimental Machine (SSEM), or `Baby' \cite{napperWEB17baby}, which stored data using the Williams-Kilburn Tube, a type of cathode ray tube.
